### 2018-03-06 article/article.tex
Tidy up for new repository, important old stuf ported over

\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\usepackage{color}
\usepackage{authblk}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{amsmath}
%PREPRINT/MANUSCRIPT OPTIONS
\usepackage{setspace}
\usepackage{lineno}
\linenumbers
\doublespacing

%opening

% \author{
%     \IEEEauthorblockN{James Gilbert\IEEEauthorrefmark{1}, Nicole Pearcy\IEEEauthorrefmark{1}, Jamie Twycross\IEEEauthorrefmark{2}}
%     \IEEEauthorblockA{\IEEEauthorrefmark{1}Synthetic Biology Research Centre, School of Life Sciences, University of Nottingham}
%     \IEEEauthorblockA{\IEEEauthorrefmark{2}Intelligent Modelling and Analysis Group, School of Computer Science, University of Nottingham}
% }

\begin{document}

\title{From clusters to queries: exploiting uncertainty in the modular landscape of complex networks}

%\titlerunning{Short form of title}        % if too long for running head

\author{James P Gilbert         \and
	Jamie Twycross 		\and
	John King
	}
\date{Received: date / Accepted: date}

\maketitle

\begin{abstract}
Uncovering latent community structure in complex networks is a field that has received an enormous amount of attention.
Unfortunately, whilst potentially very powerful unsupervised methods for classifying nodes into similar groups based on topology alone has been shown to have several major limitations.
Crucially, the search space for module extraction approaches appears to be extremely glassy, with many high valued solutions that lack any real similarity to one another.
However, in this paper we argue that this is not a flaw with the modularity maximisation algorithm but, rather, information that can be used to aid the classification of functional relationships between vertices.
Formally, we present an approach to generating a search ``index'' for a network, based on the space of high value modular partitions.
This search spaces allows the formulation of query based measures that provide a score for the level of relatedness to a given labelled query set.
The methods developed in this paper are applied to biological and social datasets with ground-truth label data, with very small query sets for nodes.
When tested on both real and synthetic datasets our method achieves extremely high levels of classification.
Furthermore, the approach can be applied in distributed environments potentially allowing it to scale to very large networks.
\end{abstract}

\section{Introduction}

A fundamental issue at the heart of machine learning methods applied to large scale datasets is the ability to correctly identify classes of related objects in an unsupervised manner.
In network science, this methodology is often referred to as \textit{community} detection, due to the intuitive analogy from the social sciences \cite{fortunato2010community}.
Many algorithms exist to solve this problem, yet initial starting conditions or different optimisation strategies may result in conflicting results even when the same objective function is being maximised \cite{good2010performance}.
In this paper, we develop an intuitive method to use the uncertainty amongst a high number of near optimal solutions to measure the overall quality of a given labelling scheme that can come from classes known \textit{a-priori} or clusters detected through other methods.
This approach also allows the expansion of labels to find potentially related vertices to an initial starting subset.

The number and size of communities is, generally, not known \textit{a priori}, and the problem has been shown to be NP-hard.
The work of Good \textit{et al.} \cite{good2010performance} recently highlighted that the popular modularity maximisation algorithm has a highly ``glassy'' search space.
In this situation there are many locally optimal partitions that bear little to no resemblance to each other by measure of mutual information.
This allows greedy optimisation algorithms \cite{blondel2008fast} to trivially find solutions that score extremely high values of modularity.
In order to solve this issue, certain approaches use a consensus based approach to clustering, combining many high value partitions into a given median partition.

Though the methods presented here can be applied to any complex network, the focus of this work is biological in nature; characterising the function of all genes within an organism is a problem critical to systems biology \cite{}.
In many situations, only the role of a small number of genes is known, with much of the annotation for a given organism being computed through naive homology information that ignores the role of a gene within a wider context.
The advent of high throughput experimental datasets has allowed the construction of genome scale networks, leading to the observation of non-trivial topological properties such as densely connected clusters \cite{ArabidopsisConsortium2011}.
These densely connected clusters are widely believed to be associated with specific function, such as protein complexes or biochemical pathways \cite{}.

This, and work in related fields, has led to the desire for computational techniques that elucidate related, modular structure in the form of community detection algorithms \cite{fortunato2010community}.
As a form of unsupervised machine learning module extraction methods largely focus on optimising some objective function with the desire of finding meaningful clusterings.
Perhaps the most popular of these methods is that of modularity maximisation \cite{newman2004}, which seeks to find the most unexpected partition of a graph with respect to a given null model.
One limitation of partition based methods is that each vertex can only belong to a community.
Overlapping methods have recently been applied to this problem in both \textit{crisp} \cite{ahn2010link, lancichinetti2011finding} and \textit{fuzzy} \cite{gregory2011fuzzy} based algorithms.

In this paper, we do not seek to find a single ``best'' partition, either overlapping or not.
Instead, we use the large number of highly modular solutions to form the index for a search query system.
In essence, this is a method of semi-supervised learning that attempts to find items related given labelled sets of vertices using topology alone.
Each high value partition, if statistically more modular than random, can be treated as information about the relationships between vertices.
As the objective of community detection approaches is to relate information, it is assumed that some labelled meta-data can be used to find unlabelled, potentially related vertices.
The overall objective can be thought of as a form of recommender system \cite{ricci2011introduction}, relating a given query in the form of a vertex set to potentially related information by exploiting the co-occurrence between communities.

In this vein, we apply the method presented in this paper to the problem of classifying biological function.
The objective of our algorithm, in this sense, is given sets of known function for genes or proteins within interaction networks, to generate meaningful hypothesis that can be externally validated.
Naturally this process depends heavily on the quality of underlying datasets, however, we feel this approach is a conceptual change from conventional module detection approaches which only consider a single clustering of a network, overlapping or not, where only binary classification is considered.

We propose an algorithm that pre-computes an index of clusterings for a given complex network, based on the fast greedy Louvain algorithm \cite{blondel2008fast}, used in a distributed manner.
The detected clusters then form the basis of a searching algorithm that allows one to compute the relatedness of subsets of nodes.
The querying method is a polynomial time algorithm that could be trivially adapted to form the basis of many user facing applications.
This approach is applied to a number of real world metabolic and protein interaction datasets with explicit queries relating to biological function.
In addition, the ranking scores for the uncertainty of community classification are used to capture critical ``bridge'' nodes and edges allowing an efficient multi-scale form of visualisation for networks with glassy modular structure.

\section{Vertex classification}
The intuitive notion that the structure of a vertex's connections gives insight into its function is a fundamental basis for research in network science.
In many cases, the role of given node is uncharacterised and we would seek to discover latent relationships through methods such as community detection.
The basic premise of community detection is that detecting dense topological sub-graphs allows one to uncover the function of vertices \cite{}.

In this paper, we consider the notion of relatedness to require additional meta-data, or vertex labels, that can be attributed to specific ontological definitions.
In many situations this information will be sparse or incomplete.
For example, in biological networks only a very small number of organisms have a high level of coverage in terms of functional annotation \cite{}.

The problem tackled in this paper can be formulated as follows:
Given a graph made up of vertices and edges $G = (V, E)$, we formally ask the question; \textit{How related is a given vertex to a given query set?}
This question assumes that a given query set is formally related, in practice, however, this may not be the case.
Consequently we also use our approach to ask another question; \textit{ How related are a set of query vertices?}

\section{Exploiting the modularity query space}
In order to characterise community structure, one of the most popular approaches is to use modularity maximisation.
The modularity quality function of a partition on a graph is given by the following equation \cite{newman2004}
\begin{equation}\label{eq:modularity}
  Q = \frac{1}{2m}\sum_{i,j} \left[A_{ij} - \frac{k_i k_j}{2m}\right]\delta(c_i, c_j),
\end{equation}
where $m$ is the number of edges in the network, $A_{ij}$ is the binary variable indicating the adjacency of nodes $i$ and $j$, $k_i$ is the degree of a vertex, $c_i$ indicates the community of a given vertex and $\delta(c_i, c_j)$ is the Kronecker delta such that $\delta(c_i, c_j) = 1$ if $c_i = c_j$ and $0$ otherwise.
As a combinatorial optimisation problem, there are many different algorithmic approaches to finding high values of $Q$.

The work by \cite{good2010performance} forms the basis of the motivation of the approach taken here.
In this study, the authors discovered that the modularity search space for many real-world networks contains a huge number of high value solutions.
Each of these solution partitions are extremely close to the global maxima, making it both difficult to find the optimal value of $Q$ and difficult to argue that the highest scoring partition is the ``true'' community structure.
This fact is visually demonstrated with the software from \cite{good2010performance} in Figure \ref{fig:modular_search_space}, which shows the modularity search space of an \textit{E coli} metabolic network reconstruction \cite{GuimeraNature2005}.
The similarity between the partitions is compared with variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear}.

\begin{figure}
\centering
 \includegraphics[width=0.7\textwidth]{images/search_space_3.png}
 \caption{
 Modularity search space of the \textit{E. coli} metabolic network.
 Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
  The inset (top) demonstrates the landscape of the high modularity region. 
  Figure generated with the software of Good \textit{et al.}\cite{good2010performance}.
 }
 \label{fig:modular_search_space}
\end{figure}

In our work, instead of seeing this modular search space as a flaw we consider each high value partition to be information about latent relationships between vertices inferred through the topology of the network.
In the parlance of the computational and information sciences, we consider the mapping of this search space to be an \textit{index} analogous to search algorithms.
Whilst methods based on simulated annealing can be used to guarantee full coverage of the network, the following section describes a method adapted from the greedy agglomerative Louvain algorithm \cite{blondel2008fast}.

\subsection{Algorithm outline}
A broad outline of the proposed method is presented in Figure \ref{fig:algorithm_outline}.
In essence, the objective is to use multiple modular representation of a given dataset to generate a relatedness score for a given set of query vertices.

\begin{figure*}
 \centering
 \includegraphics[width=0.6\textwidth]{images/meth_fig/fig1_desc.eps}
 \caption{Outline of the proposed approach to querying networks by using multiple, high quality representations of modular networks.}
 \label{fig:algorithm_outline}
\end{figure*}

\subsection{Generating the search index}
In order to cover the space of high modularity partitions, randomly generated starting partitions are computed with a random cut set.
To achieve this each edge is either placed inside the cut set or not as the result of an independent Bernoulli trial. 
Each random partition is used as the starting partition for the greedy louvain process.
In principle, any search exploration procedure, such as simulated annealing \cite{GuimeraNature2005} could be used.
The Louvain algorithm is selected as it is fast, running in $O(n \log n)$ time complexity \cite{blondel2008fast}, and because it is a greedy algorithm is is guaranteed to stop after finding a locally maximal solution.

The Louvain algorithm is conceptually very simple; starting from a random partition, clusters are agglomerated if the merge results in a positive change in modularity $\Delta Q$.
When no possible moves result in an increase in modularity the algorithm has found a local optima and stops.
Whilst, in principle, the found local optima should have a high modularity score this is not guaranteed.
Consequently, the process here rejects any solutions if the value of modularity is not significantly higher than the distribution of starting partitions.
This is achieved by means of a standard $z$-test, formally the probability of generating a random partition with a modularity score $Q$ as high as observed as a result of the Louvain optimisation must be $p < 0.01$.
Furthermore, only unique solutions are accepted.

The index \textit{coverage} is directly proportional to the number of starting random partitions.
A full coverage index could be considered as every locally optimal partition.
Given that there is no free lunch and it is impossible to know every solution, one can only ensure a full coverage index through an exhaustive search over the $2^m$ possible starting cut sets.
Consequently, in the approach taken here is to use a large but not exhaustive subset of the possible solutions using 10,000 solutions for the large networks studied in this paper.

\subsection{Measuring the quality of relationships} \label{sec:expansion}
Given a query of vertices, the relatedness to other vertexes in a network is quantifiable by the fraction of times they are clustered with the query set, given the set of high quality partitions.
Formally, this can be expressed in terms of the \textit{expansion score} of a given vertex,
\begin{equation} \label{eq:mu_score}
\mu_i(S) = \frac{1}{|\mathcal{P}| |S - i|} \sum_{P \in \mathcal{P}} \sum_{j \in S - i} \delta(c^{P}_{i}, c^{P}_{j}),
\end{equation}
where $S$ denotes a query set, $P$ is a given partition in the space of all high quality partitions $\mathcal{P}$, $c^{P}_{i}$ indicates the partition vertex $i$ is contained in within partition $P$ and $\delta(u, v)$ is the Dirac delta function that equals 1 if vertex $i$ and $j$ are in the same partition and $0$ otherwise.
Borrowing the terminology of fuzzy logic \cite{zimmermann2001fuzzy}, \textit{$\mu_i(S)$} can be considered a membership function and we can interpret this as a measure of the \textit{possibility} for which a given vertex belongs to the query set, given a set of partitions.
Where $\mu_i(S) = 1$ the partition space indicates that a given vertex is always partitioned in the same group as the query set.
In the case $\mu_i(S) = 0$ the vertex $i$ never appears in the same cluster as any vertex in the query set.

The subtraction of the vertex from the query set ($S - i$) allows an unbiased score for vertices within the query set.
This allows us to define a vector, $\mu(S)$ for all vertices in the network, including those in $S$.

\section{Results}
\subsection{Cross-validation method}
\label{sec:cross_validation}
In this work we are presented with a problem of a small number of labels for true positive cluster information.
The cross validation procedure we devise is described as follows and depends on the size of the community and the number of initial seed labels being used.
For this work we would like to capture binary classification  performance, \textit{true positives (tp), true negatives (tn), false positives (fp)} and \textit{false negatives (fn)}, on our datasets.
As the seed label sets can be as small as 3 vertices, exhaustive cross validation is not possible for all labelling schemes.
Consequently, cross validation is either conducted on an exhaustive set of all possible $\binom{|L|}{s}$ unique labellings or 120 seed queries sampled without replacement, where $L$ is the set of gold standard true labels and $s$ is the size of the randomly selected seed sets.
It should therefore be noted that presented receiver operator characteristic (ROC) scores are, therefore, dependent on community sizes.

\subsection{Synthetic networks}
In this section we test the method on a number benchmark networks constructed with a known, ground-truth community structure.
To evaluate how our method performs we demonstrate results against two benchmark networks the conventionally used LFR benchmark \cite{lfr} and a newer form of benchmark for community detection algorithms developed in previous studies \cite{cigram}.
Both these benchmarks allow for a configurable level of overlapping and mixing between communities.

\subsubsection{LFR benchmarks}

\subsubsection{CiGRAM benchmarks}

\subsection{Real networks}
In order to test the performance of the semi-supervised classification on real-world data we present our findings on example networks with known metadata communities.
All datasets taken use the largest single connected component sub-graph.

\subsubsection{Dataset descriptions}
\label{sec:real_network_descs}
The real networks used are listed as follows:
\begin{itemize}
 \item \textbf{EU emails dataset (EU emails)} This anonymised dataset is taken from the SNAP database \cite{snap} and contains $986$ nodes and $16,687$ edges representing emails between individuals.
 The metadata community labels represent different departments within the organisation.
 In total there are 42 communities, 39 of which contain at least 3 nodes.

 \item \textbf{Yeast protein-protein interaction network (Yeast PPI)} \cite{yeast_ppi}
 This dataset is a collection of recorded binary interactions between proteins collected with high-throughput yeast-2-hybrid assays.
 The metadata used are known, experimentally validated protein complexes from \cite{yeast_ppi_complexes}.
 The network contains 6222 nodes in the largest connected component, with 22,3868 edges.
 There are 409 experimentally validated protein complexes, 236 of which contain 3 or more nodes.
 The protein complexes are typically very small in terms of number of proteins with only 90\% of the complexes containing less than 10 proteins and only 2 complexes containing 50 or more proteins.

\end{itemize}

\begin{figure}[ht]
     \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/eu_roc_scores.eps}
        \caption{EU email departments}
    \end{subfigure}

    \centering
    \begin{subfigure}[b]{\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/yeast_ppi_roc_scores.eps}
        \caption{Yeast PPI protein complexes}
    \end{subfigure}

    \caption{Mean area under RO curve (AUC) scores from cross-validation performed on Metadata communities for networks described in Section \ref{sec:real_network_descs}.
    Dashed line indicates an AUC score of 0.5 (random chance).
    Communities are ordered by size.
    Error bars indicate standard deviation.
    }
    \label{fig:real_network_results}
\end{figure}

\begin{figure}[ht]
     \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/eu_email_nodewise_roc.eps}
        \caption{EU email departments (986 nodes)}
    \end{subfigure}

    \centering
    \begin{subfigure}[b]{0.8\textwidth}
        \centering
        \includegraphics[width=\textwidth]{images/yeast_ppi_nodewise_roc.eps}
        \caption{Yeast PPI protein complexes (1628 nodes)}
    \end{subfigure}

    \caption{Receiver Operator Characteristic curves for node communities.
    Dashed line indicates an AUC score of 0.5 (random chance).
    Represents mean, shaded area indicates standard deviation.
    }
    \label{fig:real_network_nodwise_classifiers}
\end{figure}

We tested the method on each real network described in section \ref{sec:real_network_descs}.
Figure \ref{fig:real_network_results} shows the mean ROC scores for each community in the relevant networks, organised by size of community at increasing numbers levels of query seed nodes.
On the EU emails and Yeast PPI dataasets, for all communities tested with 3 or more nodes, mean AUC scores calculated with the cross validation method described in section \ref{sec:cross_validation} were above 0.6.
There appeared to be no statistically significant improvements to using more than 3 seed nodes.

The classification for individual nodes is presented in Figure \ref{fig:real_network_nodwise_classifiers}.
Here, binary classification is performed on each node for which community data is available.
The $mu_i({i})$ score is used as a binary classifier.
For the EU email and Yeast PPI the average ROC AUC score to classify node membership inside communities is 0.9 and 0.93, respectively.

\section{Discussion}
The semi-supervised method for vertex classification presented in this work has shown to have good results on both synthetic benchmarks and real-world datasets.
Interestingly, this method is capable of correctly classifying communities with only a small number of seed query vertexes.
These results show that the community query method could be used as a powerful exploratory tool in network analysis.

The fact that the method is able to uncover small protein complexes seems to contradict the principle that modularity maximisation algorithms have a resolution limit \cite{}.
This may be due to the fact that
We do note that, where communities are very small, any approach will extremely sensitive to false positive and false negative results.
This should be considered when using this method as an exploratory tool.

The results also appear to be highly tolerant to a small number of seed nodes.
This is interesting as in most sampled cases the relevant nodes are unlikely to be direct neighbours.
From the perspective of exploratory study, this implies that a small number of query vertices can be used to find potentially related vertices.

This allows the use of a single node to find related vertices, in real networks the results appeared to have a very good level of accuracy with average AUC of ROC curves above $0.9$.
In a practical context, however, this should not be interpreted as uncovering the community structure as this includes many overlapping communities for which the node is a member.

\section{Related work}
\label{sec:related_work}

This work relates very strongly to the idea of local community detection, more specifically the idea of \textit{seed set expansion}.
Here, a given seed set is created a random walks are analysed to find clearly related communities of vertices.
One of the most common approaches to finding related vertices in a network is the random walk with restart (RWR) \cite{can2005analysis, kohler2008walking}.
This approach has been applied in fields as diverse as recommender systems and the detection of potential drug targets \cite{chen2012drug}.
In RWR the relatedness of any pair of vertices can be seen as the probability of a particle traversing the graph starting at a given vertex and ending at another.
The restart aspect of the random walk can be thought of as the probability of the walker teleporting back to the start vertex with some none zero probability. 
The higher the probability of the walker ending up at a given vertex, the more likely it is that the two vertices are related.

Conceptually, RWR is very similar to the method presented in this paper given that the user has a given query.
One can thing of the RWR probability as analogous to the value of $\mu_i(S)$ presented above.
However, the RWR value is based only on a single vertex as a query set where the approach presented in this work requires many vertices associated with a given label for it to be readily applicable.

Many existing method are based on the idea of a locally dense subgraph containing \textit{all query nodes} \cite{}.
In contrast, the query approach presented here does not require the queries to be a self contained sub-graph.
Indeed, queries can contain spurious nodes that are topologically distinct from one another - the result is that the either $q(S)$ score for the query will be very low and insignificant, or the spurious nodes will be ignored in the final query set.
In user facing domains it is highly likely that very large query sets do not form isolated topologies.
With Conventional methods some ``cleaning up'' of the underlying queries is often required to gather any meaningful expansion.

Whilst modularity maximisation is used for the set of global partitions, this approach is distinct from local modularity based approaches \cite{}.
A limitation of this approach compared with localised methods is that the entire dataset is required.
However, the objective is somewhat different as the approach presented here relies on high quality meta-data labels for queries.
In this sense, the approach should be considered closer to semi-supervised \textit{classification} than unsupervised \textit{clustering}.

In the field of community detection, a number of very recent articles have focused on using metadata to improve the results of community detection approaches.

%TODO: Discuss citations of metadata based community detection - Newman-Clauset, Jure Lesovec, other citations in newman paper.

These algorithms, however, are distinct from the approach taken here as the metadata is not used in the module discovery process.
Furthermore, the results in this work attempt to explicitly label unlabelled data and only require a relatively small number of labels to operate in such a fashion.
In contrast,  the recent approach by Newman and Clauset \cite{}, for example, uses examples in which practically the entire network contains labels which is less useful from the perspective of label discovery.
However, these methods are vastly superior to the work presented here when considering the research question of whether a labelling scheme (such as demography in a social network) accurately describes the structure of the network.

\section{Conclusions}
This paper has presented a novel approach to semi-supervised community detection utilising a consensus of high scoring partitions computed with the popular modularity maximisation approach.
Previously the glassy search space of this optimisation algorithm has been seen as a major limitation of the approach.
However, in this work we consider each locally optimal partition to be information regarding the true multi-class labels that are likely present in real networks.
As the algorithm is trivial to run in a distributed manner, this approach can be applied to relatively large graphs.
Further research can be conducted into this approach with alternative quality functions to modularity that do not suffer the same limitations in terms of a resolution limit.

However, this approach requires the community landscape to contain many local maxima, a property likely shared by many real networks.
Similarly, the method presented here requires both some labelled data and the labels to be represented well within the topology of the underlying network.
The approach presented here differs from other ensemble approaches in that the objective is to provide a probabilistic framework for label classification.
This approach performs extremely well on both synthetically generated networks and real-world ground truth communities with relatively small sets of labels.

% Furthermore, we extended the use of this framework to allow quality measurements of selected labellings and similarity comparrisons between data.

\section*{Acknowledgements}
We are grateful for access to the University of Nottingham High Performance Computing Facility for supporting this work.
This work was supported by the Biotechnology and Biological Sciences Research Council grant BB/L013940/1.

\bibliographystyle{IEEEtran} 
\bibliography{references}

% \nocite{*}
\end{document}

### 2018-03-06 cluster_query_tool/experiments/__init__.py

@@ -1,0 +1,41 @@
+from scipy.special import binom
+import itertools
+
+
+def unique_sampler(node_set, sample_size, max_samples=120):
+    """
+    For sampling random query sets of a given size.
+
+    The node set size (e.g. true positives) limits the maximum number of samples to n choose k
+    where n is the node set size and k is the size of the sample
+
+    we want up to max_samples unique sets to be used as random starting labels
+
+    :param node_set: Set of nodes to sample from
+    :param sample_size: How many nodes to sample
+    :param max_samples: Maximum number of samples
+    :return:
+    """
+    sample_sets = set()
+
+    # maximum number of samples
+    sspace = binom(len(node_set), sample_size)
+    if sspace > max_samples:
+
+        if sspace > max_samples * 2:
+            # problem with this loop is when max_samples is close to n choose k
+            while len(sample_sets) < max_samples:
+                samp = tuple(sorted(np.random.choice(node_set, sample_size, replace=False)))
+                sample_sets.add(samp)
+        else:
+            # Generate max_samples, unique random numbers sampling without replacement from possible combinations
+            # Faster than above loop in case where n choose k is close to max_samples
+            sp = np.random.choice(range(int(binom(len(node_set), sample_size))), max_samples, replace=False)
+            poss = list(itertools.combinations(node_set, sample_size))
+            for s in sp:
+                sample_sets.add(poss[s])
+
+    else:
+        sample_sets = set(itertools.combinations(node_set, sample_size))
+
+    return sample_sets

### 2018-03-06 cluster_query_tool/experiments/lfr.py

@@ -1,0 +1,48 @@
+from cigram import lfr_benchmark_graph
+from cluster_query_tool.louvain_consensus import mu_ivector
+from cluster_query_tool.indexer import get_index
+from cluster_query_tool.experiments import unique_sampler
+from sklearn.metrics import roc_auc_score, average_precision_score
+
+
+def gen_network_index(params):
+    """
+
+    :param params:
+    :return: partitions - ensemble of network partitions
+    """
+    graph, communities = lfr_benchmark_graph(**params)
+    # Partitions are cached
+    partitions = get_index(graph)
+    return partitions
+
+
+def auc_scores(gparams, partitions, seed_size=3, max_samples=120):
+    """
+
+    :param graph:
+    :param comms:
+    :param partitions:
+    :param seed_size:
+    :param max_samples:
+    :return:
+    """
+
+    graph, comms = lfr_benchmark_graph(**gparams)
+    auc_scores = dict()
+    app_scores = dict()
+
+    for c in comms:
+        for cs in unique_sampler(comms[c], seed_size, max_samples=max_samples):
+            vec, key = mu_ivector(graph, partitions, cs)
+            inc = lambda x: 1 if x in comms[c] else 0
+            y_true = [inc(x) for x in graph.nodes() if x not in cs]
+            y_score = [vec[key[x]] for x in graph.nodes() if x not in cs]
+
+            auc_scores[c].append(roc_auc_score(y_true, y_score))
+            app_scores[c].append(average_precision_score(y_true, y_score))
+
+
+def sampler(seed, num_jobs, **kwargs):
+    """"""
+    Parallel(num_jobs=num_jobs)

### 2018-03-06 cluster_query_tool/indexer.py

@@ -1,0 +1,113 @@
+"""
+Create and save a partition space index for the data
+"""
+from cluster_query_tool.louvain_consensus import gen_local_optima_community, partition_to_cut_set
+import random
+from multiprocessing import cpu_count
+import json
+import os
+from joblib import Parallel, delayed
+import networkx as nx
+
+
+def _try_int(num):
+    """
+    Can the value be parsed as an int?
+    :param num: any type
+    :return: Boolean
+    """
+    try:
+        int(num)
+    except ValueError:
+        return False
+
+    return True
+
+
+def get_index(graph, space_sample_size="medium", seed=1, num_procs=cpu_count(), use_cache=True):
+    """
+    Generate a partition space index for a given network
+    :param graph: networkx graph object (make sure name is set for caching)
+    :param space_sample_size: can be string high (10,000 samples), medium (2000 samples) or low (100 samples) or int of
+    samples
+    :param seed:
+    :param num_procs:
+    :param use_cache: cache result to disk
+    :return:
+    """
+    # TODO: change the actual values of these numbers to something more solid
+    if space_sample_size == "low":
+        space_sample_size = 100
+    elif space_sample_size == "medium":
+        space_sample_size = 2000
+    elif space_sample_size == "high":
+        space_sample_size = 10000
+    elif not _try_int(space_sample_size):
+        space_sample_size = 2000
+
+    if not os.path.exists(".ctq_cache"):
+        os.mkdir(".ctq_cache")
+
+    space_sample_size = int(space_sample_size)
+    # cache_result
+    cache_location = os.path.join(".ctq_cache", "get_index_{0}_{1}_{2}.json".format(seed,
+                                                                                    space_sample_size, graph.name))
+
+    if use_cache and os.path.exists(cache_location):
+
+        try:
+            with open(cache_location) as cache:
+                result = json.load(cache)
+            return result
+        except json.JSONDecodeError:
+            pass
+
+    result = gen_sample_sets(graph, num_samples=space_sample_size, num_procs=num_procs, seed=seed)
+
+    if use_cache:
+        with open(cache_location, "w+") as cache:
+            json.dump(result, cache)
+        
+    return result
+
+
+def partition_from_cut(graph, edge_set):
+    """
+    Cut out connected components
+    """
+    graph.remove_edges_from(edge_set)
+    partition = []
[…]

### 2018-03-06 cluster_query_tool/louvain.py

@@ -1,0 +1,513 @@
+#!/usr/bin/python
+# -*- coding: utf-8 -*-
+"""
+This module implements community detection.
+"""
+__all__ = ["partition_at_level", "modularity", "best_partition", "generate_dendogram", "induced_graph"]
+__author__ = """Thomas Aynaud (thomas.aynaud@lip6.fr)"""
+#    Copyright (C) 2009 by
+#    Thomas Aynaud <thomas.aynaud@lip6.fr>
+#    All rights reserved.
+#    BSD license.
+
+__PASS_MAX = -1
+__MIN = 0.0000001
+
+import networkx as nx
+import types
+import array
+
+
+def partition_at_level(dendogram, level) :
+    """Return the partition of the nodes at the given level
+
+    A dendogram is a tree and each level is a partition of the graph nodes.
+    Level 0 is the first partition, which contains the smallest communities, and the best is len(dendogram) - 1.
+    The higher the level is, the bigger are the communities
+
+    Parameters
+    ----------
+    dendogram : list of dict
+       a list of partitions, ie dictionnaries where keys of the i+1 are the values of the i.
+    level : int
+       the level which belongs to [0..len(dendogram)-1]
+
+    Returns
+    -------
+    partition : dictionnary
+       A dictionary where keys are the nodes and the values are the set it belongs to
+
+    Raises
+    ------
+    KeyError
+       If the dendogram is not well formed or the level is too high
+
+    See Also
+    --------
+    best_partition which directly combines partition_at_level and generate_dendogram to obtain the partition of highest modularity
+
+    Examples
+    --------
+    >>> G=nx.erdos_renyi_graph(100, 0.01)
+    >>> dendo = generate_dendogram(G)
+    >>> for level in range(len(dendo) - 1) :
+    >>>     print( "partition at level", level, "is", partition_at_level(dendo, level)
+    """
+    partition = dendogram[0].copy()
+    for index in range(1, level + 1) :
+        for node, community in partition.items() :
+            partition[node] = dendogram[index][community]
+    return partition
+
+
+def modularity(partition, graph) :
+    """Compute the modularity of a partition of a graph
+
+    Parameters
+    ----------
+    partition : dict
+       the partition of the nodes, i.e a dictionary where keys are their nodes and values the communities
+    graph : networkx.Graph
+       the networkx graph which is decomposed
+
+    Returns
+    -------
+    modularity : float
+       The modularity
+
[…]

### 2018-03-06 cluster_query_tool/louvain_consensus.py

@@ -1,0 +1,123 @@
+from __future__ import division
+from . import louvain
+import networkx as nx
+import random
+import numpy as np
+
+
+def modularity(graph, part):
+    """
+    Return the newman modularity of graph graph
+    Optional parameter part, is a partition of a graph
+    """
+    partition = dict()
+    for k, com in enumerate(part):
+        for node in com:
+            partition[node] = k
+
+    return louvain.modularity(partition, graph)
+
+
+def create_partition_from_edge_set(graph, edge_set, parition_nodes_format=False):
+    """
+    Cut out connected components
+    """
+    graph.remove_edges_from(edge_set)
+    partition = {}
+    partition_map = {}
+    for i, cc in enumerate(nx.connected_components(graph)):
+        partition[i] = cc
+        for node in cc:
+            partition_map[node] = i
+
+    graph.add_edges_from(edge_set)
+    if parition_nodes_format:
+        return partition
+
+    return partition_map
+
+
+def partition_to_cut_set(graph, partition):
+    """
+    Partition in {node:community} format
+    Fast
+    # Returns a sorted tuple of edge tuples, hashable
+    """
+    return tuple(sorted(set([edge for edge in graph.edges() if partition[edge[0]] != partition[edge[1]]])))
+
+
+def gen_local_optima_community(graph):
+    # The possible space of communities is huge!
+    sample = random.sample(graph.edges(), random.randint(1, graph.number_of_edges()))
+    # convert to partition
+    start_partition = create_partition_from_edge_set(graph, sample)
+    local_optima = louvain.best_partition(graph, partition=start_partition)
+
+    return start_partition, local_optima
+
+
+def mu_iscore(nodes, partitions, query_nodes):
+    """
+    
+    """
+    query_set = set(query_nodes)
+    qs = 0
+    muscore = dict([(n, 0) for n in nodes])
+    
+    for partition in partitions:
+        best = max([(len(query_set.intersection(set(cluster))), cluster) for cluster in partition], key=lambda x: x[0])
+
+        qs += 1.0/(len(query_set) - 1) * (best[0] - 1)
+        
+        for n in best[1]:
+            if n in muscore and best[0] > 0:
+                muscore[n] += 1.0/len(partitions)
+    
+    qs *= 1.0/len(partitions)
+
+    return muscore
+
+
+def mu_ivector(graph, partitions, query_nodes):
+    """
[…]

### 2018-03-06 setup.py

@@ -1,0 +1,26 @@
+from setuptools import setup, find_packages
+
+
+with open('requirements.txt') as f:
+    requirements = f.read().splitlines()
+
+
+long_description = '''
+'''
+
+setup(
+    name="cqt",
+    version="0.0.1",
+    description="Cluster query tool for complex networks",
+    long_description=long_description,
+    zip_safe=False,
+    author="James Gilbert",
+    install_requires=requirements,
+    author_email="jamie.gilbert@azimov.co.uk",
+    license="GPL",
+    entry_points={},
+    url="https://github.com/azimov/cluster_query_tool",
+    include_package_data=True,
+    packages=find_packages(),
+    project_urls=dict(),
+)

### 2018-03-06 article/article.tex
changes to article

@@
 \doublespacing
-
+\DeclareMathOperator*{\argmax}{argmax}
 %opening
@@
 When no possible moves result in an increase in modularity the algorithm has found a local optima and stops.
-Whilst, in principle, the found local optima should have a high modularity score this is not guaranteed.
-Consequently, the process here rejects any solutions if the value of modularity is not significantly higher than the distribution of starting partitions.
-This is achieved by means of a standard $z$-test, formally the probability of generating a random partition with a modularity score $Q$ as high as observed as a result of the Louvain optimisation must be $p < 0.01$.
-Furthermore, only unique solutions are accepted.
 
@@
 Formally, this can be expressed in terms of the \textit{expansion score} of a given vertex,
+% \begin{equation} \label{eq:mu_score}
+% \mu_i(S) = \frac{1}{|\mathcal{P}| |S - i|} \sum_{P \in \mathcal{P}} \sum_{j \in S - i} \delta(c^{P}_{i}, c^{P}_{j}),
+% \end{equation}
 \begin{equation} \label{eq:mu_score}
-\mu_i(S) = \frac{1}{|\mathcal{P}| |S - i|} \sum_{P \in \mathcal{P}} \sum_{j \in S - i} \delta(c^{P}_{i}, c^{P}_{j}),
+\mu_i(S) = \frac{1}{|\mathcal{P}|} \sum_{P \in \mathcal{P}} \delta(c^{P}_i, c^{P}_S),
 \end{equation}
-where $S$ denotes a query set, $P$ is a given partition in the space of all high quality partitions $\mathcal{P}$, $c^{P}_{i}$ indicates the partition vertex $i$ is contained in within partition $P$ and $\delta(u, v)$ is the Dirac delta function that equals 1 if vertex $i$ and $j$ are in the same partition and $0$ otherwise.
+where $S$ denotes a query set, $P$ is a given partition in the space of all high quality partitions $\mathcal{P}$, $c^{P}_{i}$ indicates the partition vertex $i$ is contained in within partition $P$ and
+$\delta(u, v)$ is the Dirac delta function that equals 1 if are the same cluster and $0$ otherwise, where $c^{P}_S$ is given by,
+\begin{equation}
+ c^{P}_S = \argmax_{C \in P} |C \cap S|,
+\end{equation}
+or the largest intersecting cluster with the query set, in partition $P$.
+Using the largest intersecting community with $S$ is both computationally favourable for computing $mu_i$ for all $i$ in $V$ and allows the query set to contain potentially suprious query nodes.
 Borrowing the terminology of fuzzy logic \cite{zimmermann2001fuzzy}, \textit{$\mu_i(S)$} can be considered a membership function and we can interpret this as a measure of the \textit{possibility} for which a given vertex belongs to the query set, given a set of partitions.
 Where $\mu_i(S) = 1$ the partition space indicates that a given vertex is always partitioned in the same group as the query set.
-In the case $\mu_i(S) = 0$ the vertex $i$ never appears in the same cluster as any vertex in the query set.
+In the case $\mu_i(S) = 0$ the vertex $i$ never appears in the same cluster as the largest query set.
 

### 2018-03-06 cluster_query_tool/louvain_consensus.py

@@ -113,11 +113,11 @@ def mu_ivector_n(graph, partitions, query_nodes):
     key = dict([(k, i) for i, k in enumerate(sorted(graph.nodes()))])
 
     for partition in partitions:
-        best = [(len(query_set.intersection(set(cluster))), cluster) for cluster in partition]
-
-        for s, cluster in best:
-            for i in cluster:
-                muscore[key[i]] += s
+        for cluster in partitions:
+            s = len(query_set.intersection(cluster))
+            if s > 0:
+                for i in cluster:
+                    muscore[key[i]] += 1/s
 
     # Normalise result
     return muscore * 1 / len(partitions), key

### 2018-03-16 article/article.tex
changed job queue

@@
 
-The number and size of communities is, generally, not known \textit{a priori}, and the problem has been shown to be NP-hard.
+The number and size of communities is, generally, not known \textit{a priori}, and the problem has been shown to be NP-hard \cite{npHardModularity}.
 The work of Good \textit{et al.} \cite{good2010performance} recently highlighted that the popular modularity maximisation algorithm has a highly ``glassy'' search space.
@@
 
-Though the methods presented here can be applied to any complex network, the focus of this work is biological in nature; characterising the function of all genes within an organism is a problem critical to systems biology \cite{}.
+One example of community detection that has gained significant interest is in systems biology \cite{}.
+A core goal here is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network.
 In many situations, only the role of a small number of genes is known, with much of the annotation for a given organism being computed through naive homology information that ignores the role of a gene within a wider context.

### 2018-03-16 experiments/lfr_nooverlap.py

@@ -100,7 +100,7 @@ python experiments/lfr_nooverlap.py auc_compute {n} {mu:.2f} $JOB $RESULTS_DIR/{
     script_settings = dict(
         walltime="walltime={}".format(walltime),
         request="select=1:ncpus=16:mem=16gb",
-        queue="HPCA-02856-EFR",
+        queue="HPCA-01839-EFR",
         workdir="$HOME/repos/cluster_query_tool",
         results_file=results_file,
         n=n

### 2018-03-16 experiments/lfr_nooverlap.py
Fixed data storage

@@ -62,15 +62,13 @@ def auc_compute(seed, n, mu, results_file):
     graph, communities, index = get_benchmark(pset)
     results = []
     for c, comm in communities.items():
-        results[str(c)] = {}
         for seed_size in _seed_sizes:
-            results[str(c)][str(seed_size)] = []
             if len(comm) > seed_size:
                 # Seed of AUC scores for node this size
                 auc_s = get_auc_scores_community(seed_size, comm, graph, index)
-                results[str(c)][str(seed_size)].append([len(comm), np.mean(auc_s), np.std(auc_s)])
+                results.append([str(c), str(seed_size), len(comm), np.mean(auc_s), np.std(auc_s)])
 
-    save_results(results, results_file, mu, seed)
+    save_results(results, results_file, mu)
 
 
 @click.command()
@@ -78,8 +76,9 @@ def auc_compute(seed, n, mu, results_file):
 @click.option("--mu_steps", default=10)
 @click.option("--network_samples", default=10)
 @click.option("--walltime", default="01:30:00")
-@click.option("--execucte/--no_exec", default=False)
-def run_jobs(n, mu_steps, network_samples, walltime, execucte):
+@click.option("--execute/--no_exec", default=False)
+@click.option("--queue", default="HPCA-01839-EFR")
+def run_jobs(n, mu_steps, network_samples, walltime, execucte, queue):
     script_template = """#!/bin/bash
 #PBS -k oe
 #PBS -l {request}
@@ -100,7 +99,7 @@ python experiments/lfr_nooverlap.py auc_compute {n} {mu:.2f} $JOB $RESULTS_DIR/{
     script_settings = dict(
         walltime="walltime={}".format(walltime),
         request="select=1:ncpus=16:mem=16gb",
-        queue="HPCA-01839-EFR",
+        queue=queue,
         workdir="$HOME/repos/cluster_query_tool",
         results_file=results_file,
         n=n

### 2018-03-16 experiments/lfr_nooverlap.py
Fixed data storage

@@ -66,7 +66,7 @@ def auc_compute(seed, n, mu, results_file):
             if len(comm) > seed_size:
                 # Seed of AUC scores for node this size
                 auc_s = get_auc_scores_community(seed_size, comm, graph, index)
-                results.append([str(c), str(seed_size), len(comm), np.mean(auc_s), np.std(auc_s)])
+                results.append([seed, c, seed_size, len(comm), np.mean(auc_s), np.std(auc_s)])
 
     save_results(results, results_file, mu)
 

### 2018-03-16 experiments/lfr_nooverlap.py
Job script error/output reporting tidied

@@ -84,6 +84,11 @@ def run_jobs(n, mu_steps, network_samples, walltime, execucte, queue):
 #PBS -l {request}
 #PBS -l {walltime}
 #PBS -P {queue}
+#PBS -e $HOME/ctq_run/error/error_{n}_{mu}.txt
+#PBS -o $HOME/ctq_run/ouput/output_{n}_{mu}.txt
+
+mkdir -p $HOME/ctq_run/output/
+mkdir -p $HOME/ctq_run/error/
 
 WORK_DIR={workdir}
 RESULTS_DIR=

### 2018-03-16 experiments/lfr_nooverlap.py
Minor bug in job script command

@@ -78,7 +78,7 @@ def auc_compute(seed, n, mu, results_file):
 @click.option("--walltime", default="01:30:00")
 @click.option("--execute/--no_exec", default=False)
 @click.option("--queue", default="HPCA-01839-EFR")
-def run_jobs(n, mu_steps, network_samples, walltime, execucte, queue):
+def run_jobs(n, mu_steps, network_samples, walltime, execute, queue):
     script_template = """#!/bin/bash
 #PBS -k oe
 #PBS -l {request}
@@ -133,7 +133,7 @@ python experiments/lfr_nooverlap.py auc_compute {n} {mu:.2f} $JOB $RESULTS_DIR/{
         params['command_file'] = command_file_path
         command = cmd_template.format(**params)
         click.echo(command)
-        if execucte:
+        if execute:
             call(command.split())
 
 

### 2018-03-16 experiments/lfr_nooverlap.py
Minor bug in job script command

@@ -87,9 +87,6 @@ def run_jobs(n, mu_steps, network_samples, walltime, execute, queue):
 #PBS -e $HOME/ctq_run/error/error_{n}_{mu}.txt
 #PBS -o $HOME/ctq_run/ouput/output_{n}_{mu}.txt
 
-mkdir -p $HOME/ctq_run/output/
-mkdir -p $HOME/ctq_run/error/
-
 WORK_DIR={workdir}
 RESULTS_DIR=
 JOB=$PBS_ARRAY_INDEX

### 2018-03-16 experiments/lfr_nooverlap.py
More job script bugs

@@ -84,11 +84,9 @@ def run_jobs(n, mu_steps, network_samples, walltime, execute, queue):
 #PBS -l {request}
 #PBS -l {walltime}
 #PBS -P {queue}
-#PBS -e $HOME/ctq_run/error/error_{n}_{mu}.txt
-#PBS -o $HOME/ctq_run/ouput/output_{n}_{mu}.txt
 
 WORK_DIR={workdir}
-RESULTS_DIR=
+RESULTS_DIR=$WORK_DIR/hpc_results
 JOB=$PBS_ARRAY_INDEX
 
 mkdir -p $RESULTS_DIR
@@ -110,7 +108,9 @@ python experiments/lfr_nooverlap.py auc_compute {n} {mu:.2f} $JOB $RESULTS_DIR/{
     cmd_opt = dict(
         options="",
         jcount=network_samples,
-        n=n
+        n=n,
+        e="$HOME/ctq_run/error/error_{n}.txt".format(n),
+        o="$HOME/ctq_run/output/output_{n}.txt".format(n),
     )
     cmd_template = "qsub {options} -J 1-{jcount} {command_file}"
 

### 2018-03-16 experiments/lfr_nooverlap.py
More job script bugs

@@ -109,8 +109,8 @@ python experiments/lfr_nooverlap.py auc_compute {n} {mu:.2f} $JOB $RESULTS_DIR/{
         options="",
         jcount=network_samples,
         n=n,
-        e="$HOME/ctq_run/error/error_{n}.txt".format(n),
-        o="$HOME/ctq_run/output/output_{n}.txt".format(n),
+        e="$HOME/ctq_run/error/error_{}.txt".format(n),
+        o="$HOME/ctq_run/output/output_{}.txt".format(n),
     )
     cmd_template = "qsub {options} -J 1-{jcount} {command_file}"
 

### 2018-03-16 article/article.tex
More job script bugs

@@
 
-One example of community detection that has gained significant interest is in systems biology \cite{}.
-A core goal here is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network.
+The use of community detection is widespread.
+For example, core goal in systems biology is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network \cite{}.
 In many situations, only the role of a small number of genes is known, with much of the annotation for a given organism being computed through naive homology information that ignores the role of a gene within a wider context.

### 2018-03-16 experiments/lfr_nooverlap.py

@@ -66,9 +66,9 @@ def auc_compute(seed, n, mu, results_file):
             if len(comm) > seed_size:
                 # Seed of AUC scores for node this size
                 auc_s = get_auc_scores_community(seed_size, comm, graph, index)
-                results.append([seed, c, seed_size, len(comm), np.mean(auc_s), np.std(auc_s)])
+                results.append([c, seed_size, len(comm), np.mean(auc_s), np.std(auc_s)])
 
-    save_results(results, results_file, mu)
+    save_results(results, results_file, mu, seed)
 
 
 @click.command()

### 2018-03-26 article/article.tex
Added boilerplate to article. But looks like I need to redo the analysis

@@
 \subsubsection{LFR benchmarks}
+In this section we test the area under the ROC curve (AUC) scores for networks synthetically generated with the LFR benchmark.
+The community distribution is defined with a powerlaw coefficient of $-1.0$ and the degree distribution is defined with a powerlaw coefficient of $-2.0$.
+\textbf{Non-overlapping modules.} Figure \ref{fig:auc_no_overlap} represents tests on 100 networks with different randomly selected seed nodes.
+As one would expect, the prediction of the method drops off steeply where communities are less defined above a mixing coefficient of 0.6.
+Using larger seed sets also improves accuracy with some prediction of true communities being possible at extremely high levels of mixing.
+
+\begin{figure*}[ht]
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc.eps}
+        \caption{1000 nodes}
+    \end{subfigure}
+
+    \centering
+    \begin{subfigure}[b]{0.45\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc.eps}
+        \caption{5000 nodes}
+    \end{subfigure}
+    \caption{Non-overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
+     Data points represent mean auc scores for all communities on 100 sampled networks at varying mixing coefficients.
+     Error bars represent standard deviations.}
+\end{figure*}
 

### 2018-03-26 experiments/experiments.py

@@ -76,8 +76,8 @@ def unique_sampler(node_set, sample_size, max_samples=96):
 def roc_score_node(n, graph, index, node_comms):
     vec, key = mu_ivector(graph, index, [n])
     inc = lambda x: 1 if x in node_comms[n] else 0
-    y_true = [inc(x) for x in graph.nodes()]
-    y_score = [vec[key[x]] for x in graph.nodes()]
+    y_true = [inc(x) for x in graph.nodes() if x != n]
+    y_score = [vec[key[x]] for x in graph.nodes() if x != n]
 
     return roc_auc_score(y_true, y_score)
 
@@ -85,8 +85,8 @@ def roc_score_node(n, graph, index, node_comms):
 def roc_score_seed(seed_set, graph, index, comm):
     vec, key = mu_ivector(graph, index, seed_set)
     inc = lambda x: 1 if x in comm else 0
-    y_true = [inc(x) for x in graph.nodes()]
-    y_score = [vec[key[x]] for x in graph.nodes()]
+    y_true = [inc(x) for x in graph.nodes() if x not in seed_set]
+    y_score = [vec[key[x]] for x in graph.nodes() if x not in seed_set]
     return roc_auc_score(y_true, y_score)
 
 

### 2018-03-28 experiments/lfr_nooverlap.py
Handling plot of figures

@@ -86,14 +86,19 @@ python {_file} auc_compute {n} {mu:.2f} $JOB {results_folder}
         _file=__file__,
     )
 
+    opt_path = os.path.join(workdir, 'hpc_out', 'output_{}'.format(n))
+    err_path = os.path.join(workdir, 'hpc_out', 'error_{}'.format(n))
+
+    os.makedirs(os.path.join(workdir, 'hpc_out'), exist_ok=True)
+
     cmd_opt = dict(
         options="",
         jcount=network_samples,
         n=n,
-        e="$HOME/ctq_run/error/error_{}.txt".format(n),
-        o="$HOME/ctq_run/output/output_{}.txt".format(n),
+        e=err_path,
+        o=opt_path,
     )
-    cmd_template = "qsub {options} -J 1-{jcount} {command_file}"
+    cmd_template = "qsub {options} -J 1-{jcount} {command_file} -e {e} -o {o}"
 
     commands_path = os.path.abspath(os.path.join(os.path.dirname(__file__), 'job_scripts'))
     if not os.path.exists(commands_path):
@@ -109,12 +114,55 @@ python {_file} auc_compute {n} {mu:.2f} $JOB {results_folder}
             cmdfile.write(script)
 
         params = cmd_opt.copy()
-        params['mu'] = mu
         params['command_file'] = command_file_path
         command = cmd_template.format(**params)
         click.echo(command)
         if execute:
             call(command.split())
+
+
+@click.command()
+@click.argument("n")
+def gen_figure(n):
+    import json
+    from matplotlib import pyplot as plt
+    import glob
+    import pandas as pd
+    rows = []
+
+    for f in glob.glob("hpc_results/lfr_no_overlap_{}/*.json".format(n)):
+        with open(f) as jf:
+            rts = json.load(jf)
+            for row in rts:
+                rows.append(row)
+
+    df = pd.DataFrame(rows, columns=['n', 'mixing', 'seed', 'c', 'seed_size', 'comm', 'auc', 'auc_std'])
+
+    fig, ax = plt.subplots()
+    fig.set_dpi(90)
+    ax.set_ylabel("Mean AUC")
+    ax.set_xlabel("Mixing coefficient $\mu$")
+    ax.set_ylim(0.4, 1.01)
+    ax.set_xlim(0.0, 1.01)
+    x_vals = df['mixing'].unique()
+    x_vals.sort()
+
[…]

### 2018-03-28 experiments/lfr_overlap.py
Changes to overlap

@@ -86,14 +86,19 @@ python {file} auc_compute {n} {ol} $JOB {results_folder}
         file=os.path.abspath(__file__),
     )
 
+    opt_path = os.path.join(workdir, 'hpc_out', 'output_{}'.format(n))
+    err_path = os.path.join(workdir, 'hpc_out', 'error_{}'.format(n))
+
+    os.makedirs(os.path.join(workdir, 'hpc_out'), exist_ok=True)
+
     cmd_opt = dict(
         options="",
         jcount=network_samples,
         n=n,
-        e="$HOME/ctq_run/error/error_{}.txt".format(n),
-        o="$HOME/ctq_run/output/output_{}.txt".format(n),
+        e=err_path,
+        o=opt_path,
     )
-    cmd_template = "qsub {options} -J 1-{jcount} {command_file}"
+    cmd_template = "qsub {options} -J 1-{jcount} -e {e} -o {o} {command_file}"
 
     commands_path = os.path.abspath(os.path.join(os.path.dirname(__file__), 'job_scripts'))
     if not os.path.exists(commands_path):

### 2018-04-06 article/article.tex
Handling plot of figures
Added notebook for dblp

@@
-\documentclass[a4paper,10pt]{article}
+\listfiles
+\documentclass[manuscript, review, sigconf]{acmart}
 \usepackage[utf8]{inputenc}
-\usepackage{fullpage}
 \usepackage{color}
-\usepackage{authblk}
+
 \usepackage{listings}
@@
 \usepackage{amsmath}
-%PREPRINT/MANUSCRIPT OPTIONS
-\usepackage{setspace}
-\usepackage{lineno}
-\linenumbers
-\doublespacing
+
+\usepackage{booktabs} 
 \DeclareMathOperator*{\argmax}{argmax}
-%opening
 
-% \author{
-%     \IEEEauthorblockN{James Gilbert\IEEEauthorrefmark{1}, Nicole Pearcy\IEEEauthorrefmark{1}, Jamie Twycross\IEEEauthorrefmark{2}}
-%     \IEEEauthorblockA{\IEEEauthorrefmark{1}Synthetic Biology Research Centre, School of Life Sciences, University of Nottingham}
-%     \IEEEauthorblockA{\IEEEauthorrefmark{2}Intelligent Modelling and Analysis Group, School of Computer Science, University of Nottingham}
-% }
+\date{Received: date / Accepted: date}
 
@@
 
-\title{From clusters to queries: exploiting uncertainty in the modular landscape of complex networks}
+\title{From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks}
 
-%\titlerunning{Short form of title}        % if too long for running head
+\author{James P Gilbert}
+\affiliation{%
+  \institution{Synthetic biology research centre}
+  \streetaddress{University of Nottingham}
+  \city{Nottingham}
+  \country{United Kingdom}
+  \postcode{NG7 2RD}
+}
+\email{james.gilbert@nottingham.ac.uk}
 
-\author{James P Gilbert         \and
-	Jamie Twycross 		\and
-	John King
+\author{Jamie Twycross}
+\affiliation{%
+  \institution{School of Computer Science}
+  \streetaddress{University of Nottingham}
+  \city{Nottingham}
+  \country{United Kingdom}
+  \postcode{NG7 2RD}
 }
-\date{Received: date / Accepted: date}
+\email{jamie.twycross@nottingham.ac.uk}
 
-\maketitle
+\author{John King}
+\affiliation{%
+  \institution{School of Mathematical Sciences}
+  \streetaddress{University of Nottingham}
+  \city{Nottingham}
+  \country{United Kingdom}
+  \postcode{NG7 2RD}
+}
+\email{john.king@nottingham.ac.uk}
 
@@
 \end{abstract}
+
+\maketitle
 
@@
 \centering
- \includegraphics[width=0.7\textwidth]{images/search_space_3.png}
+ \includegraphics[width=0.48\textwidth]{images/search_space_3.png}
  \caption{
@@
     \centering
-    \begin{subfigure}[b]{0.45\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc.eps}
+        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc_1000.eps}
         \caption{1000 nodes}
     \end{subfigure}
-
+    \begin{subfigure}[b]{0.48\textwidth}
         \centering
-    \begin{subfigure}[b]{0.45\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc.eps}
+        \includegraphics[width=\textwidth]{images/lfr_binary_mo_overlap_auc_5000.eps}
         \caption{5000 nodes}
@@
 
-\begin{figure}[ht]
+\begin{figure*}
      \centering
-    \begin{subfigure}[b]{\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \centering
@@
     \end{subfigure}
-
-    \centering
-    \begin{subfigure}[b]{\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \centering
@@
     \end{subfigure}
-
     \caption{Mean area under RO curve (AUC) scores from cross-validation performed on Metadata communities for networks described in Section \ref{sec:real_network_descs}.
@@
     \label{fig:real_network_results}
-\end{figure}
+\end{figure*}
 
-\begin{figure}[ht]
+\begin{figure*}
     \centering
-    \begin{subfigure}[b]{0.8\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \centering
@@
     \end{subfigure}
-
-    \centering
-    \begin{subfigure}[b]{0.8\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \centering
@@
     \end{subfigure}
-
     \caption{Receiver Operator Characteristic curves for node communities.
@@
     \label{fig:real_network_nodwise_classifiers}
-\end{figure}
+\end{figure*}
 

### 2018-04-09 article/article.tex
Added mann-whitney u test for query set significance.

@@
 \listfiles
-\documentclass[manuscript, review, sigconf]{acmart}
+\documentclass[manuscript, proceedings]{acmart}
 \usepackage[utf8]{inputenc}
@@
  \caption{
- Modularity search space of the \textit{E. coli} metabolic network.
+ Modularity search space of an \textit{E. coli} metabolic network.
  Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
@@
 or the largest intersecting cluster with the query set, in partition $P$.
-Using the largest intersecting community with $S$ is both computationally favourable for computing $mu_i$ for all $i$ in $V$ and allows the query set to contain potentially suprious query nodes.
-Borrowing the terminology of fuzzy logic \cite{zimmermann2001fuzzy}, \textit{$\mu_i(S)$} can be considered a membership function and we can interpret this as a measure of the \textit{possibility} for which a given vertex belongs to the query set, given a set of partitions.
+Using the largest intersecting community with $S$ is both computationally favourable for computing $mu_i$ for all $i$ in $V$ and allows the query set to contain potentially spurious query nodes.
 Where $\mu_i(S) = 1$ the partition space indicates that a given vertex is always partitioned in the same group as the query set.
 In the case $\mu_i(S) = 0$ the vertex $i$ never appears in the same cluster as the largest query set.
+We define $\mu_i(S)$ for all vertices in the network, including those in $S$.
+In many cases, a query set will not be fully represented by the partitions found within the network, this is further elaborated in the following section.
 
-The subtraction of the vertex from the query set ($S - i$) allows an unbiased score for vertices within the query set.
-This allows us to define a vector, $\mu(S)$ for all vertices in the network, including those in $S$.
+\subsection{Statistically significant query sets}
+Naturally, not every label set will be of high quality or represented within the community structure of a network.
+This is established further in section \ref{sec:go_labels} which tests gene ontology terms (GO) on protein interaction networks.
+In this case, all the labels relate to the real function of the vertices, however, GO is a hierarchical system and many terms are extremely general.
+Furthermore, even for specific terms the network datasets will often not be well represented.
+A common approach with community detection and clustering (used for example in \cite{dekkers2013}) is to detect communities and find clusters containing significant GO terms.
+
+In this work, we would wish to use the community partition space, described above, to find highly related sets of vertices.
+For this we take the distribution, from Equation \ref{eq:mu_score} for a given query set.
+For a query set to be relevant it should be significantly more related than one would expect from a set of nodes selected at random within a network.
+
+Formally, given the partition space $\mathcal{P}$ and a query set $S$ we consider the distribution of quality scores as $\mu_i(S - i)$, for all $i$ in $S$.
+In order for $S$ to be a high quality query set, its value of internal vertices should be significantly higher than for external vertices.
+Formally, we assert that the distribution $\mu_i(S - i)$ should reject the null hypothesis that the mean is not significantly greater than $\mu_j(S)$ where $j \in S - V$, the set of vertices excluding those in the query set.
+For the purposes of this work we use the non-parametric Mann–Whitney $U$ test and reject the null hypothesis where $p < 0.01$.
+In section \ref{sec:go_labels} this is used to exclude less relevant GO terms.
 
@@
 In this section we test the method on a number benchmark networks constructed with a known, ground-truth community structure.
-To evaluate how our method performs we demonstrate results against two benchmark networks the conventionally used LFR benchmark \cite{lfr} and a newer form of benchmark for community detection algorithms developed in previous studies \cite{cigram}.
-Both these benchmarks allow for a configurable level of overlapping and mixing between communities.
-
-\subsubsection{LFR benchmarks}
-In this section we test the area under the ROC curve (AUC) scores for networks synthetically generated with the LFR benchmark.
+To evaluate how our method performs we demonstrate results against two benchmark networks the conventionally used LFR benchmark \cite{lfr} for community detection algorithms.
+We test the area under the ROC curve (AUC) scores for networks synthetically generated with the LFR benchmark.
 The community distribution is defined with a powerlaw coefficient of $-1.0$ and the degree distribution is defined with a powerlaw coefficient of $-2.0$.
@@
 
-\subsubsection{CiGRAM benchmarks}
-
 \subsection{Real networks}
@@
  There are 409 experimentally validated protein complexes, 236 of which contain 3 or more nodes.
- The protein complexes are typically very small in terms of number of proteins with only 90\% of the complexes containing less than 10 proteins and only 2 complexes containing 50 or more proteins.
+ The protein complexes are typically very small in terms of number of proteins with  90\% of the complexes containing less than 10 proteins and only 2 complexes containing 50 or more proteins.
 
@@
 For the EU email and Yeast PPI the average ROC AUC score to classify node membership inside communities is 0.9 and 0.93, respectively.
+
+\subsection{Gene ontology data}
+\label{sec:go_labels}
 

### 2018-04-09 cluster_query_tool/louvain_consensus.py

@@ -3,7 +3,7 @@ from . import louvain
 import networkx as nx
 import random
 import numpy as np
-
+from scipy.stats import mannwhitneyu
 
 def modularity(graph, part):
     """
@@ -58,21 +58,21 @@ def gen_local_optima_community(graph):
 
 def mu_iscore(nodes, partitions, query_nodes):
     """
-    
+
     """
     query_set = set(query_nodes)
     qs = 0
     muscore = dict([(n, 0) for n in nodes])
-    
+
     for partition in partitions:
         best = max([(len(query_set.intersection(set(cluster))), cluster) for cluster in partition], key=lambda x: x[0])
 
         qs += 1.0/(len(query_set) - 1) * (best[0] - 1)
-        
+
         for n in best[1]:
             if n in muscore and best[0] > 0:
                 muscore[n] += 1.0/len(partitions)
-    
+
     qs *= 1.0/len(partitions)
 
     return muscore
@@ -121,3 +121,21 @@ def mu_ivector_n(graph, partitions, query_nodes):
 
     # Normalise result
     return muscore * 1 / len(partitions), key
+
+
+def q_significance(graph, index, testset):
+    """
+    For a given query set, return the p value from a mann-whitney u test that the null hypothesis that the query nodes
+    could have been selected randomly from within the network.
+    :param graph:
+    :param index:
+    :param testset:
+    :return:
+    """
+    testset = set(testset)
+    vec, keys = mu_ivector(graph, index, testset)
+
+    network_dist = [vec[keys[x]] for x in keys if x not in testset]
+    seed_dist = [vec[keys[x]] for x in keys if x in testset]
+    u_score, pvalue = mannwhitneyu(network_dist, seed_dist)
+    return pvalue

### 2018-04-19 article/article.tex
MNinor article changes
Added an indexer for distributed louvain

@@
 Many algorithms exist to solve this problem, yet initial starting conditions or different optimisation strategies may result in conflicting results even when the same objective function is being maximised \cite{good2010performance}.
-In this paper, we develop an intuitive method to use the uncertainty amongst a high number of near optimal solutions to measure the overall quality of a given labelling scheme that can come from classes known \textit{a-priori} or clusters detected through other methods.
+In this paper, we develop an intuitive method to use the uncertainty amongst a high number of near optimal solutions to meaedsure the overall quality of a given labelling scheme that can come from classes known \textit{a-priori} or clusters detected through other methods.
 This approach also allows the expansion of labels to find potentially related vertices to an initial starting subset.
@@
 Formally, we assert that the distribution $\mu_i(S - i)$ should reject the null hypothesis that the mean is not significantly greater than $\mu_j(S)$ where $j \in S - V$, the set of vertices excluding those in the query set.
-For the purposes of this work we use the non-parametric Mann–Whitney $U$ test and reject the null hypothesis where $p < 0.01$.
+For the purposes of this work we use the non-parametric Mann–Whitney $U$ test and reject the null hypothesis where $p < 0.001$.
 In section \ref{sec:go_labels} this is used to exclude less relevant GO terms.

### 2018-04-19 cluster_query_tool/distributed_indexer.py

@@ -1,0 +1,172 @@
+import click
+import os
+import json
+import glob
+from hashlib import sha256
+from .indexer import partition_to_cut_set, partition_from_cut, dump
+from .louvain_consensus import gen_local_optima_community
+import random
+import networkx as nx
+
+
+def load_graph(path):
+    graph = nx.read_edgelist(path)
+    graph.name = os.path.basename(path)
+    return graph
+
+
+@click.command()
+@click.argument('graph_path')
+@click.argument('seed')
+@click.argument('n_jobs')
+@click.argument('results_folder')
+@click.option("--walltime", default="01:30:00")
+@click.option("--space_sample_size", default=2000)
+@click.option("--request", default="select=1:ncpus=1:mem=8gb")
+@click.option("--queue", default="HPCA-01839-EFR")
+def pbs_indexer(graph_path, seed, n_jobs, results_folder, walltime, request, space_sample_size, queue):
+    """
+    Generates space_sample_size starting cut sets and divides them in to n jobs to be scheduled
+
+    :param graph_path:
+    :param seed:
+    :param n_jobs:
+    :param results_folder:
+    :param walltime:
+    :param request:
+    :param space_sample_size:
+    :param queue:
+    :return:
+    """
+    random.seed(seed)
+    graph = load_graph(graph_path)
+
+    def random_cut_set():
+        cs = random.sample(graph.edges(), random.randint(1, graph.number_of_edges()))
+        return tuple(sorted(cs))
+
+    # Generate and dump starting cut sets to disk
+    starting_cut_sets = [random_cut_set() for _ in range(space_sample_size)]
+    cs_path = os.path.abspath(graph_path) + 'cs-{}-{}.json'.format(seed, space_sample_size)
+    with open(cs_path, 'w+') as csfile:
+        json.dump(starting_cut_sets, csfile)
+
+    job_options = dict(
+        walltime=walltime,
+        results_folder=os.path.abspath(results_folder),
+        request=request,
+        queue=queue,
+        graph_path=os.path.abspath(graph_path),
+        n_jobs=n_jobs,
+        cs_path=cs_path,
+    )
+
+    job_template = """#!/bin/bash
+    #PBS -k oe
+    #PBS -l {request}
+    #PBS -l {walltime}
+    #PBS -P {queue}
+
+    JOB=$PBS_ARRAY_INDEX
+
+    cd $WORK_DIR
+    modindexer dist_partitions {graph_path} $JOB {n_jobs} {cs_path} {results_folder}
[…]

### 2018-04-19 cluster_query_tool/indexer.py

@@ -37,7 +37,7 @@ def load(filepath):
     return json.loads(json_bytes.decode("utf-8"))
 
 
-def get_index(graph, space_sample_size="medium", seed=1, num_procs=cpu_count(), use_cache=True):
+def get_index(graph, space_sample_size="medium", seed=1, num_procs=cpu_count(), use_cache=True, cache_location=None):
     """
     Generate a partition space index for a given network
     :param graph: networkx graph object (make sure name is set for caching)
@@ -63,7 +63,8 @@ def get_index(graph, space_sample_size="medium", seed=1, num_procs=cpu_count(), 
 
     space_sample_size = int(space_sample_size)
     # cache_result
-    cache_location = os.path.join(".ctq_cache", "get_index_{0}_{1}_{2}.json.xz".format(seed,
+    if cache_location is None:
+        cache_location = os.path.join(".ctq_cache", "get_index_{0}_{1}_{2}.json.xz".format(seed,
                                                                                     space_sample_size, graph.name))
 
     if use_cache and os.path.exists(cache_location):
@@ -72,7 +73,7 @@ def get_index(graph, space_sample_size="medium", seed=1, num_procs=cpu_count(), 
             result = load(cache_location)
             return result
         except json.JSONDecodeError:
-            pass
+            pass # Regenerate the cache
 
     result = gen_sample_sets(graph, num_samples=space_sample_size, num_procs=num_procs, seed=seed)
 
@@ -96,7 +97,6 @@ def partition_from_cut(graph, edge_set):
 
 def _sample_local_optima(graph, seed):
     """
-
     :param graph:
     :param seed:
     :return:

### 2018-04-19 setup.py

@@ -9,7 +9,7 @@ long_description = '''
 '''
 
 setup(
-    name="cqt",
+    name="cluster_query_tool",
     version="0.0.1",
     description="Cluster query tool for complex networks",
     long_description=long_description,
@@ -18,7 +18,11 @@ setup(
     install_requires=requirements,
     author_email="jamie.gilbert@azimov.co.uk",
     license="GPL",
-    entry_points={},
+    entry_points={
+        'console_scripts': [
+            "modindexer=cluster_query_tool.distributed_indexer:cli"
+        ]
+    },
     url="https://github.com/azimov/cluster_query_tool",
     include_package_data=True,
     packages=find_packages(),

### 2018-04-19 cluster_query_tool/louvain_consensus.py
Faster and better methods for query vectors

@@ -49,11 +49,18 @@ def partition_to_cut_set(graph, partition):
     return tuple(sorted(set([edge for edge in graph.edges() if partition[edge[0]] != partition[edge[1]]])))
 
 
-def gen_local_optima_community(graph):
+def gen_local_optima_community(graph, cut_set=None):
+    """
+    Generate a partition with louvain. If cut_set is None the starting partition will be randomly chosen.
+    :param graph: nx.Graph
+    :param cut_set: iterble, tuple of edges
+    :return:
+    """
     # The possible space of communities is huge!
-    sample = random.sample(graph.edges(), random.randint(1, graph.number_of_edges()))
+    if cut_set is None:
+       cut_set = random.sample(graph.edges(), random.randint(1, graph.number_of_edges()))
     # convert to partition
-    start_partition = create_partition_from_edge_set(graph, sample)
+    start_partition = create_partition_from_edge_set(graph, cut_set)
     local_optima = louvain.best_partition(graph, partition=start_partition)
 
     return start_partition, local_optima
@@ -169,29 +176,67 @@ def s_quality(query_nodes, nmap, M):
 
 
 @jit(nopython=True, nogil=True)
-def query_vector_jit(query_indexes, membership_mat):
-    qm = np.zeros(membership_mat.shape[0])
-    norm_const = 1 / (membership_mat.shape[1] * query_indexes.shape[0])
-    for v in range(membership_mat.shape[0]):
+def query_vector(query_indexes, M):
+    qm = np.zeros(M.shape[0])
+    norm_const = 1 / (M.shape[1] * query_indexes.shape[0])
+    for v in np.ndindex(M.shape[0]):
         for q in query_indexes:
-            qm[v] += (membership_mat[v] == membership_mat[q]).sum()
+            # Number of times node is in the same cluster as a query node
+            qm[v] += (M[v] == M[q]).sum()
 
     return qm * norm_const
 
 
+@jit(nopython=True, nogil=True)
 def mui_vec_membership(query_indexes, membership_mat):
-
     # Get the sub matrix slice based on query node indexes
-    qmat = membership_mat[np.array(query_indexes)]
+    # qmat = membership_mat[np.array(query_indexes, dtype=np.int16)]
+    '''
+    qmat = np.zeros((query_indexes.shape[0], membership_mat.shape[1]))
+    for i in range(query_indexes.shape[0]):
+        qmat[i] = membership_mat[query_indexes[i]]
[…]

### 2018-04-20 cluster_query_tool/experiments/lfr.py
article/article.tex

@@ -1,48 +1,0 @@
-from cigram import lfr_benchmark_graph
-from cluster_query_tool.louvain_consensus import mu_ivector
-from cluster_query_tool.indexer import get_index
-from cluster_query_tool.experiments import unique_sampler
-from sklearn.metrics import roc_auc_score, average_precision_score
-
-
-def gen_network_index(params):
-    """
-
-    :param params:
-    :return: partitions - ensemble of network partitions
-    """
-    graph, communities = lfr_benchmark_graph(**params)
-    # Partitions are cached
-    partitions = get_index(graph)
-    return partitions
-
-
-def auc_scores(gparams, partitions, seed_size=3, max_samples=120):
-    """
-
-    :param graph:
-    :param comms:
-    :param partitions:
-    :param seed_size:
-    :param max_samples:
-    :return:
-    """
-
-    graph, comms = lfr_benchmark_graph(**gparams)
-    auc_scores = dict()
-    app_scores = dict()
-
-    for c in comms:
-        for cs in unique_sampler(comms[c], seed_size, max_samples=max_samples):
-            vec, key = mu_ivector(graph, partitions, cs)
-            inc = lambda x: 1 if x in comms[c] else 0
-            y_true = [inc(x) for x in graph.nodes() if x not in cs]
-            y_score = [vec[key[x]] for x in graph.nodes() if x not in cs]
-
-            auc_scores[c].append(roc_auc_score(y_true, y_score))
-            app_scores[c].append(average_precision_score(y_true, y_score))
-
-
-def sampler(seed, num_jobs, **kwargs):
-    """"""
-    Parallel(num_jobs=num_jobs)

### 2018-04-20 cluster_query_tool/louvain_consensus.py

@@ -5,7 +5,7 @@ import random
 import numpy as np
 from scipy.stats import mannwhitneyu
 from itertools import combinations, product
-from numba import jit
+import numba
 
 
 def modularity(graph, part):
@@ -168,8 +168,8 @@ def s_quality(query_nodes, nmap, M):
     return np.mean(Mx), np.std(Mx)
 
 
-@jit(nopython=True, nogil=True)
-def query_vector_jit(query_indexes, membership_mat):
+@numba.jit(nopython=True, nogil=True)
+def query_vector(query_indexes, membership_mat):
     qm = np.zeros(membership_mat.shape[0])
     norm_const = 1 / (membership_mat.shape[1] * query_indexes.shape[0])
     for v in range(membership_mat.shape[0]):
@@ -179,8 +179,13 @@ def query_vector_jit(query_indexes, membership_mat):
     return qm * norm_const
 
 
+@numba.jit(nopython=True, nogil=True)
 def mui_vec_membership(query_indexes, membership_mat):
-
+    """
+    :param query_indexes:  numpy.array (1D) of node indexes to query
+    :param membership_mat: n * P matrix of node memberships
+    :return:
+    """
     # Get the sub matrix slice based on query node indexes
     qmat = membership_mat[np.array(query_indexes)]
 
@@ -189,7 +194,7 @@ def mui_vec_membership(query_indexes, membership_mat):
 
     mtrans = membership_mat.transpose()
 
-    for col_id, col in enumerate(qtrans):
+    for col_id, col in np.ndenumerate(qtrans):
         for it in np.unique(col):
             isize = (col == it).sum()  # size of intersection for each community
             mu_vec[np.where((mtrans[col_id] == it))] += isize

### 2018-04-23 cluster_query_tool/louvain_consensus.py
New way of computing intersection scores

@@ -4,8 +4,8 @@ import networkx as nx
 import random
 import numpy as np
 from scipy.stats import mannwhitneyu
-from itertools import combinations, product
-import numba
+from itertools import combinations
+from numba import jit
 
 
 def modularity(graph, part):
@@ -175,19 +175,11 @@ def s_quality(query_nodes, nmap, M):
     return np.mean(Mx), np.std(Mx)
 
 
-<<<<<<< HEAD
-@numba.jit(nopython=True, nogil=True)
-def query_vector(query_indexes, membership_mat):
-    qm = np.zeros(membership_mat.shape[0])
-    norm_const = 1 / (membership_mat.shape[1] * query_indexes.shape[0])
-    for v in range(membership_mat.shape[0]):
-=======
 @jit(nopython=True, nogil=True)
 def query_vector(query_indexes, M):
     qm = np.zeros(M.shape[0])
     norm_const = 1 / (M.shape[1] * query_indexes.shape[0])
     for v in np.ndindex(M.shape[0]):
->>>>>>> 7425665db98e644be9a70462e465d9b5d9fa2aeb
         for q in query_indexes:
             # Number of times node is in the same cluster as a query node
             qm[v] += (M[v] == M[q]).sum()
@@ -195,18 +187,8 @@ def query_vector(query_indexes, M):
     return qm * norm_const
 
 
-<<<<<<< HEAD
-@numba.jit(nopython=True, nogil=True)
-def mui_vec_membership(query_indexes, membership_mat):
-    """
-    :param query_indexes:  numpy.array (1D) of node indexes to query
-    :param membership_mat: n * P matrix of node memberships
-    :return:
-    """
-=======
 @jit(nopython=True, nogil=True)
 def mui_vec_membership(query_indexes, membership_mat):
->>>>>>> 7425665db98e644be9a70462e465d9b5d9fa2aeb
     # Get the sub matrix slice based on query node indexes
     # qmat = membership_mat[np.array(query_indexes, dtype=np.int16)]
     '''
@@ -221,16 +203,10 @@ def mui_vec_membership(query_indexes, membership_mat):
 
     mtrans = membership_mat.transpose()
 
-<<<<<<< HEAD
-    for col_id, col in np.ndenumerate(qtrans):
-        for it in np.unique(col):
-            isize = (col == it).sum()  # size of intersection for each community
-=======
     for col_id in range(qtrans.shape[0]):
[…]

### 2018-04-23 article/article.tex
article/article.tex
New figure for explaining method

@@
-\listfiles
 \documentclass[manuscript, proceedings]{acmart}
@@
 
+\begin{figure*}[ht]
+\includegraphics[width=\textwidth]{images/ppi_example_combined.eps}
+\caption{An example of the query term \textit{``SNAP receptor activity''} on the arabidopsis protein-protein interaction network.
+(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
+(B) Shows a reduced view of the network where a threshold is selected.
+(C) Shows an example ROC curve, sampled from combinations of using 3 randomly selected query nodes including this term.
+Blue nodes indicate those in the query set, the shade of red relates to the strength of the relationship each node has to the query set.
+}
+\label{fig:query_example}
+\end{figure*}
+
 We tested the method on each real network described in section \ref{sec:real_network_descs}.

### 2018-04-23 article/article.tex
Figure and changed article format to signconf (which appears to be correct)

--- 2018-04-19 article/article.tex
@@
-\listfiles
-\documentclass[manuscript, proceedings]{acmart}
+\documentclass[sigconf]{acmart}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{amsmath}
+\usepackage{booktabs}
 
-\usepackage{booktabs} 
 \DeclareMathOperator*{\argmax}{argmax}
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
- \includegraphics[width=0.48\textwidth]{images/search_space_3.png}
+
+  \begin{subfigure}[ht]{0.4\textwidth}
+    \includegraphics[width=\textwidth]{images/search_space_3.png}
+    \caption{Modularity optimisation space of an \textit{E. coli} metabolic network.}
+    \label{fig:modular_search_space}
+  \end{subfigure}
+  \begin{subfigure}[ht]{0.58\textwidth}
+    \centering
+    \includegraphics[width=\textwidth]{images/meth_fig/fig1_desc.eps}
+    \caption{Outline of the proposed approach to querying networks by using multiple, high quality representations of modular networks.}
+    \label{fig:algorithm_outline}
+  \end{subfigure}
  \caption{
@@
  }
- \label{fig:modular_search_space}
-\end{figure}
+\end{figure*}
 
@@
 In essence, the objective is to use multiple modular representation of a given dataset to generate a relatedness score for a given set of query vertices.
-
-\begin{figure*}
- \centering
- \includegraphics[width=0.6\textwidth]{images/meth_fig/fig1_desc.eps}
- \caption{Outline of the proposed approach to querying networks by using multiple, high quality representations of modular networks.}
- \label{fig:algorithm_outline}
-\end{figure*}
 
@@
 \subsection{Real networks}
+
+\begin{figure*}[ht]
+\includegraphics[width=\textwidth]{images/ppi_example_combined.eps}
+\caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
+(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
+(B) Shows a reduced view of the network where a threshold is selected, reducing the network to 404 nodes.
+(C) Shows an example ROC curve, sampled from combinations of using 3 randomly selected query nodes including this term.
+Blue nodes indicate those in the randomly selected 3 query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
+}
+\label{fig:query_example}
+\end{figure*}
+
 In order to test the performance of the semi-supervised classification on real-world data we present our findings on example networks with known metadata communities.
@@
 
-\begin{figure*}
-     \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{images/eu_roc_scores.eps}
-        \caption{EU email departments}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{images/yeast_ppi_roc_scores.eps}
-        \caption{Yeast PPI protein complexes}
-    \end{subfigure}
-    \caption{Mean area under RO curve (AUC) scores from cross-validation performed on Metadata communities for networks described in Section \ref{sec:real_network_descs}.
-    Dashed line indicates an AUC score of 0.5 (random chance).
-    Communities are ordered by size.
-    Error bars indicate standard deviation.
-    }
-    \label{fig:real_network_results}
-\end{figure*}
-
-\begin{figure*}
-    \centering
-    \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{images/eu_email_nodewise_roc.eps}
-        \caption{EU email departments (986 nodes)}
-    \end{subfigure}
-    \begin{subfigure}[b]{0.48\textwidth}
-        \centering
-        \includegraphics[width=\textwidth]{images/yeast_ppi_nodewise_roc.eps}
-        \caption{Yeast PPI protein complexes (1628 nodes)}
-    \end{subfigure}
-    \caption{Receiver Operator Characteristic curves for node communities.
-    Dashed line indicates an AUC score of 0.5 (random chance).
-    Represents mean, shaded area indicates standard deviation.
-    }
-    \label{fig:real_network_nodwise_classifiers}
-\end{figure*}
+% \begin{figure*}
+%      \centering
+%     \begin{subfigure}[b]{0.48\textwidth}
+%         \centering
+%         \includegraphics[width=\textwidth]{images/eu_roc_scores.eps}
+%         \caption{EU email departments}
+%     \end{subfigure}
+%     \begin{subfigure}[b]{0.48\textwidth}
+%         \centering
+%         \includegraphics[width=\textwidth]{images/yeast_ppi_roc_scores.eps}
+%         \caption{Yeast PPI protein complexes}
+%     \end{subfigure}
+%     \caption{Mean area under RO curve (AUC) scores from cross-validation performed on Metadata communities for networks described in Section \ref{sec:real_network_descs}.
+%     Dashed line indicates an AUC score of 0.5 (random chance).
+%     Communities are ordered by size.
+%     Error bars indicate standard deviation.
+%     }
+%     \label{fig:real_network_results}
+% \end{figure*}
+% 
+% 
+% \begin{figure*}
+%     \centering
+%     \begin{subfigure}[b]{0.48\textwidth}
+%         \centering
+%         \includegraphics[width=\textwidth]{images/eu_email_nodewise_roc.eps}
+%         \caption{EU email departments (986 nodes)}
+%     \end{subfigure}
+%     \begin{subfigure}[b]{0.48\textwidth}
+%         \centering
+%         \includegraphics[width=\textwidth]{images/yeast_ppi_nodewise_roc.eps}
+%         \caption{Yeast PPI protein complexes (1628 nodes)}
+%     \end{subfigure}
+%     \caption{Receiver Operator Characteristic curves for node communities.
+%     Dashed line indicates an AUC score of 0.5 (random chance).
+%     Represents mean, shaded area indicates standard deviation.
+%     }
+%     \label{fig:real_network_nodwise_classifiers}
+% \end{figure*}
 
@@
 
-\section{Related work}
-\label{sec:related_work}
-
-This work relates very strongly to the idea of local community detection, more specifically the idea of \textit{seed set expansion}.
-Here, a given seed set is created a random walks are analysed to find clearly related communities of vertices.
-One of the most common approaches to finding related vertices in a network is the random walk with restart (RWR) \cite{can2005analysis, kohler2008walking}.
-This approach has been applied in fields as diverse as recommender systems and the detection of potential drug targets \cite{chen2012drug}.
-In RWR the relatedness of any pair of vertices can be seen as the probability of a particle traversing the graph starting at a given vertex and ending at another.
-The restart aspect of the random walk can be thought of as the probability of the walker teleporting back to the start vertex with some none zero probability. 
-The higher the probability of the walker ending up at a given vertex, the more likely it is that the two vertices are related.
-
-Conceptually, RWR is very similar to the method presented in this paper given that the user has a given query.
-One can thing of the RWR probability as analogous to the value of $\mu_i(S)$ presented above.
-However, the RWR value is based only on a single vertex as a query set where the approach presented in this work requires many vertices associated with a given label for it to be readily applicable.
-
-Many existing method are based on the idea of a locally dense subgraph containing \textit{all query nodes} \cite{}.
-In contrast, the query approach presented here does not require the queries to be a self contained sub-graph.
-Indeed, queries can contain spurious nodes that are topologically distinct from one another - the result is that the either $q(S)$ score for the query will be very low and insignificant, or the spurious nodes will be ignored in the final query set.
-In user facing domains it is highly likely that very large query sets do not form isolated topologies.
-With Conventional methods some ``cleaning up'' of the underlying queries is often required to gather any meaningful expansion.
-
-Whilst modularity maximisation is used for the set of global partitions, this approach is distinct from local modularity based approaches \cite{}.
-A limitation of this approach compared with localised methods is that the entire dataset is required.
-However, the objective is somewhat different as the approach presented here relies on high quality meta-data labels for queries.
-In this sense, the approach should be considered closer to semi-supervised \textit{classification} than unsupervised \textit{clustering}.
-
-In the field of community detection, a number of very recent articles have focused on using metadata to improve the results of community detection approaches.
-
-%TODO: Discuss citations of metadata based community detection - Newman-Clauset, Jure Lesovec, other citations in newman paper.
-
-These algorithms, however, are distinct from the approach taken here as the metadata is not used in the module discovery process.
-Furthermore, the results in this work attempt to explicitly label unlabelled data and only require a relatively small number of labels to operate in such a fashion.
-In contrast,  the recent approach by Newman and Clauset \cite{}, for example, uses examples in which practically the entire network contains labels which is less useful from the perspective of label discovery.
-However, these methods are vastly superior to the work presented here when considering the research question of whether a labelling scheme (such as demography in a social network) accurately describes the structure of the network.
+% \section{Related work}
+% \label{sec:related_work}
+% This work relates very strongly to the idea of local community detection, more specifically the idea of \textit{seed set expansion}.
+% Here, a given seed set is created a random walks are analysed to find clearly related communities of vertices.
+% One of the most common approaches to finding related vertices in a network is the random walk with restart (RWR) \cite{can2005analysis, kohler2008walking}.
+% This approach has been applied in fields as diverse as recommender systems and the detection of potential drug targets \cite{chen2012drug}.
+% In RWR the relatedness of any pair of vertices can be seen as the probability of a particle traversing the graph starting at a given vertex and ending at another.
+% The restart aspect of the random walk can be thought of as the probability of the walker teleporting back to the start vertex with some none zero probability. 
+% The higher the probability of the walker ending up at a given vertex, the more likely it is that the two vertices are related.
+% 
+% Conceptually, RWR is very similar to the method presented in this paper given that the user has a given query.
+% One can thing of the RWR probability as analogous to the value of $\mu_i(S)$ presented above.
+% However, the RWR value is based only on a single vertex as a query set where the approach presented in this work requires many vertices associated with a given label for it to be readily applicable.
+% 
+% Many existing method are based on the idea of a locally dense subgraph containing \textit{all query nodes} \cite{}.
+% In contrast, the query approach presented here does not require the queries to be a self contained sub-graph.
+% Indeed, queries can contain spurious nodes that are topologically distinct from one another - the result is that the either $q(S)$ score for the query will be very low and insignificant, or the spurious nodes will be ignored in the final query set.
+% In user facing domains it is highly likely that very large query sets do not form isolated topologies.
+% With Conventional methods some ``cleaning up'' of the underlying queries is often required to gather any meaningful expansion.
+% 
+% Whilst modularity maximisation is used for the set of global partitions, this approach is distinct from local modularity based approaches \cite{}.
+% A limitation of this approach compared with localised methods is that the entire dataset is required.
+% However, the objective is somewhat different as the approach presented here relies on high quality meta-data labels for queries.
+% In this sense, the approach should be considered closer to semi-supervised \textit{classification} than unsupervised \textit{clustering}.
+% 
+% In the field of community detection, a number of very recent articles have focused on using metadata to improve the results of community detection approaches.
+% 
+% %TODO: Discuss citations of metadata based community detection - Newman-Clauset, Jure Lesovec, other citations in newman paper.
+% 
+% These algorithms, however, are distinct from the approach taken here as the metadata is not used in the module discovery process.
+% Furthermore, the results in this work attempt to explicitly label unlabelled data and only require a relatively small number of labels to operate in such a fashion.
+% In contrast,  the recent approach by Newman and Clauset \cite{}, for example, uses examples in which practically the entire network contains labels which is less useful from the perspective of label discovery.
+% However, these methods are vastly superior to the work presented here when considering the research question of whether a labelling scheme (such as demography in a social network) accurately describes the structure of the network.
 

### 2018-04-24 article/article.tex
Tidyup, figure, refs

@@
 
-\author{John King}
-\affiliation{%
-  \institution{School of Mathematical Sciences}
-  \streetaddress{University of Nottingham}
-  \city{Nottingham}
-  \country{United Kingdom}
-  \postcode{NG7 2RD}
-}
-\email{john.king@nottingham.ac.uk}
+% \author{John King}
+% \affiliation{%
+%   \institution{School of Mathematical Sciences}
+%   \streetaddress{University of Nottingham}
+%   \city{Nottingham}
+%   \country{United Kingdom}
+%   \postcode{NG7 2RD}
+% }
+% \email{john.king@nottingham.ac.uk}
 
@@
 Uncovering latent community structure in complex networks is a field that has received an enormous amount of attention.
-Unfortunately, whilst potentially very powerful unsupervised methods for classifying nodes into similar groups based on topology alone has been shown to have several major limitations.
-Crucially, the search space for module extraction approaches appears to be extremely glassy, with many high valued solutions that lack any real similarity to one another.
-However, in this paper we argue that this is not a flaw with the modularity maximisation algorithm but, rather, information that can be used to aid the classification of functional relationships between vertices.
-Formally, we present an approach to generating a search ``index'' for a network, based on the space of high value modular partitions.
-This search spaces allows the formulation of query based measures that provide a score for the level of relatedness to a given labelled query set.
-The methods developed in this paper are applied to biological and social datasets with ground-truth label data, with very small query sets for nodes.
-When tested on both real and synthetic datasets our method achieves extremely high levels of classification.
+Unfortunately, whilst potentially very powerful unsupervised methods for uncovering labels based on topology alone has been shown to have several difficulties.
+For example, the search space for module extraction approaches appears to be extremely glassy, with many high valued solutions that lack any real similarity to one another.
+However, in this paper we argue that this is not a flaw with the modularity maximisation algorithm but, rather, information that can be used to aid the context specific classification of functional relationships between vertices.
+Formally, we present an approach to generating a high value modularity consensus space for a network, based on the space of locally optimal modular partitions.
+This is then used as an approach to uncover latent relationships between sets initial query sets.
+The methods developed in this paper are applied to biological and social datasets with ground-truth label data, with a small number of examples used as seed sets to uncover relationships.
+When tested on both real and synthetic datasets our method achieves extremely high levels of classification accuracy in a context specific manner.
 Furthermore, the approach can be applied in distributed environments potentially allowing it to scale to very large networks.
@@
 A fundamental issue at the heart of machine learning methods applied to large scale datasets is the ability to correctly identify classes of related objects in an unsupervised manner.
-In network science, this methodology is often referred to as \textit{community} detection, due to the intuitive analogy from the social sciences \cite{fortunato2010community}.
-Many algorithms exist to solve this problem, yet initial starting conditions or different optimisation strategies may result in conflicting results even when the same objective function is being maximised \cite{good2010performance}.
-In this paper, we develop an intuitive method to use the uncertainty amongst a high number of near optimal solutions to meaedsure the overall quality of a given labelling scheme that can come from classes known \textit{a-priori} or clusters detected through other methods.
-This approach also allows the expansion of labels to find potentially related vertices to an initial starting subset.
+In network science, this methodology is often referred to as \textit{community} detection, due to the intuitive analogy to the notion of social groupings \cite{fortunato2010community}.
+Many algorithms exist to solve this problem \cite{fortunato2016community}, yet initial starting conditions or different optimisation strategies may result in conflicting results even when the same objective function is being maximised \cite{good2010performance}.
+In this paper, we develop an intuitive method to use the uncertainty amongst a high number of near optimal solutions to measure context sensitive relationships between small sets of labelled vertices.
+This approach can be based on labels that are not first neighbours in order to find other potentially related vertices.
 
@@
 This allows greedy optimisation algorithms \cite{blondel2008fast} to trivially find solutions that score extremely high values of modularity.
-In order to solve this issue, certain approaches use a consensus based approach to clustering, combining many high value partitions into a given median partition.
+In order to solve this issue, certain approaches use a consensus based approach to clustering, combining many high value partitions into a given median partition \cite{lancichinetti2012consensus}.
 
 The use of community detection is widespread.
-For example, core goal in systems biology is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network \cite{}.
+For example, core goal in systems biology is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network \cite{girvan2002community}.
 In many situations, only the role of a small number of genes is known, with much of the annotation for a given organism being computed through naive homology information that ignores the role of a gene within a wider context.
 The advent of high throughput experimental datasets has allowed the construction of genome scale networks, leading to the observation of non-trivial topological properties such as densely connected clusters \cite{ArabidopsisConsortium2011}.
-These densely connected clusters are widely believed to be associated with specific function, such as protein complexes or biochemical pathways \cite{}.
+These densely connected clusters are widely believed to be associated with specific function, such as multi-protein complexes or biochemical pathways.
 
@@
 As the objective of community detection approaches is to relate information, it is assumed that some labelled meta-data can be used to find unlabelled, potentially related vertices.
-The overall objective can be thought of as a form of recommender system \cite{ricci2011introduction}, relating a given query in the form of a vertex set to potentially related information by exploiting the co-occurrence between communities.
-
-In this vein, we apply the method presented in this paper to the problem of classifying biological function.
-The objective of our algorithm, in this sense, is given sets of known function for genes or proteins within interaction networks, to generate meaningful hypothesis that can be externally validated.
-Naturally this process depends heavily on the quality of underlying datasets, however, we feel this approach is a conceptual change from conventional module detection approaches which only consider a single clustering of a network, overlapping or not, where only binary classification is considered.
 
@@
 The querying method is a polynomial time algorithm that could be trivially adapted to form the basis of many user facing applications.
-This approach is applied to a number of real world metabolic and protein interaction datasets with explicit queries relating to biological function.
-In addition, the ranking scores for the uncertainty of community classification are used to capture critical ``bridge'' nodes and edges allowing an efficient multi-scale form of visualisation for networks with glassy modular structure.
+This approach is applied to social and protein-protein interaction networks with good quality ground truth labels.
 
-\section{Vertex classification}
+\section{The multi-vertex classification problem}
 The intuitive notion that the structure of a vertex's connections gives insight into its function is a fundamental basis for research in network science.
 In many cases, the role of given node is uncharacterised and we would seek to discover latent relationships through methods such as community detection.
-The basic premise of community detection is that detecting dense topological sub-graphs allows one to uncover the function of vertices \cite{}.
+The basic premise of community detection is that detecting dense topological sub-graphs allows one to uncover the function of vertices \cite{fortunato2010community}.
 
@@
 In many situations this information will be sparse or incomplete.
-For example, in biological networks only a very small number of organisms have a high level of coverage in terms of functional annotation \cite{}.
+For example, in biological networks only a very small number of organisms have a high level of coverage in terms of functional annotation \cite{bassel2012systems}.
 
 The problem tackled in this paper can be formulated as follows:
-Given a graph made up of vertices and edges $G = (V, E)$, we formally ask the question; \textit{How related is a given vertex to a given query set?}
-This question assumes that a given query set is formally related, in practice, however, this may not be the case.
-Consequently we also use our approach to ask another question; \textit{ How related are a set of query vertices?}
+Given a graph made up of vertices and edges $G = (V, E)$, and a query set $S \subset V$, we formally ask the question; \textit{How related is a given vertex to $S$?}
+This question assumes that a given query set is formally related.
+In practice, this is likely not the case for most subsets of $V$.
+Consequently we also use our approach to ask another question; \textit{How well related is $S$?}
+In order to answer these questions we focus on the set of high valued partitions of a given network detectable with the well known modularity maximisation algorithm.
 
 \section{Exploiting the modularity query space}
-In order to characterise community structure, one of the most popular approaches is to use modularity maximisation.
+To characterise latent community structure, one of the most popular approaches is to use modularity maximisation.
 The modularity quality function of a partition on a graph is given by the following equation \cite{newman2004}
@@
 
-In our work, instead of seeing this modular search space as a flaw we consider each high value partition to be information about latent relationships between vertices inferred through the topology of the network.
-In the parlance of the computational and information sciences, we consider the mapping of this search space to be an \textit{index} analogous to search algorithms.
+In this work, we consider each high value partition to be information about latent relationships between vertices inferred through the topology of the network.
+This approach, in and of itself is not unique, as there have been previous approaches that use the consensus of an ensemble of clusters to create high quality overlapping clustering of networks \cite{lancichinetti2012consensus}.
+Such an approach, whilst well principled, is a context insensitive view of the modular structure of a graph.
+
+The objective, then, is to use the disagreement between the set of highly modular partitions as information; that is to say, to infer the probability that sets of vertices are contained within the same cluster.
 Whilst methods based on simulated annealing can be used to guarantee full coverage of the network, the following section describes a method adapted from the greedy agglomerative Louvain algorithm \cite{blondel2008fast}.
@@
 
-\subsection{Generating the search index}
 In order to cover the space of high modularity partitions, randomly generated starting partitions are computed with a random cut set.
 To achieve this each edge is either placed inside the cut set or not as the result of an independent Bernoulli trial. 
-Each random partition is used as the starting partition for the greedy louvain process.
+Each random partition is used as the starting partition for the greedy Louvain process.
 In principle, any search exploration procedure, such as simulated annealing \cite{GuimeraNature2005} could be used.
@@
 Formally, this can be expressed in terms of the \textit{expansion score} of a given vertex,
-% \begin{equation} \label{eq:mu_score}
-% \mu_i(S) = \frac{1}{|\mathcal{P}| |S - i|} \sum_{P \in \mathcal{P}} \sum_{j \in S - i} \delta(c^{P}_{i}, c^{P}_{j}),
-% \end{equation}
 \begin{equation} \label{eq:mu_score}
-\mu_i(S) = \frac{1}{|\mathcal{P}|} \sum_{P \in \mathcal{P}} \delta(c^{P}_i, c^{P}_S),
+\mu_i(S) = \frac{1}{|\mathcal{P}| |S| } \sum_{P \in \mathcal{P}} \sum_{j \in S} \delta(c^{p}_i, c^{p}_j),
 \end{equation}
-where $S$ denotes a query set, $P$ is a given partition in the space of all high quality partitions $\mathcal{P}$, $c^{P}_{i}$ indicates the partition vertex $i$ is contained in within partition $P$ and
-$\delta(u, v)$ is the Dirac delta function that equals 1 if are the same cluster and $0$ otherwise, where $c^{P}_S$ is given by,
-\begin{equation}
- c^{P}_S = \argmax_{C \in P} |C \cap S|,
-\end{equation}
-or the largest intersecting cluster with the query set, in partition $P$.
-Using the largest intersecting community with $S$ is both computationally favourable for computing $mu_i$ for all $i$ in $V$ and allows the query set to contain potentially spurious query nodes.
-Where $\mu_i(S) = 1$ the partition space indicates that a given vertex is always partitioned in the same group as the query set.
-In the case $\mu_i(S) = 0$ the vertex $i$ never appears in the same cluster as the largest query set.
+where $S$ denotes a query set, $P$ is a given partition in the space of all high quality partitions $\mathcal{P}$, $c^{p}_{i}$ indicates the partition vertex $i$ is contained in within partition $P$ and
+$\delta(u, v)$ is the Dirac delta function that equals 1 if $c^{p}_i$ and  $c^{p}_j$ are the same cluster and $0$ otherwise.
+As a simple example, for a pair of vertices $i$ and $S$ such that $S = {j}$ we would consider $\mu_i$ to be the number of times $i$ and $j$ appear in the same cluster, given an ensemble of network clusterings.
 We define $\mu_i(S)$ for all vertices in the network, including those in $S$.
+However, for the case where $i$ is in $S$ we, instead, consider the value $\mu_i(S - i)$ to remove bias.
 In many cases, a query set will not be fully represented by the partitions found within the network, this is further elaborated in the following section.
@@
 Interestingly, this method is capable of correctly classifying communities with only a small number of seed query vertexes.
-These results show that the community query method could be used as a powerful exploratory tool in network analysis.
+These results show that this query method could be used as a powerful exploratory tool in network analysis.
 
-The fact that the method is able to uncover small protein complexes seems to contradict the principle that modularity maximisation algorithms have a resolution limit \cite{}.
-This may be due to the fact that
+The fact that the method is able to uncover small protein complexes seems to contradict the principle that modularity maximisation algorithms have a resolution limit \cite{fortunato2007resolution}.
+Whilst this appears to be the case it is important to not that the resolution limit applies to a single partition of space.
+Further work is needed to investigate why small communities are still detectable.
+However, we speculate that is likely due to the fact that the co-classification of vertices between different partitions remains fairly tolerant to changes.
+I.e. whilst the large communities they reside in changes significantly, the small cluster of nodes is always clustered in the same community, regardless of the partition.
 We do note that, where communities are very small, any approach will extremely sensitive to false positive and false negative results.
-This should be considered when using this method as an exploratory tool.
+As such, this should be considered when using any method of this form as an exploratory tool.
 
@@
 
-This allows the use of a single node to find related vertices, in real networks the results appeared to have a very good level of accuracy with average AUC of ROC curves above $0.9$.
-In a practical context, however, this should not be interpreted as uncovering the community structure as this includes many overlapping communities for which the node is a member.
+\section{Related work}
+\label{sec:related_work}
+This work relates very strongly to the idea of local community detection, more specifically the idea of \textit{seed set expansion} \cite{gleich2012vertex}..
+Here, a given seed set is created a random walks are analysed to find clearly related communities of vertices.
+One of the most common approaches to finding related vertices in a network is the random walk with restart (RWR) \cite{can2005analysis, kohler2008walking}.
+This approach has been applied in fields as diverse as recommender systems and the detection of potential drug targets \cite{chen2012drug}.
+In RWR the relatedness of any pair of vertices can be seen as the probability of a particle traversing the graph starting at a given vertex and ending at another.
+The restart aspect of the random walk can be thought of as the probability of the walker teleporting back to the start vertex with some none zero probability. 
+The higher the probability of the walker ending up at a given vertex, the more likely it is that the two vertices are related.
 
-% \section{Related work}
-% \label{sec:related_work}
-% This work relates very strongly to the idea of local community detection, more specifically the idea of \textit{seed set expansion}.
-% Here, a given seed set is created a random walks are analysed to find clearly related communities of vertices.
-% One of the most common approaches to finding related vertices in a network is the random walk with restart (RWR) \cite{can2005analysis, kohler2008walking}.
-% This approach has been applied in fields as diverse as recommender systems and the detection of potential drug targets \cite{chen2012drug}.
-% In RWR the relatedness of any pair of vertices can be seen as the probability of a particle traversing the graph starting at a given vertex and ending at another.
-% The restart aspect of the random walk can be thought of as the probability of the walker teleporting back to the start vertex with some none zero probability. 
-% The higher the probability of the walker ending up at a given vertex, the more likely it is that the two vertices are related.
-% 
-% Conceptually, RWR is very similar to the method presented in this paper given that the user has a given query.
-% One can thing of the RWR probability as analogous to the value of $\mu_i(S)$ presented above.
-% However, the RWR value is based only on a single vertex as a query set where the approach presented in this work requires many vertices associated with a given label for it to be readily applicable.
-% 
-% Many existing method are based on the idea of a locally dense subgraph containing \textit{all query nodes} \cite{}.
-% In contrast, the query approach presented here does not require the queries to be a self contained sub-graph.
-% Indeed, queries can contain spurious nodes that are topologically distinct from one another - the result is that the either $q(S)$ score for the query will be very low and insignificant, or the spurious nodes will be ignored in the final query set.
-% In user facing domains it is highly likely that very large query sets do not form isolated topologies.
-% With Conventional methods some ``cleaning up'' of the underlying queries is often required to gather any meaningful expansion.
-% 
-% Whilst modularity maximisation is used for the set of global partitions, this approach is distinct from local modularity based approaches \cite{}.
-% A limitation of this approach compared with localised methods is that the entire dataset is required.
-% However, the objective is somewhat different as the approach presented here relies on high quality meta-data labels for queries.
-% In this sense, the approach should be considered closer to semi-supervised \textit{classification} than unsupervised \textit{clustering}.
-% 
-% In the field of community detection, a number of very recent articles have focused on using metadata to improve the results of community detection approaches.
-% 
-% %TODO: Discuss citations of metadata based community detection - Newman-Clauset, Jure Lesovec, other citations in newman paper.
-% 
-% These algorithms, however, are distinct from the approach taken here as the metadata is not used in the module discovery process.
-% Furthermore, the results in this work attempt to explicitly label unlabelled data and only require a relatively small number of labels to operate in such a fashion.
-% In contrast,  the recent approach by Newman and Clauset \cite{}, for example, uses examples in which practically the entire network contains labels which is less useful from the perspective of label discovery.
-% However, these methods are vastly superior to the work presented here when considering the research question of whether a labelling scheme (such as demography in a social network) accurately describes the structure of the network.
+Conceptually, RWR is very similar to the method presented in this paper given that the user has a given query.
+The RWR probability as analogous to the value of $\mu_i(S)$ presented above.
+Further investigation needs to be conducted into how similar local community based approaches, such as random walks, compare with this method.
+
+Many existing method are based on the idea of a locally dense subgraph containing \textit{all query nodes} \cite{benson2016higher}.
+In contrast, the query approach presented here does not require the queries to be a self contained sub-graph.
+Indeed, queries can contain spurious nodes that are topologically distinct from one another - the result is that the either $q(S)$ score for the query will be very low and statistically insignificant, or the spurious nodes will be ignored in the final query set.
+
+In the field of community detection, a number of very recent articles have focused on using metadata to improve the results of community detection approaches.
+These algorithms, however, are distinct from the approach taken here as the metadata is not used in the module discovery process.
+Furthermore, the results in this work attempt to explicitly label unlabelled data and only require a relatively small number of labels to operate in such a fashion.
+In contrast,  the recent approach by Newman and Clauset \cite{newman2016structure}, for example, uses examples in which practically the entire network contains labels which is less useful from the perspective of label discovery.
+However, these methods generally consider if a labelling scheme (such as demography in a social network) accurately describes the structure of the network.
 
@@
 
-However, this approach requires the community landscape to contain many local maxima, a property likely shared by many real networks.
+However, this approach requires the community landscape to contain many local maxima, a property likely shared by many real-world, heterogeneous networks.
 Similarly, the method presented here requires both some labelled data and the labels to be represented well within the topology of the underlying network.
@@
 
-% Furthermore, we extended the use of this framework to allow quality measurements of selected labellings and similarity comparrisons between data.
+This work presents a number of interesting potential future avenues for research, such as observing how query sets change in time dynamic or multi-scale networks.
+Similarly, further analysis could be conducted to test how large the set of high value partitions needs to be, and how applicable this approach can be to very large graphs.
 

### 2018-04-24 experiments/experiments.py
Now updated experiments to use threads instead of processes.

@@ -1,4 +1,4 @@
-from cluster_query_tool.louvain_consensus import mu_ivector
+from cluster_query_tool.louvain_consensus import query_vector
 
 from sklearn.metrics import roc_auc_score
 
@@ -12,6 +12,8 @@ import logging
 
 from scipy.special import binom
 import itertools
+
+from numba import jit
 
 logger = logging.getLogger("cigram.generators")
 logger.setLevel(logging.WARNING)
@@ -73,27 +75,44 @@ def unique_sampler(node_set, sample_size, max_samples=96):
     return sample_sets
 
 
-def roc_score_node(n, graph, index, node_comms):
-    vec, key = mu_ivector(graph, index, [n])
-    inc = lambda x: 1 if x in node_comms[n] else 0
-    y_true = [inc(x) for x in graph.nodes() if x != n]
-    y_score = [vec[key[x]] for x in graph.nodes() if x != n]
+@jit(nopython=True, nogil=True)
+def fast_auc(y_true, y_prob):
+    """
+    Numba implementation of auc score calculation for multi threaded purposes
+    :param y_true:
+    :param y_prob:
+    :return:
+    """
+    y_true = y_true[np.argsort(y_prob)]
+    nfalse = 0
+    auc = 0
+    n = len(y_true)
+    for i in range(n):
+        y_i = y_true[i]
+        nfalse += (1 - y_i)
+        auc += y_i * nfalse
+    auc /= (nfalse * (n - nfalse))
+    return auc
 
-    return roc_auc_score(y_true, y_score)
+
+def roc_score_seed(seed_set, nodes, membership_ma, comm):
+    vec = query_vector(seed_set, membership_ma)
+
+    def inc(x):
+        if x in comm:
+            return 1
+        return 0
+
+    y_true = np.array([inc(x) for x in nodes if x not in seed_set])
+    y_score = np.array([vec[x] for x in nodes if x not in seed_set])
+    return fast_auc(y_true, y_score)
 
 
-def roc_score_seed(seed_set, graph, index, comm):
-    vec, key = mu_ivector(graph, index, seed_set)
-    inc = lambda x: 1 if x in comm else 0
-    y_true = [inc(x) for x in graph.nodes() if x not in seed_set]
-    y_score = [vec[key[x]] for x in graph.nodes() if x not in seed_set]
-    return roc_auc_score(y_true, y_score)
-
-
-def get_auc_scores_community(seed_size, community, graph, index, sample_seed=1337):
[…]

### 2018-04-24 experiments/lfr_nooverlap.py

@@ -4,6 +4,7 @@ HPC script for running evaluation of performance on benchmark graphs
 This script is supposed to be run by the jobscript
 """
 from experiments import get_benchmark, get_auc_scores_community
+from cluster_query_tool.louvain_consensus import membership_matrix
 import numpy as np
 import click
 from subprocess import call
@@ -35,12 +36,17 @@ def auc_compute(seed, n, mu, results_folder):
     results_file = os.path.abspath(os.path.join(results_folder, rp))
 
     graph, communities, index = get_benchmark(pset)
+
+    membership_ma, nmap = membership_matrix(graph.nodes(), index)
+
+    nodes = np.array(list(nmap.values()))
     results = []
     for c, comm in communities.items():
         for seed_size in _seed_sizes:
             if len(comm) > seed_size:
                 # Seed of AUC scores for node this size
-                auc_s = get_auc_scores_community(seed_size, comm, graph, index)
+                scom = np.array([nmap[i] for i in comm])
+                auc_s = get_auc_scores_community(seed_size, scom, nodes, membership_ma)
                 results.append([int(n), float(mu), int(seed), c, seed_size, len(comm), np.mean(auc_s), np.std(auc_s)])
 
     with open(results_file, "w+") as rf:

### 2018-04-24 experiments/experiments.py
Tidy up

@@ -1,7 +1,5 @@
 from cluster_query_tool.louvain_consensus import query_vector
 
-from sklearn.metrics import roc_auc_score
-
 from cigram import lfr_benchmark_graph
 from joblib import Parallel, delayed
 from multiprocessing import cpu_count
@@ -95,6 +93,7 @@ def fast_auc(y_true, y_prob):
     return auc
 
 
+@jit(nopython=True, nogil=True)
 def roc_score_seed(seed_set, nodes, membership_ma, comm):
     vec = query_vector(seed_set, membership_ma)
 
@@ -115,4 +114,3 @@ def get_auc_scores_community(seed_size, community, nodes, membership_ma, sample_
     funcs = (delayed(roc_score_seed)(np.array(sample), nodes, membership_ma, community) for sample in samples)
     auc_scores = Parallel(n_jobs=cpu_count(), backend='threading')(funcs)
     return auc_scores
-

### 2018-04-25 experiments/lfr_overlap.py
Fixed overlapping experiment

@@ -9,15 +9,16 @@ import click
 from subprocess import call
 import os
 import json
-from joblib import load, dump
+from cluster_query_tool.louvain_consensus import membership_matrix
 
 
 _base_params = dict(
     average_degree=20,
-    max_degree=50,
-    minc_size=10,
+    max_degree=300,
+    minc_size=1,
     maxc_size=50,
-    mu=0.1,
+    mu=0.3,
+    overlapping_memberships=4,
 )
 
 _seed_sizes = [1, 3, 7, 15]
@@ -39,27 +40,20 @@ def auc_compute(seed, n, ol, results_folder):
 
     graph, communities, index = get_benchmark(pset)
 
-    graph_path = '/dev/shm/{}.graph'.format(graph.name)
-    dump(graph, graph_path)
-    graph = load(graph_path, mmap_mode='r')
+    membership_ma, nmap = membership_matrix(graph.nodes(), index)
 
-    index_path = '/dev/shm/{}.index'.format(graph.name)
-    dump(index, index_path)
-    index = load(index_path, mmap_mode='r')
-
+    nodes = np.array(list(nmap.values()))
     results = []
     for c, comm in communities.items():
         for seed_size in _seed_sizes:
             if len(comm) > seed_size:
                 # Seed of AUC scores for node this size
-                m_auc, std_auc = get_auc_scores_community(seed_size, comm, graph, index)
-                results.append([int(n), int(ol), int(seed), c, seed_size, len(comm), m_auc, std_auc])
+                scom = np.array([nmap[i] for i in comm])
+                auc_s = get_auc_scores_community(seed_size, scom, nodes, membership_ma)
+                results.append([int(n), int(ol), int(seed), c, seed_size, len(comm), np.mean(auc_s), np.std(auc_s)])
 
     with open(results_file, "w+") as rf:
         json.dump(results, rf)
-
-    os.unlink(graph_path)
-    os.unlink(index_path)
 
 
 @click.command()
@@ -117,7 +111,7 @@ python {file} auc_compute {n} {ol} $JOB {results_folder}
     if not os.path.exists(commands_path):
         os.mkdir(commands_path)
 
-    overlap_vals = np.linspace(0.0, 0.5, 10)
+    overlap_vals = np.linspace(0.0, 1.0, 10)
     overlap_vals *= int(n)
     for ol in overlap_vals.astype(int):
         command_file_path = os.path.join(commands_path, "lfr_bm_overlap_{}_{:.2f}.sh".format(n, ol))

### 2018-04-26 cluster_query_tool/distributed_indexer.py
Changes to indexer

@@ -41,16 +41,6 @@ def pbs_indexer(graph_path, seed, n_jobs, results_folder, walltime, request, spa
     random.seed(seed)
     graph = load_graph(graph_path)
 
-    def random_cut_set():
-        cs = random.sample(graph.edges(), random.randint(1, graph.number_of_edges()))
-        return tuple(sorted(cs))
-
-    # Generate and dump starting cut sets to disk
-    starting_cut_sets = [random_cut_set() for _ in range(space_sample_size)]
-    cs_path = os.path.abspath(graph_path) + 'cs-{}-{}.json'.format(seed, space_sample_size)
-    with open(cs_path, 'w+') as csfile:
-        json.dump(starting_cut_sets, csfile)
-
     job_options = dict(
         walltime=walltime,
         results_folder=os.path.abspath(results_folder),
@@ -58,7 +48,7 @@ def pbs_indexer(graph_path, seed, n_jobs, results_folder, walltime, request, spa
         queue=queue,
         graph_path=os.path.abspath(graph_path),
         n_jobs=n_jobs,
-        cs_path=cs_path,
+        n_samps=int(round(int(space_sample_size) / int(n_jobs)))
     )
 
     job_template = """#!/bin/bash
@@ -70,7 +60,7 @@ def pbs_indexer(graph_path, seed, n_jobs, results_folder, walltime, request, spa
     JOB=$PBS_ARRAY_INDEX
 
     cd $WORK_DIR
-    modindexer dist_partitions {graph_path} $JOB {n_jobs} {cs_path} {results_folder}
+    modindexer dist_partitions {graph_path} $JOB {n_jobs} {n_samps} {results_folder}
 
     """.format(**job_options)
 
@@ -97,30 +87,21 @@ def pbs_indexer(graph_path, seed, n_jobs, results_folder, walltime, request, spa
 @click.command()
 @click.argument('graph_path')
 @click.argument('job_id', type=int)
-@click.argument('n_jobs', type=int)
-@click.argument('cs_path')
+@click.argument('n_samps', type=int)
 @click.argument('results_folder')
-def dist_partitions(graph_path, job_id, n_jobs, cs_path, results_folder):
+def dist_partitions(graph_path, job_id, n_samps, results_folder):
     """
     Distributed partition job task
     :return:
     """
     graph = load_graph(graph_path)
 
-    with open(cs_path) as csf:
-        starting_cut_sets = json.load(csf)
-
-    n_samps = int(len(starting_cut_sets) / n_jobs)
[…]

### 2018-04-26 cluster_query_tool/louvain_consensus.py

@@ -58,7 +58,7 @@ def gen_local_optima_community(graph, cut_set=None):
     """
     # The possible space of communities is huge!
     if cut_set is None:
-       cut_set = random.sample(graph.edges(), random.randint(1, graph.number_of_edges()))
+        cut_set = random.sample(graph.edges(), random.randint(1, graph.number_of_edges()))
     # convert to partition
     start_partition = create_partition_from_edge_set(graph, cut_set)
     local_optima = louvain.best_partition(graph, partition=start_partition)

### 2018-04-26 experiments/lfr_overlap.py

@@ -25,6 +25,11 @@ _seed_sizes = [1, 3, 7, 15]
 
 
 @click.command()
+def gen_partition_spaces():
+    pass
+
+
+@click.command()
 @click.argument("n")
 @click.argument("ol")
 @click.argument("seed")

### 2018-04-26 article/article.tex
Fixed overlapping experiment
Changes to indexer
more changes to article and updated query set aulity analysis

@@
 \usepackage{booktabs}
-
-\DeclareMathOperator*{\argmax}{argmax}
-
-\date{Received: date / Accepted: date}
 
@@
 
+\begin{figure*}[ht]
+    \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/lfr_binary_overlap_auc_1000.eps}
+        \caption{1000 nodes}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/lfr_binary_overlap_auc_1000.eps}
+        \caption{5000 nodes}
+    \end{subfigure}
+    \caption{Overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
+     Data points represent mean auc scores for all communities on 100 sampled networks at varying overlapping fraction of nodes.
+     Error bars represent standard deviations.}
+\end{figure*}
+
 \subsection{Real networks}
@@
 (B) Shows a reduced view of the network where a threshold is selected, reducing the network to 404 nodes.
-(C) Shows an example ROC curve, sampled from combinations of using 3 randomly selected query nodes including this term.
 Blue nodes indicate those in the randomly selected 3 query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
+(C) Shows an example ROC curve from the cross validation described in the main text. 
+Based on 3 randomly selected query nodes containing this GO term.
 }
@@
 
-\bibliographystyle{IEEEtran} 
+\bibliographystyle{acm} 
 \bibliography{references}

### 2018-04-26 cluster_query_tool/louvain_consensus.py

@@ -4,7 +4,6 @@ import networkx as nx
 import random
 import numpy as np
 from scipy.stats import mannwhitneyu
-from itertools import combinations
 from numba import jit
 
 
@@ -168,11 +167,17 @@ def membership_matrix(nodes, partitions):
     return M, nmap
 
 
-def s_quality(query_nodes, nmap, M):
-    Mx = []
-    for i, j in combinations(set([nmap[i] for i in query_nodes]), 2):
-        Mx.append((M[i] == M[j]).sum(axis=0) * 1 / M.shape[1])
-    return np.mean(Mx), np.std(Mx)
+def quality_score(query_indexes, M):
+    """
+
+    :param query_indexes:
+    :param M:
+    :return:
+    """
+    vec = query_vector(query_indexes, M)
+    nset = np.array([x for x in range(vec.shape[0]) if x not in query_indexes])
+    u_score, pvalue = mannwhitneyu(vec[nset], vec[query_indexes])
+    return pvalue
 
 
 @jit(nopython=True, nogil=True)

### 2018-04-30 article/article.tex
boilerplate

@@
 
-\begin{figure*}
+\begin{figure}[ht]
+    \includegraphics[width=0.45\textwidth]{images/search_space_3.png}
+    \caption{Modularity search space of an \textit{E. coli} metabolic network.
+ Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
+  The inset (top) demonstrates the landscape of the high modularity region. 
+  Figure generated with the software of Good \textit{et al.}\cite{good2010performance}.}
+    \label{fig:modular_search_space}
+\end{figure}
+
+\begin{figure}[ht]
     \centering
-
-  \begin{subfigure}[ht]{0.4\textwidth}
-    \includegraphics[width=\textwidth]{images/search_space_3.png}
-    \caption{Modularity optimisation space of an \textit{E. coli} metabolic network.}
-    \label{fig:modular_search_space}
-  \end{subfigure}
-  \begin{subfigure}[ht]{0.58\textwidth}
-    \centering
-    \includegraphics[width=\textwidth]{images/meth_fig/fig1_desc.eps}
+    \includegraphics[width=0.45\textwidth]{images/meth_fig/fig1_desc.eps}
     \caption{Outline of the proposed approach to querying networks by using multiple, high quality representations of modular networks.}
     \label{fig:algorithm_outline}
-  \end{subfigure}
- \caption{
- Modularity search space of an \textit{E. coli} metabolic network.
- Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
-  The inset (top) demonstrates the landscape of the high modularity region. 
-  Figure generated with the software of Good \textit{et al.}\cite{good2010performance}.
- }
-\end{figure*}
+\end{figure}
 
@@
 \subsection{Synthetic networks}
-In this section we test the method on a number benchmark networks constructed with a known, ground-truth community structure.
-To evaluate how our method performs we demonstrate results against two benchmark networks the conventionally used LFR benchmark \cite{lfr} for community detection algorithms.
+In this section we test the method on benchmark networks constructed with a known, ground-truth community structure.
+To evaluate how our method performs we use the undirected, unweighted LFR benchmark \cite{lancichinetti2008benchmark} in overlapping and non-overlapping forms.
 We test the area under the ROC curve (AUC) scores for networks synthetically generated with the LFR benchmark.
-The community distribution is defined with a powerlaw coefficient of $-1.0$ and the degree distribution is defined with a powerlaw coefficient of $-2.0$.
-\textbf{Non-overlapping modules.} Figure \ref{fig:auc_no_overlap} represents tests on 100 networks with different randomly selected seed nodes.
+In these tests, the community distribution is defined with a powerlaw coefficient of $-1.0$, the degree distribution is defined with a powerlaw coefficient of $-2.0$ and the number of nodes is stated.
+
+\textbf{Non-overlapping modules.} Figure \ref{fig:auc_no_overlap} represents tests on 100 networks with 1000 and 5000 nodes varying the mixing coefficient (number of edges between communities).
 As one would expect, the prediction of the method drops off steeply where communities are less defined above a mixing coefficient of 0.6.
 Using larger seed sets also improves accuracy with some prediction of true communities being possible at extremely high levels of mixing.
+
+\textbf{Overlapping modules.} 
+In figure \ref{fig:auc_overlap} we show the results of network performance when tested against an increasing level of overlapping communities.
+For these tests we fix the mixing coefficient at $0.3$.
+Here, each vertex can belong to up to 4 communities.
+In order to test performance we varied the fraction of nodes that are in more than one community.
+Interestingly, the method still has an AUC score above 0.5 when all nodes are placed in multiple communities.
+This indicates that the method is capable of uncovering latent overlapping memberships even when given a relatively small number of seed nodes.
 
@@
      Error bars represent standard deviations.}
+     \label{fig:auc_no_overlap}
 \end{figure*}
@@
         \centering
-        \includegraphics[width=\textwidth]{images/lfr_binary_overlap_auc_1000.eps}
+        \includegraphics[width=\textwidth]{images/lfr_binary_overlap_auc_5000.eps}
         \caption{5000 nodes}
@@
      Error bars represent standard deviations.}
+     \label{fig:auc_overlap}
 \end{figure*}
@@
 (A) Shows the full network with 3 randomly chosen query nodes from the full query set.
-(B) Shows a reduced view of the network where a threshold is selected, reducing the network to 404 nodes.
+(B) Shows a reduced view of the network where a threshold of $\mu_i(S) > 0.8$ is selected, reducing the network to 404 nodes.
 Blue nodes indicate those in the randomly selected 3 query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.

### 2018-04-30 experiments/lfr_overlap.py

@@ -169,6 +169,7 @@ def gen_figure(n):
         ax.errorbar(x_vals/ int(n), y_vals, yerr=y_err)
 
     ax.legend(loc=3)
+    fig.tight_layout()
     fig.savefig("article/images/lfr_binary_overlap_auc_{}.eps".format(n))
     fig.savefig("article/images/lfr_binary_overlap_auc_{}.svg".format(n))
     fig.savefig("article/images/lfr_binary_overlap_auc_{}.png".format(n))

### 2018-04-30 experiments/real_networks.py

@@ -1,0 +1,53 @@
+import networkx as nx
+from cluster_query_tool import louvain_consensus
+from cluster_query_tool.indexer import get_index
+from .experiments import fast_auc
+
+
+def load_network(graph_path, graph_name, communities_path):
+    """
+    Load a real network into an nx Graph.
+    Return tuple graph, communities, membership_matrix, node_mapping
+    :param graph_path:
+    :param graph_name:
+    :param communities_path:
+    :return:
+    """
+    pass
+
+
+def get_community_significance_scores(graph, membership_matrix, nmap, communities):
+    """
+    Return the community signifcance scores for a network
+    :param graph:
+    :param membership_matrix:
+    :param nmap:
+    :param communities:
+    :return:
+    """
+    pass
+
+
+def get_roc_scores(graph, membership_matrix, nmap, communities):
+    pass
+
+
+def get_auc_scores(graph, membership_matrix, nmap, communities):
+    pass
+
+
+def plot_roc_curve(roc_df, save_path):
+    """
+    Takes a dataframe of roc curves at different seeds and plots the mean roc curves
+
+    Separates the results into different seed set sizes
+    computes an interpolated curve along with standard deviations in coloured shaded areas.
+
+    Returns matplotlib axis and fig objects
+
+    Labels incluse the mean AUC with standard deviations
+    :param roc_df:
+    :param save_path:
+    :return:
+    """
+    pass

### 2018-04-30 experiments/lfr_nooverlap.py
figure tidied up

@@ -165,6 +165,7 @@ def gen_figure(n):
         ax.errorbar(x_vals, y_vals, yerr=y_err)
 
     ax.legend(loc=3)
+    fig.tight_layout()
     fig.savefig("article/images/lfr_binary_mo_overlap_auc_{}.eps".format(n))
     fig.savefig("article/images/lfr_binary_mo_overlap_auc_{}.svg".format(n))
     fig.savefig("article/images/lfr_binary_mo_overlap_auc_{}.png".format(n))

### 2018-04-30 article/article.tex
figure tidied up
Real networks experiments

@@
 \documentclass[sigconf]{acmart}
+
+\usepackage{booktabs} % For formal tables
+
+% Copyright
+%\setcopyright{none}
+%\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}
+\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
+
+% DOI
+\acmDOI{10.475/123_4}
+
+% ISBN
+\acmISBN{123-4567-24-567/08/06}
+
+%Conference
+\acmConference[]{}{}{}
+\acmYear{2018}
+\copyrightyear{2018}
+
 \usepackage[utf8]{inputenc}
@@
 
+\begin{figure}[ht]
+    \includegraphics[width=0.45\textwidth]{images/search_space_3.png}
+    \caption{Modularity search space of an \textit{E. coli} metabolic network.
+ Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
+  The inset (top) demonstrates the landscape of the high modularity region. 
+  Figure generated with the software of Good \textit{et al.}\cite{good2010performance}.}
+    \label{fig:modular_search_space}
+\end{figure}
+
 \section{Exploiting the modularity query space}
@@
 The similarity between the partitions is compared with variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear}.
-
-\begin{figure}[ht]
-    \includegraphics[width=0.45\textwidth]{images/search_space_3.png}
-    \caption{Modularity search space of an \textit{E. coli} metabolic network.
- Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
-  The inset (top) demonstrates the landscape of the high modularity region. 
-  Figure generated with the software of Good \textit{et al.}\cite{good2010performance}.}
-    \label{fig:modular_search_space}
-\end{figure}
 
@@
 
-\textbf{Non-overlapping modules.} Figure \ref{fig:auc_no_overlap} represents tests on 100 networks with 1000 and 5000 nodes varying the mixing coefficient (number of edges between communities).
+\subsubsection{Non-overlapping modules.}
+Figure \ref{fig:auc_no_overlap} represents tests on 100 networks with 1000 and 5000 nodes varying the mixing coefficient (number of edges between communities).
 As one would expect, the prediction of the method drops off steeply where communities are less defined above a mixing coefficient of 0.6.
 Using larger seed sets also improves accuracy with some prediction of true communities being possible at extremely high levels of mixing.
-
-\textbf{Overlapping modules.} 
-In figure \ref{fig:auc_overlap} we show the results of network performance when tested against an increasing level of overlapping communities.
-For these tests we fix the mixing coefficient at $0.3$.
-Here, each vertex can belong to up to 4 communities.
-In order to test performance we varied the fraction of nodes that are in more than one community.
-Interestingly, the method still has an AUC score above 0.5 when all nodes are placed in multiple communities.
-This indicates that the method is capable of uncovering latent overlapping memberships even when given a relatively small number of seed nodes.
 
@@
 
+\subsubsection{Overlapping modules.} 
+In figure \ref{fig:auc_overlap} we show the results of network performance when tested against an increasing level of overlapping communities.
+For these tests we fix the mixing coefficient at $0.3$.
+Here, each vertex can belong to up to 4 communities.
+In order to test performance we varied the fraction of nodes that are in more than one community.
+Interestingly, the method still has an AUC score above 0.5 when all nodes are placed in multiple communities.
+This indicates that the method is capable of uncovering latent overlapping memberships even when given a relatively small number of seed nodes.
+
 \begin{figure*}[ht]
@@
 \end{figure*}
+
+\subsubsection{Cluster significance}
+In this section we evaluate the method for testing labels to discover significant communities by comparing the scores to randomly selected communities.
+In order to do this, we
 

### 2018-04-30 experiments/experiments.py

@@ -47,7 +47,7 @@ def get_benchmark(params, num_procs=4):
     return graph, communities, get_index(graph, num_procs=num_procs)
 
 
-def unique_sampler(node_set, sample_size, max_samples=96):
+def unique_sampler(node_set, sample_size, max_samples=120):
     sample_sets = set()
 
     # maximum number of samples

### 2018-04-30 experiments/real_networks.py

@@ -1,39 +1,120 @@
 import networkx as nx
 from cluster_query_tool import louvain_consensus
 from cluster_query_tool.indexer import get_index
-from .experiments import fast_auc
+from experiments import fast_auc, unique_sampler
+from joblib import Parallel, delayed, cpu_count
+import json
+from sklearn.metrics import roc_curve
+import numpy as np
+import os
+
+real_networks = {
+    "arabidopsis_ppi": {
+        "path": "data/arabidopsis_ppi/arabadopsis_ppi.edgelist",
+        "clusters": "data/arabidopsis_ppi/complexes.json",
+        "index": "data/arabidopsis_ppi/index.json.xz",
+        "node_type": "str",
+    },
+    "yeast_ppi": {
+        "path": "data/yeast_ppi/yeast.edgelist",
+        "clusters": "data/yeast_ppi/yeast_ppi.json",
+        "index": "data/yeast_ppi/index.json.xz",
+        "node_type":"str",
+    },
+    "eu_email": {
+        "path": "data/eu_email/network.txt",
+        "clusters": "data/eu_email/communities.json",
+        "index": "data/eu_email/index.json.xz",
+        "node_type": "int",
+    }
+}
 
 
-def load_network(graph_path, graph_name, communities_path):
+def load_network(graph_path, graph_name, communities_path, index_path, node_type):
     """
     Load a real network into an nx Graph.
     Return tuple graph, communities, membership_matrix, node_mapping
     :param graph_path:
     :param graph_name:
     :param communities_path:
+    :param index_path
     :return:
     """
-    pass
+    nt = str
+    if node_type == "int":
+        nt = int
+
+    graph = nx.read_edgelist(graph_path, nodetype=nt)
+    graph.name = graph_name
+
+    with open(communities_path) as cp:
+        comms = json.load(cp)
+
+    index = get_index(graph, cache_location=index_path)
+    mmatrix, nmap = louvain_consensus.membership_matrix(list(graph.nodes()), index)
+    return graph, comms, mmatrix, nmap
 
 
-def get_community_significance_scores(graph, membership_matrix, nmap, communities):
+def comm_significance(cid, comm, membership_matrix):
+    return cid, louvain_consensus.quality_score(comm, membership_matrix)
+
+
+def map_com(cnodes, nmap):
[…]

### 2018-05-01 article/article.tex
Added yeast stuff

@@
 
-\usepackage{booktabs} % For formal tables
-
 % Copyright
-%\setcopyright{none}
+\setcopyright{none}
 %\setcopyright{acmcopyright}
 %\setcopyright{acmlicensed}
-\setcopyright{rightsretained}
+%\setcopyright{rightsretained}
 %\setcopyright{usgov}
@@
 % DOI
-\acmDOI{10.475/123_4}
+\acmDOI{}
 
 % ISBN
-\acmISBN{123-4567-24-567/08/06}
+\acmISBN{}
 
@@
 \subsection{Statistically significant query sets}
+\label{sec:query_sign}
 Naturally, not every label set will be of high quality or represented within the community structure of a network.
@@
 
-\subsubsection{Cluster significance}
-In this section we evaluate the method for testing labels to discover significant communities by comparing the scores to randomly selected communities.
-In order to do this, we
-
 \subsection{Real networks}
@@
 
+\subsubsection{High quality labels}
 We tested the method on each real network described in section \ref{sec:real_network_descs}.
@@
 
-\subsection{Gene ontology data}
+\subsubsection{Gene ontology data}
 \label{sec:go_labels}
+In this section we analyse the performance of our method on gene ontology data for the protein interaction networks in this study.
+Unlike the the curated protein complexes and known departmental memberships in Section \ref{sec:real_network_labels}, gene ontology cannot be considered fully relevant in all cases.
+Specific terms may have no relevance in the context of protein-protein interactions, and many terms are extremely general.
+Consequently, we cannot expect the labels to perform well in this context.
+Therefore, we use the query set significance testing outlined in Section \ref{sec:query_sign}.
+The data used in this study contains all non-redundant gene ontology terms available for proteins contained within a network from AmiGO \cite{carbon2008amigo}.
+The purpose of this test is not to find biologically relevant information but, rather, to show how the method presented here can be tuned to evaluate poor quality label sets.
 

### 2018-05-01 experiments/real_networks.py
real network logging

@@ -141,6 +141,7 @@ def generate_results(network, overwrite=False):
     roc_df_path = os.path.join("results", graph.name) + "roc_res.json"
 
     if overwrite or not os.path.exists(roc_df_path):
+        print(network, "gen_roc_curves")
         roc_results = get_rocs(mmatrix, nmap, comms)
         with open(roc_df_path, "w+") as roc_df:
             json.dump(roc_results, roc_df)
@@ -149,11 +150,12 @@ def generate_results(network, overwrite=False):
 
     if overwrite or not os.path.exists(sign_df_path):
         sigscores = get_community_significance_scores(mmatrix, nmap, comms)
-
+        print(network, "gen_sig_scores")
         with open(sign_df_path, "w+") as sig_df:
             json.dump(sigscores, sig_df)
 
 
 if __name__ == "__main__":
     for n in real_networks:
+        print(n)
         generate_results(n)

### 2018-05-01 experiments/real_networks.py
broken path

@@ -10,7 +10,7 @@ import os
 
 real_networks = {
     "arabidopsis_ppi": {
-        "path": "data/arabidopsis_ppi/arabadopsis_ppi.edgelist",
+        "path": "data/arabidopsis_ppi/arabidopsis_ppi.edgelist",
         "clusters": "data/arabidopsis_ppi/int_act_complexes.json",
         "index": "data/arabidopsis_ppi/index.json.xz",
         "node_type": "str",

### 2018-05-01 experiments/real_networks.py
prune communities to only those in network

@@ -52,7 +52,14 @@ def load_network(graph_path, graph_name, communities_path, index_path, node_type
 
     index = get_index(graph, cache_location=index_path)
     mmatrix, nmap = louvain_consensus.membership_matrix(list(graph.nodes()), index)
-    return graph, comms, mmatrix, nmap
+
+    rcomms = dict()
+    for c in comms:
+        nc = [x for c in comms[c] if x in nmap]
+        if len(nc) > 2:
+            rcomms[c] = nc
+
+    return graph, rcomms, mmatrix, nmap
 
 
 def comm_significance(cid, comm, membership_matrix):

### 2018-05-01 experiments/real_networks.py
prune communities to only those in network

@@ -55,7 +55,7 @@ def load_network(graph_path, graph_name, communities_path, index_path, node_type
 
     rcomms = dict()
     for c in comms:
-        nc = [x for c in comms[c] if x in nmap]
+        nc = [x for x in comms[c] if x in nmap]
         if len(nc) > 2:
             rcomms[c] = nc
 

### 2018-05-01 experiments/real_networks.py
progressbar

@@ -7,6 +7,8 @@ import json
 from sklearn.metrics import roc_curve
 import numpy as np
 import os
+import progressbar
+
 
 real_networks = {
     "arabidopsis_ppi": {
@@ -116,7 +118,8 @@ def get_rocs(mmatrix, nmap, comms, seed_sizes=(1, 3, 7, 15)):
     """
 
     res = []
-    for cid, comm in comms.items():
+
+    for cid, comm in progressbar.progressbar(comms.items()):
         cnodes = map_com(comm, nmap)
         for s in seed_sizes:
             if len(comm) > s:

### 2018-05-01 experiments/real_networks.py
underscores!

@@ -148,7 +148,7 @@ def generate_results(network, overwrite=False):
     dt = real_networks[network]
     graph, comms, mmatrix, nmap = load_network(dt["path"], network, dt["clusters"], dt["index"], dt["node_type"])
 
-    roc_df_path = os.path.join("results", graph.name) + "roc_res.json"
+    roc_df_path = os.path.join("results", graph.name) + "_roc_res.json"
 
     if overwrite or not os.path.exists(roc_df_path):
         print(network, "gen_roc_curves")
@@ -156,7 +156,7 @@ def generate_results(network, overwrite=False):
         with open(roc_df_path, "w+") as roc_df:
             json.dump(roc_results, roc_df)
 
-    sign_df_path = os.path.join("results", graph.name) + "sign_res.json"
+    sign_df_path = os.path.join("results", graph.name) + "_sign_res.json"
 
     if overwrite or not os.path.exists(sign_df_path):
         sigscores = get_community_significance_scores(mmatrix, nmap, comms)

### 2018-05-01 experiments/real_networks.py
pickles

@@ -4,6 +4,7 @@ from cluster_query_tool.indexer import get_index
 from experiments import fast_auc, unique_sampler
 from joblib import Parallel, delayed, cpu_count
 import json
+import pickle
 from sklearn.metrics import roc_curve
 import numpy as np
 import os
@@ -148,21 +149,21 @@ def generate_results(network, overwrite=False):
     dt = real_networks[network]
     graph, comms, mmatrix, nmap = load_network(dt["path"], network, dt["clusters"], dt["index"], dt["node_type"])
 
-    roc_df_path = os.path.join("results", graph.name) + "_roc_res.json"
+    roc_df_path = os.path.join("results", graph.name) + "_roc_res.p"
 
     if overwrite or not os.path.exists(roc_df_path):
         print(network, "gen_roc_curves")
         roc_results = get_rocs(mmatrix, nmap, comms)
         with open(roc_df_path, "w+") as roc_df:
-            json.dump(roc_results, roc_df)
+            pickle.dump(roc_results, roc_df)
 
-    sign_df_path = os.path.join("results", graph.name) + "_sign_res.json"
+    sign_df_path = os.path.join("results", graph.name) + "_sign_res.p"
 
     if overwrite or not os.path.exists(sign_df_path):
         sigscores = get_community_significance_scores(mmatrix, nmap, comms)
         print(network, "gen_sig_scores")
         with open(sign_df_path, "w+") as sig_df:
-            json.dump(sigscores, sig_df)
+            pickle.dump(sigscores, sig_df)
 
 
 if __name__ == "__main__":

### 2018-05-01 experiments/real_networks.py
pickles

@@ -154,7 +154,7 @@ def generate_results(network, overwrite=False):
     if overwrite or not os.path.exists(roc_df_path):
         print(network, "gen_roc_curves")
         roc_results = get_rocs(mmatrix, nmap, comms)
-        with open(roc_df_path, "w+") as roc_df:
+        with open(roc_df_path, "wb+") as roc_df:
             pickle.dump(roc_results, roc_df)
 
     sign_df_path = os.path.join("results", graph.name) + "_sign_res.p"
@@ -162,7 +162,7 @@ def generate_results(network, overwrite=False):
     if overwrite or not os.path.exists(sign_df_path):
         sigscores = get_community_significance_scores(mmatrix, nmap, comms)
         print(network, "gen_sig_scores")
-        with open(sign_df_path, "w+") as sig_df:
+        with open(sign_df_path, "wb+") as sig_df:
             pickle.dump(sigscores, sig_df)
 
 

### 2018-05-01 article/article.tex
gos

@@
 
-\begin{figure}[ht]
+\begin{figure}[t]
     \includegraphics[width=0.45\textwidth]{images/search_space_3.png}
@@
 
-\begin{figure}[ht]
+\begin{figure}[t]
     \centering
@@
 
-\begin{figure*}[ht]
+\begin{figure}[t]
     \centering
-    \begin{subfigure}[b]{0.48\textwidth}
+    \begin{subfigure}[b]{0.23\textwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.48\textwidth}
+    \begin{subfigure}[b]{0.23\textwidth}
         \centering
@@
      \label{fig:auc_no_overlap}
-\end{figure*}
+\end{figure}
 
@@
      \label{fig:auc_overlap}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[ht]
+\begin{figure*}[t]
 \includegraphics[width=\textwidth]{images/ppi_example_combined.eps}
@@
 
- \item \textbf{Yeast protein-protein interaction network (Yeast PPI)} \cite{yeast_ppi}
+ \item \textbf{Yeast protein-protein interaction network (Yeast PPI)} \cite{yu2008high}
  This dataset is a collection of recorded binary interactions between proteins collected with high-throughput yeast-2-hybrid assays.
- The metadata used are known, experimentally validated protein complexes from \cite{yeast_ppi_complexes}.
+ The metadata used are known, experimentally validated protein complexes from \cite{pu2008up}.
  The network contains 6222 nodes in the largest connected component, with 22,3868 edges.
@@
  The protein complexes are typically very small in terms of number of proteins with  90\% of the complexes containing less than 10 proteins and only 2 complexes containing 50 or more proteins.
+
+ \item \textbf{Arabidopsis protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}
 

### 2018-05-01 experiments/real_networks.py

@@ -10,12 +10,20 @@ import numpy as np
 import os
 import progressbar
 import pandas as pd
+import matplotlib.pyplot as plt
+from scipy import interp
 
 
 real_networks = {
     "arabidopsis_ppi": {
         "path": "data/arabidopsis_ppi/arabidopsis_ppi.edgelist",
         "clusters": "data/arabidopsis_ppi/int_act_complexes.json",
+        "index": "data/arabidopsis_ppi/index.json.xz",
+        "node_type": "str",
+    },
+    "arabidopsis_ppi_go_complexes": {
+        "path": "data/arabidopsis_ppi/arabidopsis_ppi.edgelist",
+        "clusters": "data/arabidopsis_ppi/go_complexes.json",
         "index": "data/arabidopsis_ppi/index.json.xz",
         "node_type": "str",
     },
@@ -129,7 +137,7 @@ def get_rocs(mmatrix, nmap, comms, seed_sizes=(1, 3, 7, 15)):
     return res
 
 
-def plot_roc_curve(roc_df, save_path):
+def plot_roc_curve(df, save_path):
     """
     Takes a dataframe of roc curves at different seeds and plots the mean roc curves
 
@@ -143,7 +151,51 @@ def plot_roc_curve(roc_df, save_path):
     :param save_path:
     :return:
     """
-    pass
+    colours = {
+        1: "b",
+        3: "g",
+        7: "y",
+        15: "m"
+    }
+
+    fig, ax = plt.subplots()
+    fig.set_dpi(90)
+
+    ax.set_xlabel("False positive rate")
+    ax.set_ylabel("True positive rate")
+
+    ax.set_xlim([0.0, 1.0])
+    ax.set_ylim([0.0, 1.01])
+    ax.plot(np.linspace(0, 1, 100), np.linspace(0, 1, 100), '--', color="#cccccc")
+
+    for s in df["seed"].unique():
+
+        sdf = df.loc[df["seed"] == s]
+
+        tprs = []
+        base_fpr = np.linspace(0, 1, 101)
+
+        for rid, row in sdf.iterrows():
+            tpr = interp(base_fpr, row["tpr"], row["fnr"])
+            tpr[0] = 0.0
+            tprs.append(tpr)
+
+        tprs = np.array(tprs)
+        mean_tprs = tprs.mean(axis=0)
+        std = tprs.std(axis=0)
+
+        tprs_upper = np.minimum(mean_tprs + std, 1)
[…]

### 2018-05-01 experiments/real_networks.py
gos

@@ -195,16 +195,16 @@ def plot_roc_curve(df, save_path):
         ax.legend()
 
     fig.tight_layout()
-    fig.save_fig(save_path)
+    fig.savefig(save_path)
 
 
 def generate_results(network, overwrite=False):
     dt = real_networks[network]
-    graph, comms, mmatrix, nmap = load_network(dt["path"], network, dt["clusters"], dt["index"], dt["node_type"])
 
-    roc_df_path = os.path.join("results", graph.name) + "_roc_res.p"
+    roc_df_path = os.path.join("results", network) + "_roc_res.p"
 
     if overwrite or not os.path.exists(roc_df_path):
+        graph, comms, mmatrix, nmap = load_network(dt["path"], network, dt["clusters"], dt["index"], dt["node_type"])
         print(network, "gen_roc_curves")
         roc_results = get_rocs(mmatrix, nmap, comms)
         with open(roc_df_path, "wb+") as roc_df:
@@ -213,10 +213,11 @@ def generate_results(network, overwrite=False):
     sign_df_path = os.path.join("results", graph.name) + "_sign_res.p"
 
     if overwrite or not os.path.exists(sign_df_path):
+        graph, comms, mmatrix, nmap = load_network(dt["path"], network, dt["clusters"], dt["index"], dt["node_type"])
         sigscores = get_community_significance_scores(mmatrix, nmap, comms)
         print(network, "gen_sig_scores")
         with open(sign_df_path, "wb+") as sig_df:
-            pickle.dump(sigscores, sig_df)
+           pickle.dump(sigscores, sig_df)
 
 
 def handle_results(network):
@@ -227,15 +228,17 @@ def handle_results(network):
     with open(roc_df_path, "rb") as rf:
         results = pickle.load(rf)
 
-    headings = ["cid", "s", "tpr", "fnr", "auc"]
+    headings = ["cid", "seed", "tpr", "fnr", "auc"]
 
-    df = pd.DataFrame(results, names=headings)
-
+    df = pd.DataFrame(results, columns=headings)
+    plot_roc_curve(df, "article/images/rocs/{}.png".format(network))
+    plot_roc_curve(df, "article/images/rocs/{}.svg".format(network))
+    plot_roc_curve(df, "article/images/rocs/{}.eps".format(network))
     return df
 
 
 if __name__ == "__main__":
     for n in real_networks:
         print(n)
-        #generate_results(n)
+        generate_results(n)
         handle_results(n)

### 2018-05-01 experiments/real_networks.py
gos

@@ -210,7 +210,7 @@ def generate_results(network, overwrite=False):
         with open(roc_df_path, "wb+") as roc_df:
             pickle.dump(roc_results, roc_df)
 
-    sign_df_path = os.path.join("results", graph.name) + "_sign_res.p"
+    sign_df_path = os.path.join("results", network) + "_sign_res.p"
 
     if overwrite or not os.path.exists(sign_df_path):
         graph, comms, mmatrix, nmap = load_network(dt["path"], network, dt["clusters"], dt["index"], dt["node_type"])

### 2018-05-01 experiments/real_networks.py
gos

@@ -10,6 +10,8 @@ import numpy as np
 import os
 import progressbar
 import pandas as pd
+import matplotlib as mpl
+mpl.use('Agg')
 import matplotlib.pyplot as plt
 from scipy import interp
 

### 2018-05-01 article/article.tex
ecoli_ppi

@@
 
- \item \textbf{Arabidopsis protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}
+ \item \textbf{\textit{Arabidopsis thaliana} protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}
+
+ \item \textbf{\textit{Escherichia coli} protein-protein interaction network (E.coli PPI)}
 
@@
 
-% \begin{figure*}
-%      \centering
-%     \begin{subfigure}[b]{0.48\textwidth}
-%         \centering
-%         \includegraphics[width=\textwidth]{images/eu_roc_scores.eps}
-%         \caption{EU email departments}
-%     \end{subfigure}
-%     \begin{subfigure}[b]{0.48\textwidth}
-%         \centering
-%         \includegraphics[width=\textwidth]{images/yeast_ppi_roc_scores.eps}
-%         \caption{Yeast PPI protein complexes}
-%     \end{subfigure}
-%     \caption{Mean area under RO curve (AUC) scores from cross-validation performed on Metadata communities for networks described in Section \ref{sec:real_network_descs}.
-%     Dashed line indicates an AUC score of 0.5 (random chance).
-%     Communities are ordered by size.
-%     Error bars indicate standard deviation.
-%     }
-%     \label{fig:real_network_results}
-% \end{figure*}
+\begin{figure*}
+     \centering
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/rocs/eu_email.png}
+        \caption{EU email departments}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/rocs/yeast_ppi.png}
+        \caption{Yeast PPI protein complexes}
+    \end{subfigure}
+
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi.png}
+        \caption{Arabidopsis PPI protein complexes}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.48\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi_go_complexes.png}
+        \caption{E coli PPI protein complexes}
+    \end{subfigure}
+    \caption{ROC scores for the high quality labels for real networks described in Section \ref{sec:real_network_descs}. 
+    Results represent the averages over all label sets.
+    Shaded areas indicate standard deviations.}
+    \label{fig:quality_label_rocs}
+\end{figure*}
 % 
 % 
-% \begin{figure*}
-%     \centering
-%     \begin{subfigure}[b]{0.48\textwidth}
-%         \centering
-%         \includegraphics[width=\textwidth]{images/eu_email_nodewise_roc.eps}
-%         \caption{EU email departments (986 nodes)}
-%     \end{subfigure}
-%     \begin{subfigure}[b]{0.48\textwidth}
-%         \centering
-%         \includegraphics[width=\textwidth]{images/yeast_ppi_nodewise_roc.eps}
-%         \caption{Yeast PPI protein complexes (1628 nodes)}
-%     \end{subfigure}
-%     \caption{Receiver Operator Characteristic curves for node communities.
-%     Dashed line indicates an AUC score of 0.5 (random chance).
-%     Represents mean, shaded area indicates standard deviation.
-%     }
-%     \label{fig:real_network_nodwise_classifiers}
-% \end{figure*}
+\subsubsection{High quality labels}
+In this section we observe the performance of our method on the real networks described in Section \ref{sec:real_network_descs} with high quality, gold standard, curated labels.
+For the EU Emails dataset, the communities relate to real departments of individuals.
+For the protein interaction datasets we used manually curated interaction sets.
+In the case of the Yeast this was taken from experimentally validated complexes  \cite{pu2008up}.
+For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{}.
+For the Arabidopsis dataset, the complex sources were more limited.
+Consequently, the IntAct database was used with all protein complexes listed containing less than 10 proteins in total \cite{}.
 
-\subsubsection{High quality labels}
-We tested the method on each real network described in section \ref{sec:real_network_descs}.
-Figure \ref{fig:real_network_results} shows the mean ROC scores for each community in the relevant networks, organised by size of community at increasing numbers levels of query seed nodes.
-On the EU emails and Yeast PPI dataasets, for all communities tested with 3 or more nodes, mean AUC scores calculated with the cross validation method described in section \ref{sec:cross_validation} were above 0.6.
-There appeared to be no statistically significant improvements to using more than 3 seed nodes.
-
-The classification for individual nodes is presented in Figure \ref{fig:real_network_nodwise_classifiers}.
-Here, binary classification is performed on each node for which community data is available.
-The $mu_i({i})$ score is used as a binary classifier.
-For the EU email and Yeast PPI the average ROC AUC score to classify node membership inside communities is 0.9 and 0.93, respectively.
+The results with varying number of seed nodes, for the cross validation procedure described in Section \ref{sec:cross_validation} are shown in Figure \ref{fig:quality_label_rocs}.
+These results represent ROC and AUC statistics
 

### 2018-05-01 experiments/real_networks.py

@@ -23,6 +23,14 @@ real_networks = {
         "index": "data/arabidopsis_ppi/index.json.xz",
         "node_type": "str",
     },
+
+    "ecoli_ppi": {
+        "path": "data/ecoli_ppi/ecoli_ppi.edgelist",
+        "clusters": "data/ecoli_ppi/ecoli_ppi.json",
+        "index": "data/eu_email/index.json.xz",
+        "node_type": "str",
+    }
+
     "arabidopsis_ppi_go_complexes": {
         "path": "data/arabidopsis_ppi/arabidopsis_ppi.edgelist",
         "clusters": "data/arabidopsis_ppi/go_complexes.json",

### 2018-05-01 experiments/real_networks.py
ecoli_ppi

@@ -29,7 +29,7 @@ real_networks = {
         "clusters": "data/ecoli_ppi/ecoli_ppi.json",
         "index": "data/eu_email/index.json.xz",
         "node_type": "str",
-    }
+    },
 
     "arabidopsis_ppi_go_complexes": {
         "path": "data/arabidopsis_ppi/arabidopsis_ppi.edgelist",

### 2018-05-01 experiments/real_networks.py
ecoli_ppi

@@ -27,7 +27,7 @@ real_networks = {
     "ecoli_ppi": {
         "path": "data/ecoli_ppi/ecoli_ppi.edgelist",
         "clusters": "data/ecoli_ppi/ecoli_ppi.json",
-        "index": "data/eu_email/index.json.xz",
+        "index": "data/ecoli_ppi/index.json.xz",
         "node_type": "str",
     },
 

### 2018-05-01 article/article.tex
YAY

@@
 \affiliation{%
-  \institution{Synthetic biology research centre}
+  \institution{Synthetic Biology Research Centre}
   \streetaddress{University of Nottingham}
@@
         \centering
-        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi_go_complexes.png}
+        \includegraphics[width=\textwidth]{images/rocs/ecoli_ppi.png}
         \caption{E coli PPI protein complexes}
@@
     \caption{ROC scores for the high quality labels for real networks described in Section \ref{sec:real_network_descs}. 
-    Results represent the averages over all label sets.
+    Results represent the averages over all reciever operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.
     Shaded areas indicate standard deviations.}
@@
 This approach performs extremely well on both synthetically generated networks and real-world ground truth communities with relatively small sets of labels.
+However, in a practical application this would still require selecting some form of arbitrary cut off for defining \textit{crisp} communities.
 
-This work presents a number of interesting potential future avenues for research, such as observing how query sets change in time dynamic or multi-scale networks.
-Similarly, further analysis could be conducted to test how large the set of high value partitions needs to be, and how applicable this approach can be to very large graphs.
+This also work presents a number of interesting potential future avenues for research, such as observing how query sets change in time dynamic or multi-scale networks.
 
@@
 This work was supported by the Biotechnology and Biological Sciences Research Council grant BB/L013940/1.
+We would like to thank Nicole Pearcy for assistance with this manuscript.
 

### 2018-05-02 article/article.tex
sign

@@
 Given that there is no free lunch and it is impossible to know every solution, one can only ensure a full coverage index through an exhaustive search over the $2^m$ possible starting cut sets.
-Consequently, in the approach taken here is to use a large but not exhaustive subset of the possible solutions using 10,000 solutions for the large networks studied in this paper.
+Consequently, in the approach taken here is to use a large but not exhaustive subset of the possible solutions using 2000 solutions for the networks studied in this paper.
 
@@
 
-\subsection{Statistically significant query sets}
-\label{sec:query_sign}
-Naturally, not every label set will be of high quality or represented within the community structure of a network.
-This is established further in section \ref{sec:go_labels} which tests gene ontology terms (GO) on protein interaction networks.
-In this case, all the labels relate to the real function of the vertices, however, GO is a hierarchical system and many terms are extremely general.
-Furthermore, even for specific terms the network datasets will often not be well represented.
-A common approach with community detection and clustering (used for example in \cite{dekkers2013}) is to detect communities and find clusters containing significant GO terms.
-
-In this work, we would wish to use the community partition space, described above, to find highly related sets of vertices.
-For this we take the distribution, from Equation \ref{eq:mu_score} for a given query set.
-For a query set to be relevant it should be significantly more related than one would expect from a set of nodes selected at random within a network.
-
-Formally, given the partition space $\mathcal{P}$ and a query set $S$ we consider the distribution of quality scores as $\mu_i(S - i)$, for all $i$ in $S$.
-In order for $S$ to be a high quality query set, its value of internal vertices should be significantly higher than for external vertices.
-Formally, we assert that the distribution $\mu_i(S - i)$ should reject the null hypothesis that the mean is not significantly greater than $\mu_j(S)$ where $j \in S - V$, the set of vertices excluding those in the query set.
-For the purposes of this work we use the non-parametric Mann–Whitney $U$ test and reject the null hypothesis where $p < 0.001$.
-In section \ref{sec:go_labels} this is used to exclude less relevant GO terms.
+% \subsection{Statistically significant query sets}
+% \label{sec:query_sign}
+% Naturally, not every label set will be of high quality or represented within the community structure of a network.
+% This is established further in section \ref{sec:go_labels} which tests gene ontology terms (GO) on protein interaction networks.
+% In this case, all the labels relate to the real function of the vertices, however, GO is a hierarchical system and many terms are extremely general.
+% Furthermore, even for specific terms the network datasets will often not be well represented.
+% A common approach with community detection and clustering (used for example in \cite{dekkers2013}) is to detect communities and find clusters containing significant GO terms.
+% 
+% In this work, we would wish to use the community partition space, described above, to find highly related sets of vertices.
+% For this we take the distribution, from Equation \ref{eq:mu_score} for a given query set.
+% For a query set to be relevant it should be significantly more related than one would expect from a set of nodes selected at random within a network.
+% 
+% Formally, given the partition space $\mathcal{P}$ and a query set $S$ we consider the distribution of quality scores as $\mu_i(S - i)$, for all $i$ in $S$.
+% In order for $S$ to be a high quality query set, its value of internal vertices should be significantly higher than for external vertices.
+% Formally, we assert that the distribution $\mu_i(S - i)$ should reject the null hypothesis that the mean is not significantly greater than $\mu_j(S)$ where $j \in S - V$, the set of vertices excluding those in the query set.
+% For the purposes of this work we use the non-parametric Mann–Whitney $U$ test and reject the null hypothesis where $p < 0.001$.
+% In section \ref{sec:go_labels} this is used to exclude less relevant GO terms.
 
@@
     \centering
-    \begin{subfigure}[b]{0.23\textwidth}
+    \begin{subfigure}[b]{0.48\textwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.23\textwidth}
+
+    \begin{subfigure}[b]{0.48\textwidth}
         \centering
@@
 \subsection{Real networks}
+\label{sec:real_networks}
 
@@
 All datasets taken use the largest single connected component sub-graph.
-
-\subsubsection{Dataset descriptions}
-\label{sec:real_network_descs}
 The real networks used are listed as follows:
@@
  \item \textbf{\textit{Arabidopsis thaliana} protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}
+  For the Arabidopsis dataset, the complex sources were more limited.
+  Consequently, the IntAct database was used with all protein complexes listed containing less than 10 proteins in total \cite{}.
 
- \item \textbf{\textit{Escherichia coli} protein-protein interaction network (E.coli PPI)}
+  \item \textbf{\textit{Escherichia coli} protein-protein interaction network (E.coli PPI) \cite{}}
+  For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{}.
+\end{itemize}
 
-\end{itemize}
+The results with varying number of seed nodes, for the cross validation procedure described in Section \ref{sec:cross_validation} are shown in Figure \ref{fig:quality_label_rocs}.
+These results represent ROC curves and mean AUC statistics.
+For all the datasets in this study binary community classification is high, with an average AUC score above 0.88, even when using only a single seed node.
+In the case of the \textit{Arabidopsis thaliana} network the protein complexes tested are significantly smaller than for other networks and so a comparison of seed sizes is not possible.
+However, in the other networks studied using 3 or more seed nodes appears to improve results, though for 15 seed nodes the results are not significantly better than with 7 seeds.
 
@@
     \end{subfigure}
-    \caption{ROC scores for the high quality labels for real networks described in Section \ref{sec:real_network_descs}. 
+    \caption{ROC scores for the high quality labels for real networks described in Section \ref{sec:real_networks}. 
     Results represent the averages over all reciever operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.
@@
 \end{figure*}
-% 
-% 
-\subsubsection{High quality labels}
-In this section we observe the performance of our method on the real networks described in Section \ref{sec:real_network_descs} with high quality, gold standard, curated labels.
-For the EU Emails dataset, the communities relate to real departments of individuals.
-For the protein interaction datasets we used manually curated interaction sets.
-In the case of the Yeast this was taken from experimentally validated complexes  \cite{pu2008up}.
-For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{}.
-For the Arabidopsis dataset, the complex sources were more limited.
-Consequently, the IntAct database was used with all protein complexes listed containing less than 10 proteins in total \cite{}.
-
-The results with varying number of seed nodes, for the cross validation procedure described in Section \ref{sec:cross_validation} are shown in Figure \ref{fig:quality_label_rocs}.
-These results represent ROC and AUC statistics
-
-\subsubsection{Gene ontology data}
-\label{sec:go_labels}
-In this section we analyse the performance of our method on gene ontology data for the protein interaction networks in this study.
-Unlike the the curated protein complexes and known departmental memberships in Section \ref{sec:real_network_labels}, gene ontology cannot be considered fully relevant in all cases.
-Specific terms may have no relevance in the context of protein-protein interactions, and many terms are extremely general.
-Consequently, we cannot expect the labels to perform well in this context.
-Therefore, we use the query set significance testing outlined in Section \ref{sec:query_sign}.
-The data used in this study contains all non-redundant gene ontology terms available for proteins contained within a network from AmiGO \cite{carbon2008amigo}.
-The purpose of this test is not to find biologically relevant information but, rather, to show how the method presented here can be tuned to evaluate poor quality label sets.
+.
 
@@
 This paper has presented a novel approach to semi-supervised community detection utilising a consensus of high scoring partitions computed with the popular modularity maximisation approach.
-Previously the glassy search space of this optimisation algorithm has been seen as a major limitation of the approach.
+Previously the glassy search space of this optimisation algorithm has been seen as a major limitation.
 However, in this work we consider each locally optimal partition to be information regarding the true multi-class labels that are likely present in real networks.
-As the algorithm is trivial to run in a distributed manner, this approach can be applied to relatively large graphs.
-Further research can be conducted into this approach with alternative quality functions to modularity that do not suffer the same limitations in terms of a resolution limit.
+The approach presented here differs from other ensemble approaches in that the objective is to provide a probabilistic framework for label classification.
+Performance is extremely strong on both synthetically generated networks and real-world ground truth communities with relatively small sets of labels.
 
@@
 Similarly, the method presented here requires both some labelled data and the labels to be represented well within the topology of the underlying network.
-The approach presented here differs from other ensemble approaches in that the objective is to provide a probabilistic framework for label classification.
-This approach performs extremely well on both synthetically generated networks and real-world ground truth communities with relatively small sets of labels.
-However, in a practical application this would still require selecting some form of arbitrary cut off for defining \textit{crisp} communities.
 
 This also work presents a number of interesting potential future avenues for research, such as observing how query sets change in time dynamic or multi-scale networks.
+Furthermore, as the algorithm is trivial to run in a distributed manner, this approach could be applied to larger graphs than those studied in this paper.
+Further research should also be conducted into how this approach could be applied to other partition quality functions.
 

### 2018-05-02 experiments/lfr_nooverlap.py

@@ -117,7 +117,7 @@ def plot_csign(n, results_folder):
     df = pd.DataFrame(results, columns=["N", "SEED", "MU", "CID", "qscore", "c_size" ] )
     thresh = 0.001
 
-    xvals= sorted(df["MU"].unique())
+    xvals = sorted(df["MU"].unique())
 
     fig, ax = plt.subplots()
     fig.set_dpi(90)
@@ -130,9 +130,9 @@ def plot_csign(n, results_folder):
     std = []
     for m in xvals:
         frac_signficant = []
-        sdf = df.loc(df["MU"] == m)
-        for s in sdf.loc["SEED"].unique():
-            sdf2 = sdf.loc(sdf["SEED"] == s)
+        sdf = df.loc[df["MU"] == m]
+        for s in sdf["SEED"].unique():
+            sdf2 = sdf.loc[sdf["SEED"] == s]
             fr = (sdf2["qscore"] > thresh).sum()
 
             frac_signficant.append(((len(sdf) - fr)/len(sdf)))

### 2018-05-02 experiments/real_networks.py
impact os sample_space

@@ -31,12 +31,6 @@ real_networks = {
         "node_type": "str",
     },
 
-    "arabidopsis_ppi_go_complexes": {
-        "path": "data/arabidopsis_ppi/arabidopsis_ppi.edgelist",
-        "clusters": "data/arabidopsis_ppi/go_complexes.json",
-        "index": "data/arabidopsis_ppi/index.json.xz",
-        "node_type": "str",
-    },
     "yeast_ppi": {
         "path": "data/yeast_ppi/yeast.edgelist",
         "clusters": "data/yeast_ppi/yeast_ppi.json",
@@ -121,6 +115,21 @@ def samp_roc_and_auc(samp, mmatrix, comm, cid, s):
     return cid, s, tpr, fnr, auc
 
 
+def samp_auc(samp, mmatrix, comm, cid, s, mat_size):
+    ncom = np.array([x for x in range(mmatrix.shape[0]) if x not in samp])
+    vec = louvain_consensus.query_vector(np.array(samp), mmatrix)
+
+    def inc(x):
+        if x in comm:
+            return 1
+        return 0
+
+    y_true = np.array([inc(x) for x in ncom])
+    y_prob = vec[ncom]
+    auc = fast_auc(y_true, y_prob)
+    return cid, s, mat_size, auc
+
+
 def gen_roc_curves(mmatrix, comm, s, cid):
     funcs = (delayed(samp_roc_and_auc)(samp, mmatrix, comm, cid, s) for samp in unique_sampler(comm, s))
     results = Parallel(n_jobs=cpu_count(), backend='threading')(funcs)
@@ -144,6 +153,33 @@ def get_rocs(mmatrix, nmap, comms, seed_sizes=(1, 3, 7, 15)):
         for s in seed_sizes:
             if len(comm) > s:
                 res += gen_roc_curves(mmatrix, cnodes, s, cid)
+    return res
+
+
+def gen_auc(mmatrix, comm, s, cid):
+
+    samples = unique_sampler(comm, s)
+    funcs = []
+    for mat_size in np.linspace(10, 2000, 10):
+        # Get a sub matrix of specified size
+        sub_mat = mmatrix.transpose()[:mat_size].transpose()
+
+        for samp in samples:
+            funcs.append(delayed(samp_auc)(samp, sub_mat, comm, cid, s, mat_size))
+
+    results = Parallel(n_jobs=cpu_count(), backend='threading')(funcs)
+    return list(results)
+
+
[…]

### 2018-05-02 experiments/real_networks.py
impact os sample_space

@@ -162,7 +162,7 @@ def gen_auc(mmatrix, comm, s, cid):
     funcs = []
     for mat_size in np.linspace(10, 2000, 10):
         # Get a sub matrix of specified size
-        sub_mat = mmatrix.transpose()[:mat_size].transpose()
+        sub_mat = mmatrix.transpose()[:int(mat_size)].transpose()
 
         for samp in samples:
             funcs.append(delayed(samp_auc)(samp, sub_mat, comm, cid, s, mat_size))

### 2018-05-02 experiments/real_networks.py
impact os sample_space

@@ -156,31 +156,21 @@ def get_rocs(mmatrix, nmap, comms, seed_sizes=(1, 3, 7, 15)):
     return res
 
 
-def gen_auc(mmatrix, comm, s, cid):
-
-    samples = unique_sampler(comm, s)
+def psize_scoring(mmatrix, nmap, comms, seed_sizes=(1, 3, 7, 15)):
     funcs = []
     for mat_size in np.linspace(10, 2000, 10):
-        # Get a sub matrix of specified size
         sub_mat = mmatrix.transpose()[:int(mat_size)].transpose()
+        for cid, comm in comms.items():
+            cnodes = map_com(comm, nmap)
+            for s in seed_sizes:
+                samples = unique_sampler(cnodes, s)
+                if len(comm) > s:
+                    for samp in samples:
+                        funcs.append(delayed(samp_auc)(samp, sub_mat, cnodes, cid, s, mat_size))
 
-        for samp in samples:
-            funcs.append(delayed(samp_auc)(samp, sub_mat, comm, cid, s, mat_size))
+    results = Parallel(n_jobs=cpu_count(), verbose=5)(funcs)
 
-    results = Parallel(n_jobs=cpu_count(), backend='threading')(funcs)
-    return list(results)
-
-
-def psize_scoring(mmatrix, nmap, comms, seed_sizes=(1, 3, 7, 15)):
-    res = []
-
-    for cid, comm in progressbar.progressbar(comms.items()):
-        cnodes = map_com(comm, nmap)
-
-        for s in seed_sizes:
-            if len(comm) > s:
-                res += gen_auc(mmatrix, cnodes, s, cid)
-    return res
+    return results
 
 
 def plot_roc_curve(df, save_path):

### 2018-05-02 experiments/real_networks.py
impact os sample_space

@@ -173,7 +173,7 @@ def psize_scoring(mmatrix, nmap, comms, seed_sizes=(1, 3, 7, 15)):
     return results
 
 
-def plot_roc_curve(df, save_path):
+def plot_roc_curve(df):
     """
     Takes a dataframe of roc curves at different seeds and plots the mean roc curves
 
@@ -231,7 +231,7 @@ def plot_roc_curve(df, save_path):
         ax.legend()
 
     fig.tight_layout()
-    fig.savefig(save_path)
+    return fig
 
 
 def generate_results(network, overwrite=False):
@@ -264,9 +264,35 @@ def generate_results(network, overwrite=False):
            pickle.dump(psize_scores, auc_res_df)
 
 
-def handle_results(network):
+def plot_ensemble_size_impact(df):
+    fig, ax = plt.subplots()
+    fig.set_dpi(90)
 
-    dt = real_networks[network]
+    colours = {
+        1: "b",
+        3: "g",
+        7: "y",
+        15: "m"
+    }
+
+    xvals = sorted(df["mat_size"].unique())
+
+    for seed_size in df["seed"].unique():
+        scores = []
+        stds = []
+        for msize in xvals:
+            sdf = df.loc[df["mat_size"] == msize and df["seed"] == seed_size]
+
+            scores.append(sdf.mean()["auc"])
+            stds.append(sdf.std()["auc"])
+
+        ax.scatter(xvals, scores)
+        ax.yerror(xvals, scores, yerror=stds)
+    fig.tight_layout()
+    return fig
+
+
+def handle_results(network):
 
     roc_df_path = os.path.join("results", network) + "_roc_res.p"
     with open(roc_df_path, "rb") as rf:
@@ -275,14 +301,28 @@ def handle_results(network):
     headings = ["cid", "seed", "tpr", "fnr", "auc"]
 
     df = pd.DataFrame(results, columns=headings)
-    plot_roc_curve(df, "article/images/rocs/{}.png".format(network))
-    plot_roc_curve(df, "article/images/rocs/{}.svg".format(network))
-    plot_roc_curve(df, "article/images/rocs/{}.eps".format(network))
+    fig = plot_roc_curve(df)
+    fig.savefig("article/images/rocs/{}.png".format(network))
+    fig.savefig("article/images/rocs/{}.svg".format(network))
+    fig.savefig("article/images/rocs/{}.eps".format(network))
+
[…]

### 2018-05-02 experiments/real_networks.py
impact os sample_space

@@ -158,7 +158,7 @@ def get_rocs(mmatrix, nmap, comms, seed_sizes=(1, 3, 7, 15)):
 
 def psize_scoring(mmatrix, nmap, comms, seed_sizes=(1, 3, 7, 15)):
     funcs = []
-    for mat_size in np.linspace(10, 2000, 10):
+    for mat_size in np.linspace(1, 2000, 100, dtype=int):
         sub_mat = mmatrix.transpose()[:int(mat_size)].transpose()
         for cid, comm in comms.items():
             cnodes = map_com(comm, nmap)
@@ -255,7 +255,7 @@ def generate_results(network, overwrite=False):
         with open(sign_df_path, "wb+") as sig_df:
            pickle.dump(sigscores, sig_df)
 
-    roc_res_partitions = os.path.join("results", network) + "auc_res_partitions.p"
+    roc_res_partitions = os.path.join("results", network) + "auc_res_partitions2.p"
     if overwrite or not os.path.exists(roc_res_partitions):
         graph, comms, mmatrix, nmap = load_network(dt["path"], network, dt["clusters"], dt["index"], dt["node_type"])
         psize_scores = psize_scoring(mmatrix, nmap, comms)
@@ -277,17 +277,23 @@ def plot_ensemble_size_impact(df):
 
     xvals = sorted(df["mat_size"].unique())
 
+    ax.set_xlabel("Number of partition samples")
+    ax.set_ylabel("Mean AUC score")
+
+    ax.set_xlim([1, max(xvals) + 10])
+
     for seed_size in df["seed"].unique():
         scores = []
         stds = []
+        sdf = df.loc[df["seed"] == seed_size]
         for msize in xvals:
-            sdf = df.loc[df["mat_size"] == msize and df["seed"] == seed_size]
+            sdf2 = sdf.loc[sdf["mat_size"] == msize]
+            scores.append(sdf2.mean()["auc"])
+            stds.append(sdf2.std()["auc"])
 
-            scores.append(sdf.mean()["auc"])
-            stds.append(sdf.std()["auc"])
-
-        ax.scatter(xvals, scores)
-        ax.yerror(xvals, scores, yerror=stds)
+        ax.plot(xvals, scores, label="{} seed node(s)".format(seed_size), color=colours[seed_size])
+        #ax.errorbar(xvals, scores, yerr=stds)
+    ax.legend()
     fig.tight_layout()
     return fig
 
@@ -306,7 +312,7 @@ def handle_results(network):
[…]

### 2018-05-03 article/article.tex
impact os sample_space

@@
 However, in this paper we argue that this is not a flaw with the modularity maximisation algorithm but, rather, information that can be used to aid the context specific classification of functional relationships between vertices.
-Formally, we present an approach to generating a high value modularity consensus space for a network, based on the space of locally optimal modular partitions.
+Formally, we present an approach to generating a high value modularity consensus space for a network, based on the ensemble space of locally optimal modular partitions.
 This is then used as an approach to uncover latent relationships between sets initial query sets.
@@
 The work of Good \textit{et al.} \cite{good2010performance} recently highlighted that the popular modularity maximisation algorithm has a highly ``glassy'' search space.
-In this situation there are many locally optimal partitions that bear little to no resemblance to each other by measure of mutual information.
+In essence, for real, heterogeneous networks there are many locally optimal partitions that bear little to no resemblance to each other by measure of mutual information.
 This allows greedy optimisation algorithms \cite{blondel2008fast} to trivially find solutions that score extremely high values of modularity.
@@
 Perhaps the most popular of these methods is that of modularity maximisation \cite{newman2004}, which seeks to find the most unexpected partition of a graph with respect to a given null model.
-One limitation of partition based methods is that each vertex can only belong to a community.
-Overlapping methods have recently been applied to this problem in both \textit{crisp} \cite{ahn2010link, lancichinetti2011finding} and \textit{fuzzy} \cite{gregory2011fuzzy} based algorithms.
+One limitation of partition based methods is that each vertex can only belong to a single community.
+Overlapping methods have recently been applied to this problem in both \textit{crisp} \cite{ahn2010link, lancichinetti2011finding} and \textit{fuzzy} \cite{gregory2011fuzzy} based algorithms which have been widely used to uncover latent relationships without labelling schemes.
 
-In this paper, we do not seek to find a single ``best'' partition, either overlapping or not.
+However, in this paper, we do not seek to find a single ``best'' partition, either overlapping or not and our objective is not to uncover labels but to use limited and small sets of labels to give the notion of a membership score to some grouping.
 Instead, we use the large number of highly modular solutions to form the index for a search query system.
@@
 The querying method is a polynomial time algorithm that could be trivially adapted to form the basis of many user facing applications.
-This approach is applied to social and protein-protein interaction networks with good quality ground truth labels.
+This approach is then applied to synthetic benchmark networks with known, ground-truth labels as well as social and protein-protein interaction networks with high quality ground truth label sets.
 
@@
 
-\begin{figure}[t]
+\begin{figure*}[t]
     \centering
@@
     \end{subfigure}
-
     \begin{subfigure}[b]{0.48\textwidth}
@@
      \label{fig:auc_no_overlap}
-\end{figure}
+\end{figure*}
 
@@
      \label{fig:auc_overlap}
-\end{figure}
+\end{figure*}
 
@@
 \label{sec:real_networks}
-
 \begin{figure*}[t]
@@
 \begin{itemize}
- \item \textbf{EU emails dataset (EU emails)} This anonymised dataset is taken from the SNAP database \cite{snap} and contains $986$ nodes and $16,687$ edges representing emails between individuals.
+ \item \textbf{EU emails core dataset (EU emails) \cite{leskovec2007graph}} This anonymised dataset is taken from the SNAP database \cite{snapnets} and contains $986$ nodes and $16,687$ edges representing emails between individuals.
  The metadata community labels represent different departments within the organisation.
@@
 
+  \item \textbf{\textit{Escherichia coli} protein-protein interaction network (E.coli PPI) \cite{su2007bacteriome}}
+  For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{su2007bacteriome}.
+
  \item \textbf{\textit{Arabidopsis thaliana} protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}
   For the Arabidopsis dataset, the complex sources were more limited.
-  Consequently, the IntAct database was used with all protein complexes listed containing less than 10 proteins in total \cite{}.
-
-  \item \textbf{\textit{Escherichia coli} protein-protein interaction network (E.coli PPI) \cite{}}
-  For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{}.
+  Consequently, the IntAct database was used with all protein complexes listed containing less than 10 proteins in total \cite{orchard2013mintact}.
 \end{itemize}
 
-The results with varying number of seed nodes, for the cross validation procedure described in Section \ref{sec:cross_validation} are shown in Figure \ref{fig:quality_label_rocs}.
+%The networks and resulting area under the curve (AUC) of ROC statistics are shown in Table \ref{table:dataset_table}.
+ROC curves generated with the cross validation procedure described in Section \ref{sec:cross_validation} are shown in Figure \ref{fig:quality_label_rocs}.
 These results represent ROC curves and mean AUC statistics.
@@
 However, in the other networks studied using 3 or more seed nodes appears to improve results, though for 15 seed nodes the results are not significantly better than with 7 seeds.
+
+% \begin{table*}[t]
+% \begin{center}
+% \begin{tabular}{ c c c }
+%  cell1 & cell2 & cell3 \\ 
+%  cell4 & cell5 & cell6 \\  
+%  cell7 & cell8 & cell9    
+% \end{tabular}
+% \end{center}
+%  \label{table:dataset_table}
+%  \caption{Description of datasets used in this study and results of cross validation.}
+% \end{table*}
 
@@
     \end{subfigure}
-    \caption{ROC scores for the high quality labels for real networks described in Section \ref{sec:real_networks}. 
+    \caption{Receiver operator characteristic (ROC) curves for the high quality labels for real networks described in Section \ref{sec:real_networks}. 
     Results represent the averages over all reciever operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.
@@
 \end{figure*}
-.
+
+The method also serves as a useful network reduction tool for more limited labels.
+This is demonstrated for the \textit{Arabidopsis PPI} dataset shown in \ref{fig:query_example} with a hand selected gene ontology term from AmiGO \cite{carbon2008amigo}.
 

### 2018-05-03 cluster_query_tool/louvain_consensus.py

@@ -187,7 +187,8 @@ def query_vector(query_indexes, M):
     for v in np.ndindex(M.shape[0]):
         for q in query_indexes:
             # Number of times node is in the same cluster as a query node
-            qm[v] += (M[v] == M[q]).sum()
+            if q != v:
+                qm[v] += (M[v] == M[q]).sum()
 
     return qm * norm_const
 

### 2018-05-03 experiments/real_networks.py

@@ -291,8 +291,8 @@ def plot_ensemble_size_impact(df):
             scores.append(sdf2.mean()["auc"])
             stds.append(sdf2.std()["auc"])
 
-        ax.plot(xvals, scores, label="{} seed node(s)".format(seed_size), color=colours[seed_size])
-        #ax.errorbar(xvals, scores, yerr=stds)
+        ax.scatter(xvals, scores, label="{} seed node(s)".format(seed_size), color=colours[seed_size])
+        ax.errorbar(xvals, scores, yerr=stds, color=colours[seed_size])
     ax.legend()
     fig.tight_layout()
     return fig

### 2018-05-03 article/article.tex
go_arabidopsis

@@
   For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{su2007bacteriome}.
+  The network contains 1913 nodes and 7252 edges, the protein complexes range in size between 3 and 65 nodes.
+  85\% of the complexes contain 10 or less nodes.
 
- \item \textbf{\textit{Arabidopsis thaliana} protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}
+ \item \textbf{\textit{Arabidopsis thaliana} protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}.
+  The network itself contains 4519 nodes and 11096 edges.
   For the Arabidopsis dataset, the complex sources were more limited.
-  Consequently, the IntAct database was used with all protein complexes listed containing less than 10 proteins in total \cite{orchard2013mintact}.
+  Consequently, we obtained all gene ontology annotations under the GO term \textit{``Protein-containing complex''} from AmiGO \cite{carbon2009amigo} with the label ``physical interaction evidence used in manual assertion''.
+  At the time of writing, this resulted in <INSERT> complexes within the network.
+
 \end{itemize}

### 2018-05-03 cluster_query_tool/louvain_consensus.py

@@ -247,3 +247,25 @@ def mui_vec_largest_intersec(query_indexes, membership_mat):
     mu_vec *= 1 / membership_mat.shape[1]
     return mu_vec
 
+
+@jit(nopython=True)
+def _unique(arr):
+    it = np.array([1])
+    for x in arr:
+        if x not in it:
+            it.append([x])
+    return it
+
+
+@jit(nopython=True, nogil=True)
+def uniform_membership_probability(mmatrix, q_size):
+    n = mmatrix.shape[0]
+    prob = 0.0
+
+    for i in mmatrix.transpose():
+        for c in _unique(i):
+            ps = ((i == c).sum() / n)
+            for x in range(2, q_size + 1):
+                prob += ps ** x
+
+    return prob * 1/mmatrix.shape[1]

### 2018-05-03 experiments/real_networks.py

@@ -24,6 +24,14 @@ real_networks = {
         "node_type": "str",
     },
 
+    "arabidopsis_ppi_go_comp": {
+        "path": "data/arabidopsis_ppi/arabidopsis_ppi.edgelist",
+        "clusters": "data/arabidopsis_ppi/go_complexes.json",
+        "index": "data/arabidopsis_ppi/index.json.xz",
+        "node_type": "str",
+    },
+
+
     "ecoli_ppi": {
         "path": "data/ecoli_ppi/ecoli_ppi.edgelist",
         "clusters": "data/ecoli_ppi/ecoli_ppi.json",
@@ -255,14 +263,6 @@ def generate_results(network, overwrite=False):
         with open(sign_df_path, "wb+") as sig_df:
            pickle.dump(sigscores, sig_df)
 
-    roc_res_partitions = os.path.join("results", network) + "auc_res_partitions2.p"
-    if overwrite or not os.path.exists(roc_res_partitions):
-        graph, comms, mmatrix, nmap = load_network(dt["path"], network, dt["clusters"], dt["index"], dt["node_type"])
-        psize_scores = psize_scoring(mmatrix, nmap, comms)
-
-        with open(roc_res_partitions, "wb+") as auc_res_df:
-           pickle.dump(psize_scores, auc_res_df)
-
 
 def plot_ensemble_size_impact(df):
     fig, ax = plt.subplots()
@@ -311,18 +311,6 @@ def handle_results(network):
     fig.savefig("article/images/rocs/{}.png".format(network))
     fig.savefig("article/images/rocs/{}.svg".format(network))
     fig.savefig("article/images/rocs/{}.eps".format(network))
-
-    roc_res_partitions = os.path.join("results", network) + "auc_res_partitions2.p"
-    with open(roc_res_partitions, "rb") as rf:
-        results = pickle.load(rf)
-
-    df = pd.DataFrame(results, columns=["cid", "seed", "mat_size", "auc"])
-
-    fig = plot_ensemble_size_impact(df)
-
-    fig.savefig("article/images/{}_psize_auc.png".format(network))
-    fig.savefig("article/images/{}_psize_auc.eps".format(network))
-    fig.savefig("article/images/{}_psize_auc.svg".format(network))
 
     return df
 

### 2018-05-03 experiments/real_networks.py
go_arabidopsis

@@ -24,7 +24,7 @@ real_networks = {
         "node_type": "str",
     },
 
-    "arabidopsis_ppi_go_comp": {
+    "arabidopsis_ppi_go_comp2": {
         "path": "data/arabidopsis_ppi/arabidopsis_ppi.edgelist",
         "clusters": "data/arabidopsis_ppi/go_complexes.json",
         "index": "data/arabidopsis_ppi/index.json.xz",
@@ -77,11 +77,14 @@ def load_network(graph_path, graph_name, communities_path, index_path, node_type
     index = get_index(graph, cache_location=index_path)
     mmatrix, nmap = louvain_consensus.membership_matrix(list(graph.nodes()), index)
 
+    # make sure clusters are unique, have more than 2 nodes and all nodes are contained in the graph
     rcomms = dict()
+    rcomm_l = []
     for c in comms:
-        nc = [x for x in comms[c] if x in nmap]
-        if len(nc) > 2:
+        nc = tuple(sorted(set([x for x in comms[c] if x in nmap])))
+        if len(nc) > 2 and nc not in rcomm_l:
             rcomms[c] = nc
+            rcomm_l.append(nc)
 
     return graph, rcomms, mmatrix, nmap
 

### 2018-05-04 article/article.tex
Added amigo terms for analysis

@@
 Uncovering latent community structure in complex networks is a field that has received an enormous amount of attention.
-Unfortunately, whilst potentially very powerful unsupervised methods for uncovering labels based on topology alone has been shown to have several difficulties.
-For example, the search space for module extraction approaches appears to be extremely glassy, with many high valued solutions that lack any real similarity to one another.
+Unfortunately, whilst potentially very powerful, unsupervised methods for uncovering labels based on topology alone has been shown to have several difficulties.
+For example, the search space for many module extraction approaches, such as the modularity maximisation algorithm, appears to be extremely glassy, with many high valued solutions that lack any real similarity to one another.
 However, in this paper we argue that this is not a flaw with the modularity maximisation algorithm but, rather, information that can be used to aid the context specific classification of functional relationships between vertices.
 Formally, we present an approach to generating a high value modularity consensus space for a network, based on the ensemble space of locally optimal modular partitions.
-This is then used as an approach to uncover latent relationships between sets initial query sets.
-The methods developed in this paper are applied to biological and social datasets with ground-truth label data, with a small number of examples used as seed sets to uncover relationships.
-When tested on both real and synthetic datasets our method achieves extremely high levels of classification accuracy in a context specific manner.
-Furthermore, the approach can be applied in distributed environments potentially allowing it to scale to very large networks.
+We then use this approach to uncover latent relationships between sets initial query sets.
+The methods developed in this paper are applied to biological and social datasets with ground-truth label data, using a small number of examples used as seed sets to uncover relationships.
+When tested on both real and synthetic datasets our method achieves high levels of classification accuracy in a context specific manner.
 \end{abstract}
@@
 A fundamental issue at the heart of machine learning methods applied to large scale datasets is the ability to correctly identify classes of related objects in an unsupervised manner.
-In network science, this methodology is often referred to as \textit{community} detection, due to the intuitive analogy to the notion of social groupings \cite{fortunato2010community}.
+In network science, this methodology is often referred to as \textit{community} detection \cite{fortunato2010community}.
 Many algorithms exist to solve this problem \cite{fortunato2016community}, yet initial starting conditions or different optimisation strategies may result in conflicting results even when the same objective function is being maximised \cite{good2010performance}.
 In this paper, we develop an intuitive method to use the uncertainty amongst a high number of near optimal solutions to measure context sensitive relationships between small sets of labelled vertices.
-This approach can be based on labels that are not first neighbours in order to find other potentially related vertices.
+This approach can be based on labels that are not first order neighbours in order to find other potentially related vertices.
 
@@
 The work of Good \textit{et al.} \cite{good2010performance} recently highlighted that the popular modularity maximisation algorithm has a highly ``glassy'' search space.
-In essence, for real, heterogeneous networks there are many locally optimal partitions that bear little to no resemblance to each other by measure of mutual information.
+In essence, for real, heterogeneous networks there are many locally optimal partitions that bear little resemblance to each other by measure of mutual information.
 This allows greedy optimisation algorithms \cite{blondel2008fast} to trivially find solutions that score extremely high values of modularity.
@@
 The use of community detection is widespread.
-For example, core goal in systems biology is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network \cite{girvan2002community}.
+For example, a core goal in systems biology is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network \cite{girvan2002community}.
 In many situations, only the role of a small number of genes is known, with much of the annotation for a given organism being computed through naive homology information that ignores the role of a gene within a wider context.
@@
 In essence, this is a method of semi-supervised learning that attempts to find items related given labelled sets of vertices using topology alone.
-Each high value partition, if statistically more modular than random, can be treated as information about the relationships between vertices.
+Each high value partition can be treated as information about the relationships between vertices.
+That is to say, there is not a single, correct view of the underlying community structure to a network, but rather, many different context dependent definitions.
 As the objective of community detection approaches is to relate information, it is assumed that some labelled meta-data can be used to find unlabelled, potentially related vertices.
 
+More formally, the problem tackled in this paper can be formulated as follows:
+Given a graph made up of vertices and edges $G = (V, E)$, and a query set $S \subset V$, we formally ask the question; \textit{How well is a given vertex, $i \notin S$ related to $S$?}
+
 We propose an algorithm that pre-computes an index of clusterings for a given complex network, based on the fast greedy Louvain algorithm \cite{blondel2008fast}, used in a distributed manner.
-The detected clusters then form the basis of a searching algorithm that allows one to compute the relatedness of subsets of nodes.
+The detected clusters then form the basis of a search algorithm that allows one to compute the relatedness of subsets of nodes.
 The querying method is a polynomial time algorithm that could be trivially adapted to form the basis of many user facing applications.
 This approach is then applied to synthetic benchmark networks with known, ground-truth labels as well as social and protein-protein interaction networks with high quality ground truth label sets.
-
-\section{The multi-vertex classification problem}
-The intuitive notion that the structure of a vertex's connections gives insight into its function is a fundamental basis for research in network science.
-In many cases, the role of given node is uncharacterised and we would seek to discover latent relationships through methods such as community detection.
-The basic premise of community detection is that detecting dense topological sub-graphs allows one to uncover the function of vertices \cite{fortunato2010community}.
-
-In this paper, we consider the notion of relatedness to require additional meta-data, or vertex labels, that can be attributed to specific ontological definitions.
-In many situations this information will be sparse or incomplete.
-For example, in biological networks only a very small number of organisms have a high level of coverage in terms of functional annotation \cite{bassel2012systems}.
-
-The problem tackled in this paper can be formulated as follows:
-Given a graph made up of vertices and edges $G = (V, E)$, and a query set $S \subset V$, we formally ask the question; \textit{How related is a given vertex to $S$?}
-This question assumes that a given query set is formally related.
-In practice, this is likely not the case for most subsets of $V$.
-Consequently we also use our approach to ask another question; \textit{How well related is $S$?}
-In order to answer these questions we focus on the set of high valued partitions of a given network detectable with the well known modularity maximisation algorithm.
 
@@
 \section{Exploiting the modularity query space}
-To characterise latent community structure, one of the most popular approaches is to use modularity maximisation.
-The modularity quality function of a partition on a graph is given by the following equation \cite{newman2004}
+To characterise latent community structure, one of the most popular approaches is to use modularity maximisation \cite{newman2004}.
+The modularity quality function of a partition on a graph is given by the equation
 \begin{equation}\label{eq:modularity}
@@
 In principle, any search exploration procedure, such as simulated annealing \cite{GuimeraNature2005} could be used.
-The Louvain algorithm is selected as it is fast, running in $O(n \log n)$ time complexity \cite{blondel2008fast}, and because it is a greedy algorithm is is guaranteed to stop after finding a locally maximal solution.
+The Louvain algorithm is selected as it is fast, running in $O(n \log n)$ time complexity \cite{blondel2008fast}, and because it is a greedy algorithm and is guaranteed to stop after finding a locally maximal solution.
 
 The Louvain algorithm is conceptually very simple; starting from a random partition, clusters are agglomerated if the merge results in a positive change in modularity $\Delta Q$.
-When no possible moves result in an increase in modularity the algorithm has found a local optima and stops.
+When no possible moves result in an increase in modularity the algorithm has found a local optima.
 
@@
 Given that there is no free lunch and it is impossible to know every solution, one can only ensure a full coverage index through an exhaustive search over the $2^m$ possible starting cut sets.
-Consequently, in the approach taken here is to use a large but not exhaustive subset of the possible solutions using 2000 solutions for the networks studied in this paper.
+Consequently, the approach taken here is to use a large but not exhaustive subset of the possible solutions using a suitably large space 2000 solutions for the networks studied in this paper.
+\footnote{Initial results indicated that a smaller space of partitions is possible but further work is required to asses the best number of partitions in a practical context}.
 
@@
 
-% \subsection{Statistically significant query sets}
-% \label{sec:query_sign}
-% Naturally, not every label set will be of high quality or represented within the community structure of a network.
-% This is established further in section \ref{sec:go_labels} which tests gene ontology terms (GO) on protein interaction networks.
-% In this case, all the labels relate to the real function of the vertices, however, GO is a hierarchical system and many terms are extremely general.
-% Furthermore, even for specific terms the network datasets will often not be well represented.
-% A common approach with community detection and clustering (used for example in \cite{dekkers2013}) is to detect communities and find clusters containing significant GO terms.
-% 
-% In this work, we would wish to use the community partition space, described above, to find highly related sets of vertices.
-% For this we take the distribution, from Equation \ref{eq:mu_score} for a given query set.
-% For a query set to be relevant it should be significantly more related than one would expect from a set of nodes selected at random within a network.
-% 
-% Formally, given the partition space $\mathcal{P}$ and a query set $S$ we consider the distribution of quality scores as $\mu_i(S - i)$, for all $i$ in $S$.
-% In order for $S$ to be a high quality query set, its value of internal vertices should be significantly higher than for external vertices.
-% Formally, we assert that the distribution $\mu_i(S - i)$ should reject the null hypothesis that the mean is not significantly greater than $\mu_j(S)$ where $j \in S - V$, the set of vertices excluding those in the query set.
-% For the purposes of this work we use the non-parametric Mann–Whitney $U$ test and reject the null hypothesis where $p < 0.001$.
-% In section \ref{sec:go_labels} this is used to exclude less relevant GO terms.
-
 \section{Results}
@@
 \label{sec:cross_validation}
-In this work we are presented with a problem of a small number of labels for true positive cluster information.
+In this study we test a small number of labels that we intend to use in order to evaluate how well our method correctly generalises to discover unlabelled vertices.
 The cross validation procedure we devise is described as follows and depends on the size of the community and the number of initial seed labels being used.
-For this work we would like to capture binary classification  performance, \textit{true positives (tp), true negatives (tn), false positives (fp)} and \textit{false negatives (fn)}, on our datasets.
+For this work we would like to capture binary classification  performance, \textit{true positives (tp), true negatives (tn), false positives (fp)} and \textit{false negatives (fn)}, on our datasets of community membership.
 As the seed label sets can be as small as 3 vertices, exhaustive cross validation is not possible for all labelling schemes.
-Consequently, cross validation is either conducted on an exhaustive set of all possible $\binom{|L|}{s}$ unique labellings or 120 seed queries sampled without replacement, where $L$ is the set of gold standard true labels and $s$ is the size of the randomly selected seed sets.
+Consequently, cross validation is either conducted on an exhaustive set of all possible $\binom{|L|}{s}$ unique labellings or 120 seed queries sampled without replacement\footnote{This is equivalent to $\binom{10}{3}$ combinations, an exhaustive sample would not be possible for the larger communities in this study.}, where $L$ is the set of gold standard true labels and $s$ is the size of the randomly selected seed sets.
 It should therefore be noted that presented receiver operator characteristic (ROC) scores are, therefore, dependent on community sizes.
@@
 \subsection{Synthetic networks}
-In this section we test the method on benchmark networks constructed with a known, ground-truth community structure.
+In this section we test the method on benchmark networks constructed with a ground-truth community structure.
 To evaluate how our method performs we use the undirected, unweighted LFR benchmark \cite{lancichinetti2008benchmark} in overlapping and non-overlapping forms.
 We test the area under the ROC curve (AUC) scores for networks synthetically generated with the LFR benchmark.
-In these tests, the community distribution is defined with a powerlaw coefficient of $-1.0$, the degree distribution is defined with a powerlaw coefficient of $-2.0$ and the number of nodes is stated.
+In these tests, the community distribution is defined with a power law coefficient of $-1.0$, the degree distribution is defined with a power law coefficient of $-2.0$.
+The number of nodes is stated in the text.
 
@@
      Data points represent mean auc scores for all communities on 100 sampled networks at varying mixing coefficients.
-     Error bars represent standard deviations.}
+     Error bars represent one standard deviation..}
      \label{fig:auc_no_overlap}
@@
      Data points represent mean auc scores for all communities on 100 sampled networks at varying overlapping fraction of nodes.
-     Error bars represent standard deviations.}
+     Error bars represent one standard deviation..}
      \label{fig:auc_overlap}
@@
 \label{sec:real_networks}
-\begin{figure*}[t]
-\includegraphics[width=\textwidth]{images/ppi_example_combined.eps}
-\caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
-(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
-(B) Shows a reduced view of the network where a threshold of $\mu_i(S) > 0.8$ is selected, reducing the network to 404 nodes.
-Blue nodes indicate those in the randomly selected 3 query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
-(C) Shows an example ROC curve from the cross validation described in the main text. 
-Based on 3 randomly selected query nodes containing this GO term.
-}
-\label{fig:query_example}
-\end{figure*}
-
-In order to test the performance of the semi-supervised classification on real-world data we present our findings on example networks with known metadata communities.
-All datasets taken use the largest single connected component sub-graph.
-The real networks used are listed as follows:
-\begin{itemize}
- \item \textbf{EU emails core dataset (EU emails) \cite{leskovec2007graph}} This anonymised dataset is taken from the SNAP database \cite{snapnets} and contains $986$ nodes and $16,687$ edges representing emails between individuals.
- The metadata community labels represent different departments within the organisation.
- In total there are 42 communities, 39 of which contain at least 3 nodes.
-
- \item \textbf{Yeast protein-protein interaction network (Yeast PPI)} \cite{yu2008high}
- This dataset is a collection of recorded binary interactions between proteins collected with high-throughput yeast-2-hybrid assays.
- The metadata used are known, experimentally validated protein complexes from \cite{pu2008up}.
- The network contains 6222 nodes in the largest connected component, with 22,3868 edges.
- There are 409 experimentally validated protein complexes, 236 of which contain 3 or more nodes.
- The protein complexes are typically very small in terms of number of proteins with  90\% of the complexes containing less than 10 proteins and only 2 complexes containing 50 or more proteins.
-
-  \item \textbf{\textit{Escherichia coli} protein-protein interaction network (E.coli PPI) \cite{su2007bacteriome}}
-  For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{su2007bacteriome}.
-  The network contains 1913 nodes and 7252 edges, the protein complexes range in size between 3 and 65 nodes.
-  85\% of the complexes contain 10 or less nodes.
-
- \item \textbf{\textit{Arabidopsis thaliana} protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}.
-  The network itself contains 4519 nodes and 11096 edges.
-  For the Arabidopsis dataset, the complex sources were more limited.
-  Consequently, we obtained all gene ontology annotations under the GO term \textit{``Protein-containing complex''} from AmiGO \cite{carbon2009amigo} with the label ``physical interaction evidence used in manual assertion''.
-  At the time of writing, this resulted in <INSERT> complexes within the network.
-
-\end{itemize}
-
-%The networks and resulting area under the curve (AUC) of ROC statistics are shown in Table \ref{table:dataset_table}.
-ROC curves generated with the cross validation procedure described in Section \ref{sec:cross_validation} are shown in Figure \ref{fig:quality_label_rocs}.
-These results represent ROC curves and mean AUC statistics.
-For all the datasets in this study binary community classification is high, with an average AUC score above 0.88, even when using only a single seed node.
-In the case of the \textit{Arabidopsis thaliana} network the protein complexes tested are significantly smaller than for other networks and so a comparison of seed sizes is not possible.
-However, in the other networks studied using 3 or more seed nodes appears to improve results, though for 15 seed nodes the results are not significantly better than with 7 seeds.
-
-% \begin{table*}[t]
-% \begin{center}
-% \begin{tabular}{ c c c }
-%  cell1 & cell2 & cell3 \\ 
-%  cell4 & cell5 & cell6 \\  
-%  cell7 & cell8 & cell9    
-% \end{tabular}
-% \end{center}
-%  \label{table:dataset_table}
-%  \caption{Description of datasets used in this study and results of cross validation.}
-% \end{table*}
 
@@
         \centering
-        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi.png}
+        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi_combined.png}
         \caption{Arabidopsis PPI protein complexes}
@@
     \caption{Receiver operator characteristic (ROC) curves for the high quality labels for real networks described in Section \ref{sec:real_networks}. 
-    Results represent the averages over all reciever operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.
-    Shaded areas indicate standard deviations.}
+    Results represent the averages over all receiver operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.
+    Shaded areas indicate one standard deviation.}
     \label{fig:quality_label_rocs}
@@
 
-The method also serves as a useful network reduction tool for more limited labels.
-This is demonstrated for the \textit{Arabidopsis PPI} dataset shown in \ref{fig:query_example} with a hand selected gene ontology term from AmiGO \cite{carbon2008amigo}.
+In order to test the performance of the semi-supervised classification on real-world data we present our findings on example networks with metadata communities.
+All datasets use the largest single connected component sub-graph.
+The real networks used are:
+\begin{itemize}
+ \item \textbf{EU emails core dataset (EU emails) \cite{leskovec2007graph}} This anonymised dataset is taken from the SNAP database \cite{snapnets} and contains $986$ nodes and $16,687$ edges representing emails between individuals.
+ The metadata community labels represent different departments within the organisation.
+ In total there are 42 communities, 39 of which contain at least 3 nodes.
+
+ \item \textbf{Yeast protein-protein interaction network (Yeast PPI)} \cite{yu2008high}
+ This dataset is a collection of recorded binary interactions between proteins collected with high-throughput yeast-2-hybrid assays.
+ The metadata used are known, experimentally validated protein complexes from \cite{pu2008up}.
+ The network contains 6222 nodes in the largest connected component, with 22,3868 edges.
+ There are 409 experimentally validated protein complexes, 236 of which contain 3 or more nodes.
+ The protein complexes are typically very small in terms of number of proteins, with  90\% of the complexes containing less than 10 proteins and only 2 complexes containing 50 or more proteins.
+
+  \item \textbf{\textit{Escherichia coli} protein-protein interaction network (E.coli PPI) \cite{su2007bacteriome}}
+  For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{su2007bacteriome}.
+  The network contains 1913 nodes and 7252 edges, the protein complexes range in size between 3 and 65 nodes.
+  85\% of the complexes contain 10 or less nodes.
+
+ \item \textbf{\textit{Arabidopsis thaliana} protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}.
+  The network itself contains 4519 nodes and 11096 edges.
+  For the Arabidopsis dataset, the complex sources were more limited.
+  Consequently, we obtained all gene ontology annotations under the GO term \textit{``Protein-containing complex''} from AmiGO \cite{carbon2009amigo} with the label ``physical interaction evidence used in manual assertion''.
+  At the time of writing, this resulted in 7 complexes containing between 4 and 12 nodes.
+  In addition, we included small protein complexes from the IntAct database \cite{orchard2013mintact}, resulting in a total of 165 unique complexes.
+  As the labels for this dataset are small it was not possible to test algorithm performance with 15 seed nodes.
+
+\end{itemize}
+
+%The networks and resulting area under the curve (AUC) of ROC statistics are shown in Table \ref{table:dataset_table}.
+ROC curves generated with the cross validation procedure described in Section \ref{sec:cross_validation} are shown in Figure \ref{fig:quality_label_rocs}.
+These results represent ROC curves and mean AUC statistics.
+For all the datasets in this study, binary community classification is high, with an average AUC scores above 0.83, even when using only a single seed node.
+In the case of the \textit{Arabidopsis thaliana} network the protein complexes tested are significantly smaller than for other networks and so a comparison of seed sizes is not possible.
+However, in the other networks studied, using 3 or more seed nodes appears to improve results, though for 15 seed nodes the results are not significantly better than with 7 seeds.
+
+The method also serves as a useful network reduction tool where the quality of labels is not as well defined.
+This visually is demonstrated for the \textit{Arabidopsis PPI} dataset shown in Figure \ref{fig:query_example} with a hand selected gene ontology term from AmiGO \cite{carbon2008amigo}.
+Figure \ref{fig:GO_TERM_ROCS}
+
+\begin{figure*}[t]
+\includegraphics[width=\textwidth]{images/ppi_example_combined.eps}
+\caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
+(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
+(B) Shows a reduced view of the network where a threshold of $\mu_i(S) > 0.8$ is selected, reducing the network to 404 nodes.
+Blue nodes indicate those in the randomly selected 3 query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
+(C) Shows an example ROC curve from the cross validation described in the main text.
+}
+\label{fig:query_example}
+\end{figure*}
+
+\begin{figure*}
+     \centering
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/rocs/yeast_ppi.png}
+        \caption{Yeast PPI GO terms}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi_combined.png}
+        \caption{Arabidopsis PPI GO terms}
+    \end{subfigure}
+    \begin{subfigure}[b]{0.3\textwidth}
+        \centering
+        \includegraphics[width=\textwidth]{images/rocs/ecoli_ppi.png}
+        \caption{E coli PPI GO terms}
+    \end{subfigure}
+    \caption{Receiver operator characteristic (ROC) curves for the high quality labels for real networks described in Section \ref{sec:real_networks}. 
+    Results represent the averages over all receiver operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.
+    Shaded areas indicate one standard deviation.}
+    \label{fig:GO_TERM_ROCS}
+\end{figure*}
 
@@
 However, we speculate that is likely due to the fact that the co-classification of vertices between different partitions remains fairly tolerant to changes.
-I.e. whilst the large communities they reside in changes significantly, the small cluster of nodes is always clustered in the same community, regardless of the partition.
+In other words, whilst the large communities they reside in changes significantly, the small cluster of nodes is always clustered in the same community, regardless of the partition.
 We do note that, where communities are very small, any approach will extremely sensitive to false positive and false negative results.
@@
 \label{sec:related_work}
-This work relates very strongly to the idea of local community detection, more specifically the idea of \textit{seed set expansion} \cite{gleich2012vertex}..
+This work relates very strongly to the idea of local community detection, more specifically the idea of \textit{seed set expansion} \cite{gleich2012vertex}.
 Here, a given seed set is created a random walks are analysed to find clearly related communities of vertices.
@@
 In contrast, the query approach presented here does not require the queries to be a self contained sub-graph.
-Indeed, queries can contain spurious nodes that are topologically distinct from one another - the result is that the either $q(S)$ score for the query will be very low and statistically insignificant, or the spurious nodes will be ignored in the final query set.
+Indeed, queries can contain spurious nodes that are topologically distinct from one another - the result is that the $\mu_i(S)$ score for the query set will likely be very low.
+Further investigation into how to evaluate the quality of high average $\mu_i(S)$ for $i \in S$ is left to future work.
 
@@
 The approach presented here differs from other ensemble approaches in that the objective is to provide a probabilistic framework for label classification.
-Performance is extremely strong on both synthetically generated networks and real-world ground truth communities with relatively small sets of labels.
+Performance was shown to be strong on both synthetically generated networks and real-world ground truth communities with relatively small sets of labels.
+In the case of synthetic networks communities are correctly detected up to the detectability threshold.
+For real world networks with small label sets, average AUC scores were above 0.88 for all the datasets tested in this study.
 
 However, this approach requires the community landscape to contain many local maxima, a property likely shared by many real-world, heterogeneous networks.
-Similarly, the method presented here requires both some labelled data and the labels to be represented well within the topology of the underlying network.
+Similarly, the method presented here requires both some labelled data and the labels to be relevant in the context of the underlying network.
 
@@
 \section*{Acknowledgements}
-We are grateful for access to the University of Nottingham High Performance Computing Facility for supporting this work.
+We are grateful for access to the University of Nottingham High Performance Computing Facility in support of this work.
 This work was supported by the Biotechnology and Biological Sciences Research Council grant BB/L013940/1.
-We would like to thank Nicole Pearcy for assistance with this manuscript.
+We would like to thank Nicole Pearcy and Jenna Reps for assistance with this manuscript.
 

### 2018-05-04 cluster_query_tool/louvain_consensus.py

@@ -187,8 +187,7 @@ def query_vector(query_indexes, M):
     for v in np.ndindex(M.shape[0]):
         for q in query_indexes:
             # Number of times node is in the same cluster as a query node
-            if q != v:
-                qm[v] += (M[v] == M[q]).sum()
+            qm[v] += (M[v] == M[q]).sum()
 
     return qm * norm_const
 

### 2018-05-04 experiments/real_networks.py

@@ -17,21 +17,20 @@ from scipy import interp
 
 
 real_networks = {
-    "arabidopsis_ppi": {
+
+    "arabidopsis_ppi_amigo": {
         "path": "data/arabidopsis_ppi/arabidopsis_ppi.edgelist",
-        "clusters": "data/arabidopsis_ppi/int_act_complexes.json",
+        "clusters": "data/arabidopsis_ppi/amigo_terms.json",
         "index": "data/arabidopsis_ppi/index.json.xz",
         "node_type": "str",
     },
 
-    "arabidopsis_ppi_go_comp2": {
+    "arabidopsis_ppi_combined": {
         "path": "data/arabidopsis_ppi/arabidopsis_ppi.edgelist",
-        "clusters": "data/arabidopsis_ppi/go_complexes.json",
+        "clusters": "data/arabidopsis_ppi/combine_complexes.json",
         "index": "data/arabidopsis_ppi/index.json.xz",
         "node_type": "str",
     },
-
-
     "ecoli_ppi": {
         "path": "data/ecoli_ppi/ecoli_ppi.edgelist",
         "clusters": "data/ecoli_ppi/ecoli_ppi.json",
@@ -39,9 +38,23 @@ real_networks = {
         "node_type": "str",
     },
 
+    "ecoli_ppi_amigo": {
+        "path": "data/ecoli_ppi/ecoli_ppi.edgelist",
+        "clusters": "data/ecoli_ppi/amigo_terms.json",
+        "index": "data/ecoli_ppi/index.json.xz",
+        "node_type": "str",
+    },
+
     "yeast_ppi": {
         "path": "data/yeast_ppi/yeast.edgelist",
         "clusters": "data/yeast_ppi/yeast_ppi.json",
+        "index": "data/yeast_ppi/index.json.xz",
+        "node_type": "str",
+    },
+
+    "yeast_ppi_amigo": {
+        "path": "data/yeast_ppi/yeast.edgelist",
+        "clusters": "data/yeast_ppi/amigo_terms.json",
         "index": "data/yeast_ppi/index.json.xz",
         "node_type": "str",
     },

### 2018-05-08 article/article.tex
Major changes to article to include GO test examples

@@
 %Conference
-\acmConference[]{}{}{}
+\acmConference[MLG 2018]{14th International Workshop on Mining and Learning with Graphs}{Aug 20, 2018}{United Kingdom}
 \acmYear{2018}
 \copyrightyear{2018}
+\acmPrice{}
 
@@
 
-\title{From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks}
+\title[From clusters to queries]{From clusters to queries: exploiting uncertainty in the modularity landscape of complex networks}
 
@@
 
-% \author{John King}
-% \affiliation{%
-%   \institution{School of Mathematical Sciences}
-%   \streetaddress{University of Nottingham}
-%   \city{Nottingham}
-%   \country{United Kingdom}
-%   \postcode{NG7 2RD}
-% }
-% \email{john.king@nottingham.ac.uk}
-
 \begin{abstract}
 Uncovering latent community structure in complex networks is a field that has received an enormous amount of attention.
-Unfortunately, whilst potentially very powerful, unsupervised methods for uncovering labels based on topology alone has been shown to have several difficulties.
+Unfortunately, whilst potentially very powerful, unsupervised methods for uncovering labels based on topology alone has been shown to suffer from several difficulties.
 For example, the search space for many module extraction approaches, such as the modularity maximisation algorithm, appears to be extremely glassy, with many high valued solutions that lack any real similarity to one another.
@@
 The methods developed in this paper are applied to biological and social datasets with ground-truth label data, using a small number of examples used as seed sets to uncover relationships.
-When tested on both real and synthetic datasets our method achieves high levels of classification accuracy in a context specific manner.
+When tested on both real and synthetic datasets our method is shown to achieve high levels of classification accuracy in a context specific manner.
 \end{abstract}
@@
 A fundamental issue at the heart of machine learning methods applied to large scale datasets is the ability to correctly identify classes of related objects in an unsupervised manner.
-In network science, this methodology is often referred to as \textit{community} detection \cite{fortunato2010community}.
+In network science, this methodology is often referred to as \textit{community} detection \cite{fortunato2016community}.
 Many algorithms exist to solve this problem \cite{fortunato2016community}, yet initial starting conditions or different optimisation strategies may result in conflicting results even when the same objective function is being maximised \cite{good2010performance}.
@@
 This approach can be based on labels that are not first order neighbours in order to find other potentially related vertices.
+
+The use of community detection is widespread.
+For example, a core goal in systems biology is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network \cite{girvan2002community}.
+In many situations, only the role of a small number of genes is known, with much of the annotation for a given organism being computed through naive homology information that ignores the role of a gene within a wider context.
+The advent of high throughput experimental datasets has allowed the construction of proteome scale networks, leading to the observation of non-trivial topological properties such as densely connected clusters \cite{ArabidopsisConsortium2011}.
+These densely connected clusters are widely believed to be associated with specific function, such as multi-protein complexes or biochemical pathways.
+
+As a form of unsupervised machine learning module extraction methods largely focus on optimising some objective function with the goal of finding meaningful clusterings.
+Perhaps the most popular of these methods is that of modularity maximisation \cite{newman2004}, which seeks to find the most unexpected partition of a graph with respect to a given null model.
+Overlapping methods have recently been applied to this problem in both \textit{crisp} \cite{ahn2010link, lancichinetti2011finding} and \textit{fuzzy} \cite{gregory2011fuzzy} based algorithms which have been widely used to uncover latent relationships without labelling schemes.
+In previous work, we found that most of these methods have significant disagreement when evaluated in a practical context \cite{gilbert2015probabilistic}.
 
@@
 In order to solve this issue, certain approaches use a consensus based approach to clustering, combining many high value partitions into a given median partition \cite{lancichinetti2012consensus}.
-
-The use of community detection is widespread.
-For example, a core goal in systems biology is to characterise the function and functional relationships between genes, proteins or metabolites within a larger network \cite{girvan2002community}.
-In many situations, only the role of a small number of genes is known, with much of the annotation for a given organism being computed through naive homology information that ignores the role of a gene within a wider context.
-The advent of high throughput experimental datasets has allowed the construction of genome scale networks, leading to the observation of non-trivial topological properties such as densely connected clusters \cite{ArabidopsisConsortium2011}.
-These densely connected clusters are widely believed to be associated with specific function, such as multi-protein complexes or biochemical pathways.
-
-This, and work in related fields, has led to the desire for computational techniques that elucidate related, modular structure in the form of community detection algorithms \cite{fortunato2010community}.
-As a form of unsupervised machine learning module extraction methods largely focus on optimising some objective function with the desire of finding meaningful clusterings.
-Perhaps the most popular of these methods is that of modularity maximisation \cite{newman2004}, which seeks to find the most unexpected partition of a graph with respect to a given null model.
-One limitation of partition based methods is that each vertex can only belong to a single community.
-Overlapping methods have recently been applied to this problem in both \textit{crisp} \cite{ahn2010link, lancichinetti2011finding} and \textit{fuzzy} \cite{gregory2011fuzzy} based algorithms which have been widely used to uncover latent relationships without labelling schemes.
 
@@
 \begin{figure}[t]
-    \includegraphics[width=0.45\textwidth]{images/search_space_3.png}
+    \includegraphics[width=0.43\textwidth]{images/search_space_3.png}
     \caption{Modularity search space of an \textit{E. coli} metabolic network.
@@
   The inset (top) demonstrates the landscape of the high modularity region. 
-  Figure generated with the software of Good \textit{et al.}\cite{good2010performance}.}
+  Figure generated with the software of Good \textit{et al.} \cite{good2010performance}.}
     \label{fig:modular_search_space}
@@
 \section{Exploiting the modularity query space}
-To characterise latent community structure, one of the most popular approaches is to use modularity maximisation \cite{newman2004}.
-The modularity quality function of a partition on a graph is given by the equation
+To characterise latent community structure, one of the most popular approaches is to use modularity maximisation given by the equation \cite{newman2004}
 \begin{equation}\label{eq:modularity}
@@
 Each random partition is used as the starting partition for the greedy Louvain process.
-In principle, any search exploration procedure, such as simulated annealing \cite{GuimeraNature2005} could be used.
-The Louvain algorithm is selected as it is fast, running in $O(n \log n)$ time complexity \cite{blondel2008fast}, and because it is a greedy algorithm and is guaranteed to stop after finding a locally maximal solution.
+In principle, any search exploration procedure, such as simulated annealing \cite{good2010performance} could be used.
+The Louvain algorithm was selected as it is fast, running in $O(n \log n)$ time complexity \cite{blondel2008fast}, and because it is a greedy algorithm and is guaranteed to stop after finding a locally maximal solution.
 
@@
 Given that there is no free lunch and it is impossible to know every solution, one can only ensure a full coverage index through an exhaustive search over the $2^m$ possible starting cut sets.
-Consequently, the approach taken here is to use a large but not exhaustive subset of the possible solutions using a suitably large space 2000 solutions for the networks studied in this paper.
-\footnote{Initial results indicated that a smaller space of partitions is possible but further work is required to asses the best number of partitions in a practical context}.
+Consequently, the approach taken here is to use a large but not exhaustive subset of the possible solutions using a suitably large space 2000 solutions for the networks studied in this paper
+\footnote{Initial results indicate that a significantly smaller space of partitions may still yield high quality results but we note that further work is required to asses the best number of partitions in a practical context.}.
 
@@
 $\delta(u, v)$ is the Dirac delta function that equals 1 if $c^{p}_i$ and  $c^{p}_j$ are the same cluster and $0$ otherwise.
-As a simple example, for a pair of vertices $i$ and $S$ such that $S = {j}$ we would consider $\mu_i$ to be the number of times $i$ and $j$ appear in the same cluster, given an ensemble of network clusterings.
+As a simple example, for a pair of vertices $i$ and $S$ such that $S = \{j\}$ we would consider $\mu_i$ to be the number of times $i$ and $j$ appear in the same cluster, given an ensemble of network clusterings.
 We define $\mu_i(S)$ for all vertices in the network, including those in $S$.
@@
 The cross validation procedure we devise is described as follows and depends on the size of the community and the number of initial seed labels being used.
-For this work we would like to capture binary classification  performance, \textit{true positives (tp), true negatives (tn), false positives (fp)} and \textit{false negatives (fn)}, on our datasets of community membership.
+For this work we would like to capture binary classification  performance, \textit{true positives (tp)}, \textit{true negatives (tn), false positives (fp)} and \textit{false negatives (fn)}, on our datasets of community memberships.
+In order to generate the different sets for the cross validation we take each label set and generate unique sample sets of vertices from the known true positive labels.
+
+We also note that though each node can have multiple labels, in the tests performed in this study we only consider performance on individual labels.
 As the seed label sets can be as small as 3 vertices, exhaustive cross validation is not possible for all labelling schemes.
@@
 It should therefore be noted that presented receiver operator characteristic (ROC) scores are, therefore, dependent on community sizes.
+We also note that we do not consider separate training and test sets in this study as the method does not use any examples when building the model from partitions of the graph.
+
+Formally, the steps for this procedure with a given label set $S$ are outlined as follows:
+\begin{itemize}
+ \item Generate up to 120 unique subsets of size $s$, sampled without replacement (set $T$).
+ \item For each test subset $\{\forall S_t \in T | S_t \subset S \wedge |S_t| = s \}$, generate the $\mu_i(S_t)$ score for all vertices in the network
+ \item Exclude vertices in $S_t$ from the test
+ \item Consider all nodes in nodes in $S$ but not in $S_t$ to be the \textit{tp} set.
+ \item Consider each of the nodes in $V$ not in $S$ to be the \textit{tn} set.
+ \item Generate an average ROC curve interpolated from all test subsets.
+ \end{itemize}
+
+Results presented are based on interpolated average ROC curves for all labels on each of the data sets.
 
@@
 To evaluate how our method performs we use the undirected, unweighted LFR benchmark \cite{lancichinetti2008benchmark} in overlapping and non-overlapping forms.
-We test the area under the ROC curve (AUC) scores for networks synthetically generated with the LFR benchmark.
+We test the area under the ROC curve (AUC) scores for networks varying the mixing parameter (fraction of edges between communities) and the fraction of overlapping nodes.
 In these tests, the community distribution is defined with a power law coefficient of $-1.0$, the degree distribution is defined with a power law coefficient of $-2.0$.
@@
     \centering
-    \begin{subfigure}[b]{0.48\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
         \centering
@@
     \end{subfigure}
-    \begin{subfigure}[b]{0.48\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
         \centering
@@
      Data points represent mean auc scores for all communities on 100 sampled networks at varying mixing coefficients.
-     Error bars represent one standard deviation..}
+     Error bars represent one standard deviation.}
      \label{fig:auc_no_overlap}
@@
      Data points represent mean auc scores for all communities on 100 sampled networks at varying overlapping fraction of nodes.
-     Error bars represent one standard deviation..}
+     Error bars represent one standard deviation.}
      \label{fig:auc_overlap}
@@
         \centering
-        \includegraphics[width=\textwidth]{images/rocs/eu_email.png}
+        \includegraphics[width=\textwidth]{images/rocs/eu_email.eps}
         \caption{EU email departments}
@@
         \centering
-        \includegraphics[width=\textwidth]{images/rocs/yeast_ppi.png}
+        \includegraphics[width=\textwidth]{images/rocs/yeast_ppi.eps}
         \caption{Yeast PPI protein complexes}
@@
         \centering
-        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi_combined.png}
+        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi_combined.eps}
         \caption{Arabidopsis PPI protein complexes}
@@
         \centering
-        \includegraphics[width=\textwidth]{images/rocs/ecoli_ppi.png}
+        \includegraphics[width=\textwidth]{images/rocs/ecoli_ppi.eps}
         \caption{E coli PPI protein complexes}
@@
   For the Arabidopsis dataset, the complex sources were more limited.
-  Consequently, we obtained all gene ontology annotations under the GO term \textit{``Protein-containing complex''} from AmiGO \cite{carbon2009amigo} with the label ``physical interaction evidence used in manual assertion''.
+  Consequently, we obtained all gene ontology annotations under the GO term \textit{``Protein-containing complex''} from AmiGO \cite{carbon2009amigo} where experimentally collected physical interaction evidence was acquired.
   At the time of writing, this resulted in 7 complexes containing between 4 and 12 nodes.
@@
 These results represent ROC curves and mean AUC statistics.
-For all the datasets in this study, binary community classification is high, with an average AUC scores above 0.83, even when using only a single seed node.
+For all the datasets in this study, binary community classification is high, with an average AUC scores above 0.87, even when using only a single seed node.
 In the case of the \textit{Arabidopsis thaliana} network the protein complexes tested are significantly smaller than for other networks and so a comparison of seed sizes is not possible.
@@
 
-The method also serves as a useful network reduction tool where the quality of labels is not as well defined.
-This visually is demonstrated for the \textit{Arabidopsis PPI} dataset shown in Figure \ref{fig:query_example} with a hand selected gene ontology term from AmiGO \cite{carbon2008amigo}.
-Figure \ref{fig:GO_TERM_ROCS}
+\subsubsection{Tests on gene ontology labels}
 
@@
 
-\begin{figure*}
+\begin{figure*}[t]
      \centering
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{images/rocs/yeast_ppi.png}
+        \includegraphics[width=\textwidth]{images/rocs/yeast_ppi_amigo.eps}
         \caption{Yeast PPI GO terms}
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi_combined.png}
+        \includegraphics[width=\textwidth]{images/rocs/arabidopsis_ppi_amigo.eps}
         \caption{Arabidopsis PPI GO terms}
     \end{subfigure}
-    \begin{subfigure}[b]{0.3\textwidth}
+    \begin{subfigure}[b]{0.31\textwidth}
         \centering
-        \includegraphics[width=\textwidth]{images/rocs/ecoli_ppi.png}
+        \includegraphics[width=\textwidth]{images/rocs/ecoli_ppi_amigo.eps}
         \caption{E coli PPI GO terms}
     \end{subfigure}
-    \caption{Receiver operator characteristic (ROC) curves for the high quality labels for real networks described in Section \ref{sec:real_networks}. 
+    \caption{Receiver operator characteristic (ROC) curves for gene ontology labels for real networks described in Section \ref{sec:real_networks}. 
     Results represent the averages over all receiver operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.
@@
 
+In a practical situation the high quality label sets described above are not likely to be available.
+Consequently, we wish to to highlight that the method also serves as a useful network reduction tool where the quality of labels is not well defined.
+In order to achieve this goal, for each of the biological data sets in this study, we acquired all Gene Ontology terms for each of the proteins from AmiGO \cite{carbon2008amigo}.
+Gene Ontology is a controlled vocabulary of terms associated with biological functions in three broad categories of Cellular Components (CC),  Metabolic Functions (MF) and Biological Processes (BP), forming a hierarchy of terms and associated sub terms.
+
+These labels are not all likely to be represented within the protein-protein interaction networks, though many biological processes are.
+For the Yeast, \textit{Arabidopsis} and \textit{E coli} PPIs we collected 85, 549 and 420 terms covering at least 3 nodes, respectively.
+As expected, average ROC and AUC scores shown in Figure \ref{fig:GO_TERM_ROCS} are considerably lower than for the Protein complexes. 
+However, this approach should be considered in contrast to conventional gene enrichment strategies on conventional network clusters \cite{chen2013enrichr}.
+
+The use of a $\mu_i(S)$ score on a network is visually demonstrated for the \textit{Arabidopsis PPI} dataset shown in Figure \ref{fig:query_example} with the hand selected GO term \textit{``SNAP receptor activity''}.
+
 \section{Discussion}
-The semi-supervised method for vertex classification presented in this work has shown to have good results on both synthetic benchmarks and real-world datasets.
+The semi-supervised method for vertex classification presented in this work has been shown to produce good results on both synthetic benchmarks and real-world datasets.
 Interestingly, this method is capable of correctly classifying communities with only a small number of seed query vertexes.
@@
 The fact that the method is able to uncover small protein complexes seems to contradict the principle that modularity maximisation algorithms have a resolution limit \cite{fortunato2007resolution}.
-Whilst this appears to be the case it is important to not that the resolution limit applies to a single partition of space.
+Whilst this appears to be the case it is important to note that the resolution limit applies to a single partition of space.
 Further work is needed to investigate why small communities are still detectable.
@@
 In other words, whilst the large communities they reside in changes significantly, the small cluster of nodes is always clustered in the same community, regardless of the partition.
-We do note that, where communities are very small, any approach will extremely sensitive to false positive and false negative results.
+We do note that, where communities are very small, any approach will be extremely sensitive to false positive and false negative results.
 As such, this should be considered when using any method of this form as an exploratory tool.
@@
 In contrast, the query approach presented here does not require the queries to be a self contained sub-graph.
-Indeed, queries can contain spurious nodes that are topologically distinct from one another - the result is that the $\mu_i(S)$ score for the query set will likely be very low.
+Indeed, queries can contain spurious nodes that are topologically distant from one another - the result is that the $\mu_i(S)$ score for the query set will likely be very low.
 Further investigation into how to evaluate the quality of high average $\mu_i(S)$ for $i \in S$ is left to future work.
@@
 In contrast,  the recent approach by Newman and Clauset \cite{newman2016structure}, for example, uses examples in which practically the entire network contains labels which is less useful from the perspective of label discovery.
-However, these methods generally consider if a labelling scheme (such as demography in a social network) accurately describes the structure of the network.
 
@@
 In the case of synthetic networks communities are correctly detected up to the detectability threshold.
-For real world networks with small label sets, average AUC scores were above 0.88 for all the datasets tested in this study.
+For real world networks with small label sets, average AUC scores were above 0.87 for the high quality datasets tested in this study.
 
@@
 Furthermore, as the algorithm is trivial to run in a distributed manner, this approach could be applied to larger graphs than those studied in this paper.
-Further research should also be conducted into how this approach could be applied to other partition quality functions.
+Further research should also be conducted into how this approach could be applied to other partition quality functions, such as the infomap algorithm \cite{Rosvall:2008fi}.
+The method was implemented in python and all software will be made open source at a later date.
 
 \section*{Acknowledgements}
-We are grateful for access to the University of Nottingham High Performance Computing Facility in support of this work.
-This work was supported by the Biotechnology and Biological Sciences Research Council grant BB/L013940/1.
-We would like to thank Nicole Pearcy and Jenna Reps for assistance with this manuscript.
+We would like to thank Nicole Pearcy and Jenna Reps for assistance preparing this manuscript.
+We are grateful for access to the University of Nottingham High Performance Computing Facility.
+This work was supported by the UK Biotechnology and Biological Sciences Research Council (BBSRC) grant BB/L013940/1.
 
-\bibliographystyle{acm} 
+\bibliographystyle{ACM-Reference-Format} 
 \bibliography{references}

### 2018-05-08 experiments/real_networks.py

@@ -99,6 +99,9 @@ def load_network(graph_path, graph_name, communities_path, index_path, node_type
             rcomms[c] = nc
             rcomm_l.append(nc)
 
+
+    lengths = [len(x) for x in rcomm_l]
+    print(len(rcomms), min(lengths), max(lengths))
     return graph, rcomms, mmatrix, nmap
 
 
@@ -158,6 +161,21 @@ def gen_roc_curves(mmatrix, comm, s, cid):
     funcs = (delayed(samp_roc_and_auc)(samp, mmatrix, comm, cid, s) for samp in unique_sampler(comm, s))
     results = Parallel(n_jobs=cpu_count(), backend='threading')(funcs)
     return list(results)
+
+
+def avg_mui_score(com_id, comm, nmap, mmatrix):
+    # map to matrix
+    qnodes = np.array([nmap[x] for x in comm])
+    # get query_vec
+    vec = louvain_consensus.query_vector(qnodes, mmatrix)
+    # mean for internal vector
+    return com_id, np.mean(vec)
+
+
+def gen_avg_mui_scores(mmatrix, nmap, comms):
+    funcs = (delayed(avg_mui_score)(com_id, comm, nmap, mmatrix) for com_id, comm in comms.items())
+    results = dict(Parallel(n_jobs=cpu_count(), backend='threading')(funcs))
+    return results
 
 
 def get_rocs(mmatrix, nmap, comms, seed_sizes=(1, 3, 7, 15)):
@@ -262,9 +280,9 @@ def generate_results(network, overwrite=False):
     dt = real_networks[network]
 
     roc_df_path = os.path.join("results", network) + "_roc_res.p"
-
+    graph, comms, mmatrix, nmap = load_network(dt["path"], network, dt["clusters"], dt["index"], dt["node_type"])
     if overwrite or not os.path.exists(roc_df_path):
-        graph, comms, mmatrix, nmap = load_network(dt["path"], network, dt["clusters"], dt["index"], dt["node_type"])
+
         print(network, "gen_roc_curves")
         roc_results = get_rocs(mmatrix, nmap, comms)
         with open(roc_df_path, "wb+") as roc_df:
@@ -278,6 +296,14 @@ def generate_results(network, overwrite=False):
         print(network, "gen_sig_scores")
         with open(sign_df_path, "wb+") as sig_df:
            pickle.dump(sigscores, sig_df)
+
[…]

### 2018-05-08 article/article.tex
Submission copy

@@
 However, in this paper we argue that this is not a flaw with the modularity maximisation algorithm but, rather, information that can be used to aid the context specific classification of functional relationships between vertices.
-Formally, we present an approach to generating a high value modularity consensus space for a network, based on the ensemble space of locally optimal modular partitions.
-We then use this approach to uncover latent relationships between sets initial query sets.
+Formally, we present an approach for generating a high value modularity consensus space for a network, based on the ensemble space of locally optimal modular partitions.
+We then use this approach to uncover latent relationships, given small query sets.
 The methods developed in this paper are applied to biological and social datasets with ground-truth label data, using a small number of examples used as seed sets to uncover relationships.
@@
 \section{Introduction}
-
 A fundamental issue at the heart of machine learning methods applied to large scale datasets is the ability to correctly identify classes of related objects in an unsupervised manner.
@@
 In this paper, we develop an intuitive method to use the uncertainty amongst a high number of near optimal solutions to measure context sensitive relationships between small sets of labelled vertices.
-This approach can be based on labels that are not first order neighbours in order to find other potentially related vertices.
+This approach can be based on labels that are not first order neighbours to find other potentially related vertices.
 
@@
 
-As a form of unsupervised machine learning module extraction methods largely focus on optimising some objective function with the goal of finding meaningful clusterings.
+As a form of unsupervised machine learning, module extraction methods largely focus on optimising some objective function with the goal of finding meaningful clusterings.
 Perhaps the most popular of these methods is that of modularity maximisation \cite{newman2004}, which seeks to find the most unexpected partition of a graph with respect to a given null model.
@@
 
-However, in this paper, we do not seek to find a single ``best'' partition, either overlapping or not and our objective is not to uncover labels but to use limited and small sets of labels to give the notion of a membership score to some grouping.
+However, in this paper, we do not seek to find a single ``best'' partition, whether overlapping or not and our objective is not to uncover labels but to use limited and small sets of labels to give the notion of a membership score to some grouping.
 Instead, we use the large number of highly modular solutions to form the index for a search query system.
@@
 We propose an algorithm that pre-computes an index of clusterings for a given complex network, based on the fast greedy Louvain algorithm \cite{blondel2008fast}, used in a distributed manner.
-The detected clusters then form the basis of a search algorithm that allows one to compute the relatedness of subsets of nodes.
+The detected clusters then form the basis of a search algorithm that allows one to compute the relatedness of nodes to a given query set.
 The querying method is a polynomial time algorithm that could be trivially adapted to form the basis of many user facing applications.
@@
 Each of these solution partitions are extremely close to the global maxima, making it both difficult to find the optimal value of $Q$ and difficult to argue that the highest scoring partition is the ``true'' community structure.
-This fact is visually demonstrated with the software from \cite{good2010performance} in Figure \ref{fig:modular_search_space}, which shows the modularity search space of an \textit{E coli} metabolic network reconstruction \cite{GuimeraNature2005}.
-The similarity between the partitions is compared with variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear}.
+This fact is visually demonstrated with the software from \cite{good2010performance} in Figure \ref{fig:modular_search_space}, which shows the modularity search space of an \textit{E.
+coli} metabolic network reconstruction \cite{GuimeraNature2005}.
+The similarity between the partitions is compared with the variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear}.
 
@@
 A broad outline of the proposed method is presented in Figure \ref{fig:algorithm_outline}.
-In essence, the objective is to use multiple modular representation of a given dataset to generate a relatedness score for a given set of query vertices.
+In essence, the objective is to use multiple modular representations of a given dataset to generate a relatedness score for a given set of query vertices.
 
 In order to cover the space of high modularity partitions, randomly generated starting partitions are computed with a random cut set.
-To achieve this each edge is either placed inside the cut set or not as the result of an independent Bernoulli trial. 
+To achieve this, each edge is either placed inside the cut set or not as the result of an independent Bernoulli trial. 
 Each random partition is used as the starting partition for the greedy Louvain process.
@@
 Given that there is no free lunch and it is impossible to know every solution, one can only ensure a full coverage index through an exhaustive search over the $2^m$ possible starting cut sets.
-Consequently, the approach taken here is to use a large but not exhaustive subset of the possible solutions using a suitably large space 2000 solutions for the networks studied in this paper
+Consequently, the approach taken here is to use a large but not exhaustive subset of the possible solutions using a suitably large space of 2000 solutions for the networks studied in this paper
 \footnote{Initial results indicate that a significantly smaller space of partitions may still yield high quality results but we note that further work is required to asses the best number of partitions in a practical context.}.
@@
 \subsection{Measuring the quality of relationships} \label{sec:expansion}
-Given a query of vertices, the relatedness to other vertexes in a network is quantifiable by the fraction of times they are clustered with the query set, given the set of high quality partitions.
+Given a query of vertices, the relatedness to other vertices in a network is quantifiable by the fraction of times they are clustered with the query set, given the set of high quality partitions.
 Formally, this can be expressed in terms of the \textit{expansion score} of a given vertex,
@@
 \end{equation}
-where $S$ denotes a query set, $P$ is a given partition in the space of all high quality partitions $\mathcal{P}$, $c^{p}_{i}$ indicates the partition vertex $i$ is contained in within partition $P$ and
+where $S$ denotes a query set, $P$ is a given partition in the space of all high quality partitions $\mathcal{P}$, $c^{p}_{i}$ indicates the cluster vertex $i$ is contained in within partition $P$ and
 $\delta(u, v)$ is the Dirac delta function that equals 1 if $c^{p}_i$ and  $c^{p}_j$ are the same cluster and $0$ otherwise.
@@
 In order to generate the different sets for the cross validation we take each label set and generate unique sample sets of vertices from the known true positive labels.
+We also note that although each node can have multiple labels, in the tests performed in this study we only consider performance on individual labels.
 
-We also note that though each node can have multiple labels, in the tests performed in this study we only consider performance on individual labels.
-As the seed label sets can be as small as 3 vertices, exhaustive cross validation is not possible for all labelling schemes.
-Consequently, cross validation is either conducted on an exhaustive set of all possible $\binom{|L|}{s}$ unique labellings or 120 seed queries sampled without replacement\footnote{This is equivalent to $\binom{10}{3}$ combinations, an exhaustive sample would not be possible for the larger communities in this study.}, where $L$ is the set of gold standard true labels and $s$ is the size of the randomly selected seed sets.
-It should therefore be noted that presented receiver operator characteristic (ROC) scores are, therefore, dependent on community sizes.
-We also note that we do not consider separate training and test sets in this study as the method does not use any examples when building the model from partitions of the graph.
+As the seed label sets can be as small as 3 vertices, exhaustive cross validation was not possible for all labelling schemes.
+Consequently, cross validation is either conducted on an exhaustive set of all possible $\binom{|S|}{s}$ unique labellings or 120 seed queries sampled randomly without replacement from the possible subsets \footnote{This is equivalent to $\binom{10}{3}$ combinations, an exhaustive sample would not be possible for the larger communities in this study.}, where $S$ is the set of gold standard true labels and $s$ is the size of the randomly selected seed sets.
+It should therefore be noted that presented receiver operator characteristic (ROC) scores are dependent on community sizes.
+We also note that we do not consider separate training and test sets in this study as the method does not use any examples when building the index space from partitions of the graph.
 
@@
 \begin{itemize}
- \item Generate up to 120 unique subsets of size $s$, sampled without replacement (set $T$).
+ \item Generate up to 120 unique subsets of size $s$, randomly sampled without replacement (set $T$).
  \item For each test subset $\{\forall S_t \in T | S_t \subset S \wedge |S_t| = s \}$, generate the $\mu_i(S_t)$ score for all vertices in the network
  \item Exclude vertices in $S_t$ from the test
- \item Consider all nodes in nodes in $S$ but not in $S_t$ to be the \textit{tp} set.
- \item Consider each of the nodes in $V$ not in $S$ to be the \textit{tn} set.
+ \item Consider all nodes in $S$ but not in $S_t$ to be the true positive set.
+ \item Consider each of the nodes in $V$ not in $S$ to be the true negative set.
  \item Generate an average ROC curve interpolated from all test subsets.
  \end{itemize}
-
-Results presented are based on interpolated average ROC curves for all labels on each of the data sets.
 
@@
     \caption{Non-overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
-     Data points represent mean auc scores for all communities on 100 sampled networks at varying mixing coefficients.
+     Data points represent mean AUC scores for all communities on 100 sampled networks at varying mixing coefficients.
      Error bars represent one standard deviation.}
@@
 \subsubsection{Overlapping modules.} 
-In figure \ref{fig:auc_overlap} we show the results of network performance when tested against an increasing level of overlapping communities.
+In Figure \ref{fig:auc_overlap} we show the results of network performance when tested against an increasing level of overlapping communities.
 For these tests we fix the mixing coefficient at $0.3$.
@@
     \caption{Overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
-     Data points represent mean auc scores for all communities on 100 sampled networks at varying overlapping fraction of nodes.
+     Data points represent mean AUC scores for all communities on 100 sampled networks at varying overlapping fraction of nodes.
      Error bars represent one standard deviation.}
@@
         \includegraphics[width=\textwidth]{images/rocs/ecoli_ppi.eps}
-        \caption{E coli PPI protein complexes}
+        \caption{E. coli PPI protein complexes}
     \end{subfigure}
@@
   \item \textbf{\textit{Escherichia coli} protein-protein interaction network (E.coli PPI) \cite{su2007bacteriome}}
-  For the \textit{E coli} dataset we used manually curated interacting proteins from \cite{su2007bacteriome}.
+  For the \textit{E. coli} dataset we used manually curated interacting proteins from \cite{su2007bacteriome}.
   The network contains 1913 nodes and 7252 edges, the protein complexes range in size between 3 and 65 nodes.
@@
 (B) Shows a reduced view of the network where a threshold of $\mu_i(S) > 0.8$ is selected, reducing the network to 404 nodes.
-Blue nodes indicate those in the randomly selected 3 query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
+Blue nodes indicates the 3 randomly selected query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
 (C) Shows an example ROC curve from the cross validation described in the main text.
@@
         \includegraphics[width=\textwidth]{images/rocs/ecoli_ppi_amigo.eps}
-        \caption{E coli PPI GO terms}
+        \caption{E. coli PPI GO terms}
     \end{subfigure}
@@
 In a practical situation the high quality label sets described above are not likely to be available.
-Consequently, we wish to to highlight that the method also serves as a useful network reduction tool where the quality of labels is not well defined.
+Consequently, we wish to highlight that the method also serves as a useful network reduction tool where the quality of labels is not well defined.
 In order to achieve this goal, for each of the biological data sets in this study, we acquired all Gene Ontology terms for each of the proteins from AmiGO \cite{carbon2008amigo}.
@@
 These labels are not all likely to be represented within the protein-protein interaction networks, though many biological processes are.
-For the Yeast, \textit{Arabidopsis} and \textit{E coli} PPIs we collected 85, 549 and 420 terms covering at least 3 nodes, respectively.
+For the Yeast, \textit{Arabidopsis} and \textit{E. coli} PPIs we collected 85, 549 and 420 terms covering at least 3 nodes, respectively.
 As expected, average ROC and AUC scores shown in Figure \ref{fig:GO_TERM_ROCS} are considerably lower than for the Protein complexes. 
@@
 The semi-supervised method for vertex classification presented in this work has been shown to produce good results on both synthetic benchmarks and real-world datasets.
-Interestingly, this method is capable of correctly classifying communities with only a small number of seed query vertexes.
+Interestingly, this method is capable of correctly classifying communities with only a small number of seed query vertices.
 These results show that this query method could be used as a powerful exploratory tool in network analysis.
@@
 Further work is needed to investigate why small communities are still detectable.
-However, we speculate that is likely due to the fact that the co-classification of vertices between different partitions remains fairly tolerant to changes.
+However, we speculate that it is likely due to the fact that the co-classification of vertices between different partitions remains fairly tolerant to changes.
 In other words, whilst the large communities they reside in changes significantly, the small cluster of nodes is always clustered in the same community, regardless of the partition.
@@
 This is interesting as in most sampled cases the relevant nodes are unlikely to be direct neighbours.
-From the perspective of exploratory study, this implies that a small number of query vertices can be used to find potentially related vertices.
+From the perspective of exploratory studies, this implies that a small number of query vertices can be used to find potentially related vertices.
 
@@
 This work relates very strongly to the idea of local community detection, more specifically the idea of \textit{seed set expansion} \cite{gleich2012vertex}.
-Here, a given seed set is created a random walks are analysed to find clearly related communities of vertices.
+Here, a given seed set is created and random walks are analysed to find clearly related communities of vertices.
 One of the most common approaches to finding related vertices in a network is the random walk with restart (RWR) \cite{can2005analysis, kohler2008walking}.
@@
 
-This also work presents a number of interesting potential future avenues for research, such as observing how query sets change in time dynamic or multi-scale networks.
+This work presents a number of interesting potential future avenues for research, such as observing how query sets change in time dynamic or multi-scale networks.
 Furthermore, as the algorithm is trivial to run in a distributed manner, this approach could be applied to larger graphs than those studied in this paper.

### 2018-06-12 article/article.tex
Updated footnote to exlpain figure better.

@@
 coli} metabolic network reconstruction \cite{GuimeraNature2005}.
-The similarity between the partitions is compared with the variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear}.
+The similarity between the partitions is compared with the variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear} \footnote{The reader should note that axis on these plots are a result of the dimensionality reduction performed by curvilinear component analysis \cite{demartines1997curvilinear} and, therefore, have no natural interpretation.}.
 

### 2018-06-12 cluster_query_tool/random_walk.py
Added random walk with restart functions

@@ -1,0 +1,40 @@
+import networkx as nx
+import numpy as np
+
+
+def diffusion_kernel(graph, query_nodes, beta=0.1):
+    assert isinstance(graph, nx.Graph)
+
+    l = np.array(nx.laplacian_matrix(graph).todense())
+    diff_k = np.exp(-beta * l)
+
+    score = np.zeros(graph.number_of_nodes())
+    for i in query_nodes:
+        score += diff_k[i]
+    return score
+
+
+def rwr(graph, query_nodes, restart_prob, _dthreshold=10e-7):
+    # Get adjacency matrix
+    a = nx.to_numpy_array(graph)
+
+    # Normalise the column vectors
+    nr = a.sum(axis=1)
+    w = a / nr
+
+    # initialise p_o
+    p_o = np.zeros(graph.number_of_nodes())
+    # p_o is the set of "seed" nodes that the walker would randomly jump to
+    np.put(p_o, query_nodes, 1.0 / len(query_nodes))
+    # Delta (change in L1 norm between p_t an p_tp1) should approach zero when the walker is at steady state
+    # in other words Delta = 0 after an infinite random walk
+    delta = 1.0
+    # Initialise until p_t
+    p_t = np.copy(p_o)
+    # restart is a fixed vector (i.e. the probability of jumping back to one of the seed nodes)
+    while delta > _dthreshold:
+        p_tp1 = ((1 - restart_prob) * np.dot(w, p_t)) + restart
+        delta = np.linalg.norm(p_t - p_tp1, 1)
+        p_t = p_tp1
+
+    return p_t

### 2018-06-12 cluster_query_tool/random_walk.py
fixed bug in random walk

@@ -32,6 +32,7 @@ def rwr(graph, query_nodes, restart_prob, _dthreshold=10e-7):
     # Initialise until p_t
     p_t = np.copy(p_o)
     # restart is a fixed vector (i.e. the probability of jumping back to one of the seed nodes)
+    restart = p_o * restart_prob
     while delta > _dthreshold:
         p_tp1 = ((1 - restart_prob) * np.dot(w, p_t)) + restart
         delta = np.linalg.norm(p_t - p_tp1, 1)

### 2018-06-19 article/article.tex
Minor article results changes

@@
 % DOI
-\acmDOI{}
+\acmDOI{-}
 
@@
 %Conference
-\acmConference[MLG 2018]{14th International Workshop on Mining and Learning with Graphs}{Aug 20, 2018}{United Kingdom}
+\acmConference[KDD MLG 2018]{14th International Workshop on Mining and Learning with Graphs}{Aug 20, 2018}{London, United Kingdom}
 \acmYear{2018}
-\copyrightyear{2018}
+\copyrightyear{2018 Copyright held by the owner/author(s).}
 \acmPrice{}
@@
 \begin{figure}[t]
-    \includegraphics[width=0.43\textwidth]{images/search_space_3.png}
+    \includegraphics[width=0.48\textwidth]{images/search_space_3.png}
     \caption{Modularity search space of an \textit{E. coli} metabolic network.
@@
 In this study we test a small number of labels that we intend to use in order to evaluate how well our method correctly generalises to discover unlabelled vertices.
+We would like to test a significantly smaller number of seed nodes than two class classification methods used in previous studies, which use leave-one-out cross validation \cite{kohler2008walking}.
 The cross validation procedure we devise is described as follows and depends on the size of the community and the number of initial seed labels being used.
@@
 
+\subsection{Random walk with restart}
+As a comparison, we compare our method with the commonly used random walk with restart method as described in \cite{kohler2008walking}.
+This simulates an infinite random walk with a probability, $\alpha$ that a walker would teleport back to the initial seed nodes. 
+Formally, the random walk with restart algorithm uses the form
+\begin{equation} \label{eq:rwr}
+ \vec{p}_{t+1} = (1 - \alpha) W \vec{p}_t + \alpha \vec{p}_0,
+\end{equation}
+where $W$ is the row normalised adjacency matrix of a graph, $\vec{p}_0$ is the initial walk vector such that $\vec{p}_0 = \frac{1}{|S|}$ for vertices in the seed set.
+The random walk algorithm repeats equation \ref{eq:rwr} from $\vec{p}_0$ until the L1 norm between  $\vec{p}_t$ and  $\vec{p}_{t+1}$ converges to 0.
+For the tests performed in this work we use a restart probability $\alpha = 0.5$.
+
 \subsection{Synthetic networks}
@@
 Using larger seed sets also improves accuracy with some prediction of true communities being possible at extremely high levels of mixing.
+Overall, results are comparable to the random walk with restart method, with slightly improved performance with a smaller number of seed nodes.
 
@@
 In order to test performance we varied the fraction of nodes that are in more than one community.
-Interestingly, the method still has an AUC score above 0.5 when all nodes are placed in multiple communities.
+The method still has an AUC score above 0.5 when all nodes are placed in multiple communities.
 This indicates that the method is capable of uncovering latent overlapping memberships even when given a relatively small number of seed nodes.
+As with the non-overlapping results, the scores are comparable with the rwr method with performance slightly better in the case of 1000 node models.
 
@@
      \centering
-    \begin{subfigure}[b]{0.48\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
         \centering
@@
 
-    \begin{subfigure}[b]{0.48\textwidth}
+    \begin{subfigure}[b]{0.45\textwidth}
         \centering
@@
     \caption{Receiver operator characteristic (ROC) curves for the high quality labels for real networks described in Section \ref{sec:real_networks}. 
-    Results represent the averages over all receiver operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.
-    Shaded areas indicate one standard deviation.}
+    Results represent the averages over all receiver operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.}
     \label{fig:quality_label_rocs}
@@
 \subsubsection{Tests on gene ontology labels}
-
-\begin{figure*}[t]
-\includegraphics[width=\textwidth]{images/ppi_example_combined.eps}
-\caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
-(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
-(B) Shows a reduced view of the network where a threshold of $\mu_i(S) > 0.8$ is selected, reducing the network to 404 nodes.
-Blue nodes indicates the 3 randomly selected query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
-(C) Shows an example ROC curve from the cross validation described in the main text.
-}
-\label{fig:query_example}
-\end{figure*}
-
-\begin{figure*}[t]
+\begin{figure*}[]
      \centering
@@
     \caption{Receiver operator characteristic (ROC) curves for gene ontology labels for real networks described in Section \ref{sec:real_networks}. 
-    Results represent the averages over all receiver operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.
-    Shaded areas indicate one standard deviation.}
+    Results represent the averages over all receiver operating characteristic scores from all samples of label sets with the cross validation procedure described in \ref{sec:cross_validation}.}
     \label{fig:GO_TERM_ROCS}
+\end{figure*}
+
+\begin{figure*}[t]
+\includegraphics[width=0.8\textwidth]{images/ppi_example_combined.eps}
+\caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
+(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
+(B) Shows a reduced view of the network where a threshold of $\mu_i(S) > 0.8$ is selected, reducing the network to 404 nodes.
+Blue nodes indicates the 3 randomly selected query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
+(C) Shows an example ROC curve from the cross validation described in the main text.
+}
+\label{fig:query_example}
 \end{figure*}
@@
 In RWR the relatedness of any pair of vertices can be seen as the probability of a particle traversing the graph starting at a given vertex and ending at another.
-The restart aspect of the random walk can be thought of as the probability of the walker teleporting back to the start vertex with some none zero probability. 
+The restart aspect of the random walk can be thought of as the probability of the walker teleporting back to the start vertex set, as a fixed parameter. 
 The higher the probability of the walker ending up at a given vertex, the more likely it is that the two vertices are related.
@@
 The RWR probability as analogous to the value of $\mu_i(S)$ presented above.
-Further investigation needs to be conducted into how similar local community based approaches, such as random walks, compare with this method.
 
@@
 In the case of synthetic networks communities are correctly detected up to the detectability threshold.
-For real world networks with small label sets, average AUC scores were above 0.87 for the high quality datasets tested in this study.
+For real world networks with small label sets, average AUC scores were above 0.87 and comparable to the random walk with restart method for the high quality datasets tested in this study.
 
@@
 
-% \nocite{*}
 \end{document}

### 2018-06-19 experiments/lfr_nooverlap.py

@@ -268,7 +268,7 @@ def gen_figure(n):
     fig, ax = plt.subplots()
     fig.set_dpi(90)
     ax.set_ylabel("Mean AUC")
-    ax.set_xlabel("Mixing coefficient $\mu$")
+    ax.set_xlabel("Mixing coefficient")
     ax.set_ylim(0.4, 1.01)
     ax.set_xlim(0.0, 1.01)
     x_vals = df['mixing'].unique()

### 2018-06-19 experiments/real_networks.py

@@ -353,7 +353,7 @@ def handle_results(network):
     fig = plot_roc_curve(df, df_rwr)
     fig.savefig("article/images/rocs/{}.png".format(network))
     fig.savefig("article/images/rocs/{}.svg".format(network))
-    #fig.savefig("article/images/rocs/{}.eps".format(network))
+    fig.savefig("article/images/rocs/{}.eps".format(network))
 
     return df
 

### 2018-06-19 experiments/lfr_nooverlap.py
Start jobs for partial hpc runs

@@ -173,12 +173,13 @@ python {_file} auc_compute {n} {mu:.2f} $JOB {results_folder}
 @click.command()
 @click.argument("n")
 @click.option("--mu_steps", default=10)
+@click.option("--start_job", default=1)
 @click.option("--network_samples", default=10)
 @click.option("--walltime", default="01:30:00")
 @click.option("--request", default="select=1:ncpus=16:mem=31gb")
 @click.option("--execute/--no_exec", default=False)
 @click.option("--queue", default="HPCA-01839-EFR")
-def run_jobs_rwr(n, mu_steps, network_samples, walltime, request, execute, queue):
+def run_jobs_rwr(n, mu_steps, network_samples, start_job, walltime, request, execute, queue):
     script_template = """#!/bin/bash
 #PBS -l {request}
 #PBS -l {walltime}
@@ -215,12 +216,13 @@ python {_file} auc_compute_rwr {n} {mu:.2f} $JOB {results_folder}
 
     cmd_opt = dict(
         options="",
+        jstart=start_job,
         jcount=network_samples,
         n=n,
         e=err_path,
         o=opt_path,
     )
-    cmd_template = "qsub {options} -J 1-{jcount} {command_file} -e {e} -o {o}"
+    cmd_template = "qsub {options} -J {jstart}-{jcount} {command_file} -e {e} -o {o}"
 
     commands_path = os.path.abspath(os.path.join(os.path.dirname(__file__), 'job_scripts'))
     if not os.path.exists(commands_path):

### 2018-06-19 experiments/lfr_overlap.py

@@ -165,11 +165,12 @@ python {file} auc_compute {n} {ol} $JOB {results_folder}
 @click.command()
 @click.argument("n")
 @click.option("--network_samples", default=10)
+@click.option("--start_job", default=1)
 @click.option("--walltime", default="01:30:00")
 @click.option("--request", default="select=1:ncpus=16:mem=31gb")
 @click.option("--execute/--no_exec", default=False)
 @click.option("--queue", default="HPCA-01839-EFR")
-def run_jobs_rwr(n, network_samples, walltime, request, execute, queue):
+def run_jobs_rwr(n, network_samples, start_job, walltime, request, execute, queue):
     script_template = """#!/bin/bash
 #PBS -k oe
 #PBS -l {request}

### 2018-06-19 experiments/lfr_overlap.py
Start jobs for partial hpc runs

@@ -207,12 +207,13 @@ python {file} auc_compute_rwr {n} {ol} $JOB {results_folder}
 
     cmd_opt = dict(
         options="",
+        jstart=start_job,
         jcount=network_samples,
         n=n,
         e=err_path,
         o=opt_path,
     )
-    cmd_template = "qsub {options} -J 1-{jcount} -e {e} -o {o} {command_file}"
+    cmd_template = "qsub {options} -J {jstart}-{jcount} -e {e} -o {o} {command_file}"
 
     commands_path = os.path.abspath(os.path.join(os.path.dirname(__file__), 'job_scripts'))
     if not os.path.exists(commands_path):

### 2018-06-19 article/article.tex
Code tidy up

@@
 The random walk algorithm repeats equation \ref{eq:rwr} from $\vec{p}_0$ until the L1 norm between  $\vec{p}_t$ and  $\vec{p}_{t+1}$ converges to 0.
-For the tests performed in this work we use a restart probability $\alpha = 0.5$.
+For the tests performed in this work we use a restart probability $\alpha = 0.25$.
 
@@
 This indicates that the method is capable of uncovering latent overlapping memberships even when given a relatively small number of seed nodes.
-As with the non-overlapping results, the scores are comparable with the rwr method with performance slightly better in the case of 1000 node models.
+As with the non-overlapping results, the scores are comparable with the rwr method with performance slightly improved in the case of 1000 node models, but comparable for 5000 node models.
 
@@
 However, in the other networks studied, using 3 or more seed nodes appears to improve results, though for 15 seed nodes the results are not significantly better than with 7 seeds.
+The results of our method are comparable to the random walk with restart approach, which performs better on the datasets tested with the exception of the EU email dataset for which our model performs significantly better.
 
@@
 Gene Ontology is a controlled vocabulary of terms associated with biological functions in three broad categories of Cellular Components (CC),  Metabolic Functions (MF) and Biological Processes (BP), forming a hierarchy of terms and associated sub terms.
+The use of a $\mu_i(S)$ score on a network is visually demonstrated for the \textit{Arabidopsis PPI} dataset shown in Figure \ref{fig:query_example} with the hand selected GO term \textit{``SNAP receptor activity''}.
 
@@
 For the Yeast, \textit{Arabidopsis} and \textit{E. coli} PPIs we collected 85, 549 and 420 terms covering at least 3 nodes, respectively.
-As expected, average ROC and AUC scores shown in Figure \ref{fig:GO_TERM_ROCS} are considerably lower than for the Protein complexes. 
+As expected, average ROC and AUC scores shown in Figure \ref{fig:GO_TERM_ROCS} are considerably lower than for the Protein complexes for both our method and the rwr approach. 
+Interestingly, however, the performance of the rwr approach is significantly worse than one would expect to find at random for the Yeast GO terms.
+The reason for this performance remains unknown.
 However, this approach should be considered in contrast to conventional gene enrichment strategies on conventional network clusters \cite{chen2013enrichr}.
-
-The use of a $\mu_i(S)$ score on a network is visually demonstrated for the \textit{Arabidopsis PPI} dataset shown in Figure \ref{fig:query_example} with the hand selected GO term \textit{``SNAP receptor activity''}.
 

### 2018-06-19 cluster_query_tool/distributed_indexer.py

@@ -1,205 +1,0 @@
-import click
-import os
-import json
-import glob
-from hashlib import sha256
-from .indexer import partition_to_cut_set, partition_from_cut, dump
-from .louvain_consensus import gen_local_optima_community
-import random
-import networkx as nx
-from subprocess import check_output
-
-
-def load_graph(path, graph_name=None):
-    graph = nx.read_edgelist(path)
-
-    if graph_name is not None:
-        graph.name = graph_name
-    else:
-        graph.name = os.path.basename(path)
-    return graph
-
-
-@click.command()
-@click.argument('graph_path')
-@click.argument('seed')
-@click.argument('n_jobs')
-@click.argument('results_folder')
-@click.option("--walltime", default="01:30:00")
-@click.option("--space_sample_size", default=2000)
-@click.option("--request", default="select=1:ncpus=1:mem=8gb")
-@click.option("--queue", default="HPCA-01839-EFR")
-@click.option('--graph_name', default=None)
-@click.option('--cache_path', default='.ctq_cache')
-@click.option('--cache_name', default=None)
-def pbs_indexer(graph_path, seed, n_jobs, results_folder, walltime, request, space_sample_size, queue,
-                graph_name, cache_path, cache_name):
-    """
-    Generates space_sample_size starting cut sets and divides them in to n jobs to be scheduled
-
-    :param graph_path:
-    :param seed:
-    :param n_jobs:
-    :param results_folder:
-    :param walltime:
-    :param request:
-    :param space_sample_size:
-    :param queue:
-    :return:
-    """
-    graph = load_graph(graph_path, graph_name)
-
-    if cache_name is None:
-        cache_name = '{}-dist_res.json.xz'.format(graph.name)
-
-    job_options = dict(
-        walltime=walltime,
-        results_folder=os.path.abspath(results_folder),
-        request=request,
-        queue=queue,
-        graph_path=os.path.abspath(graph_path),
-        n_jobs=n_jobs,
-        seed=seed,
-        n_samps=int(round(int(space_sample_size) / int(n_jobs))),
-        graph_name=graph.name,
-        cache_path=os.path.abspath(cache_path),
-        cache_name=cache_name,
-    )
-
-    job_template = """#!/bin/bash
-#PBS -l {request}
-#PBS -l walltime={walltime}
-#PBS -P {queue}
-
-JOB=$PBS_ARRAY_INDEX
-
[…]

### 2018-06-19 cluster_query_tool/indexer.py

@@ -95,7 +95,7 @@ def partition_from_cut(graph, edge_set):
     return partition
 
 
-def _sample_local_optima(graph, seed):
+def sample_local_optima(graph, seed):
     """
     :param graph:
     :param seed:
@@ -114,7 +114,7 @@ def gen_sample_sets(graph, num_procs=cpu_count(), num_samples=2000, seed=1):
     """
     Compute louvain accross multiple cores
     """
-    cut_sets = Parallel(n_jobs=num_procs)(delayed(_sample_local_optima)(graph, s)
+    cut_sets = Parallel(n_jobs=num_procs)(delayed(sample_local_optima)(graph, s)
                                             for s in range(seed, seed+num_samples))
 
     cut_sets = list(set(cut_sets))

### 2018-06-19 cluster_query_tool/louvain_consensus.py

@@ -3,7 +3,6 @@ from . import louvain
 import networkx as nx
 import random
 import numpy as np
-from scipy.stats import mannwhitneyu
 from numba import jit
 
 
@@ -65,97 +64,6 @@ def gen_local_optima_community(graph, cut_set=None):
     return start_partition, local_optima
 
 
-def mu_iscore(nodes, partitions, query_nodes):
-    """
-
-    """
-    query_set = set(query_nodes)
-    qs = 0
-    muscore = dict([(n, 0) for n in nodes])
-
-    for partition in partitions:
-        best = max([(len(query_set.intersection(set(cluster))), cluster) for cluster in partition], key=lambda x: x[0])
-
-        qs += 1.0/(len(query_set) - 1) * (best[0] - 1)
-
-        for n in best[1]:
-            if n in muscore and best[0] > 0:
-                muscore[n] += 1.0/len(partitions)
-
-    qs *= 1.0/len(partitions)
-
-    return muscore
-
-
-def mu_ivector(graph_or_nodes, partitions, query_nodes):
-    """
-    For all nodes in V, return a vector $\mu$ such that $\mu$ is the fraction of times that a node is in
-    the largest cluster that intersects with the query set over all clusters.
-
-    returns muscore (numpy array of floats) and  mappings for keys to vector index.
-    """
-    nodes = {}
-    if isinstance(graph_or_nodes, nx.Graph):
-        nodes = set(graph_or_nodes.nodes())
-    else:
-        nodes = set(graph_or_nodes)
-
-    query_set = set(query_nodes)
-    muscore = np.zeros(len(nodes))
-
-    key = dict([(k, i) for i, k in enumerate(sorted(nodes))])
-
-    for partition in partitions:
-        best = max([(len(query_set.intersection(set(cluster))), cluster) for cluster in partition])
-
-        for i in best[1]:
-            muscore[key[i]] += 1
-
-    # Normalise result
-    return muscore * 1/len(partitions), key
-
-
-def mu_ivector_n(graph, partitions, query_nodes):
-    """
-    For all nodes in V, return a vector $\mu$ such that $\mu$ is the fraction of times that a node is in
-    the largest cluster that intersects with the query set over all clusters.
-
-    returns muscore (numpy array of floats) and  mappings for keys to vector index.
-    """
-    query_set = set(query_nodes)
-    muscore = np.zeros(graph.number_of_nodes())
-
[…]

### 2018-06-19 setup.py

@@ -19,9 +19,7 @@ setup(
     author_email="jamie.gilbert@azimov.co.uk",
     license="GPL",
     entry_points={
-        'console_scripts': [
-            "modindexer=cluster_query_tool.distributed_indexer:cli"
-        ]
+        'console_scripts': []
     },
     url="https://github.com/azimov/cluster_query_tool",
     include_package_data=True,

### 2018-06-19 cluster_query_tool/sampler.py
Added sampler for figure

@@ -1,0 +1,49 @@
+import networkx as nx
+import joblib
+import random
+from . import louvain
+from .louvain_consensus import create_partition_from_edge_set, modularity
+
+
+def partitions(graph, seed):
+    """
+    Generate a partition with louvain. If cut_set is None the starting partition will be randomly chosen.
+    :param graph: nx.Graph
+    :param cut_set: iterble, tuple of edges
+    :param seed: random seed
+    :return:
+    """
+    random.seed(seed)
+    cut_set = random.sample(graph.edges(), random.randint(1, graph.number_of_edges()))
+    # convert to partition
+    start_partition = create_partition_from_edge_set(graph, cut_set)
+    local_optima = louvain.best_partition(graph, partition=start_partition)
+
+    q_s = modularity(graph, start_partition)
+    q_o = modularity(graph, local_optima)
+
+    return (q_s, start_partition), (q_o, local_optima)
+
+
+def gen_sample(network_path, nsamples=10, seed=1):
+    """
+    Sampler for visualisation of network parition space
+    :param network_path:
+    :param nsamples:
+    :param seed:
+    :return:
+    """
+    graph = nx.read_edgelist(network_path)
+
+    # Sample start and end partitions and modularity for them
+    # store only unique partitions
+
+    partition_results = joblib.Parallel(n_jobs=joblib.cpu_count())(joblib.delayed(partitions)(graph, s)
+                                                                   for s in range(seed, seed+nsamples))
+
+    with open("partitions_mod.txt") as of:
+        # Output
+        for start, lo in partition_results:
+            for q, part in [start, lo]:
+                ptl = str([int(part[node]) for node in graph.nodes()])
+                of.write("{},{}\n".format(q, ptl))

### 2018-06-20 article/article.tex
Code tidy up

@@
 The methods developed in this paper are applied to biological and social datasets with ground-truth label data, using a small number of examples used as seed sets to uncover relationships.
-When tested on both real and synthetic datasets our method is shown to achieve high levels of classification accuracy in a context specific manner.
+When tested on both real and synthetic datasets our method is shown to achieve high levels of classification accuracy in a context specific manner, with results comparable to random walk with restart methods.
 \end{abstract}

### 2018-06-20 cluster_query_tool/experiments/__init__.py

@@ -1,41 +1,0 @@
-from scipy.special import binom
-import itertools
-
-
-def unique_sampler(node_set, sample_size, max_samples=120):
-    """
-    For sampling random query sets of a given size.
-
-    The node set size (e.g. true positives) limits the maximum number of samples to n choose k
-    where n is the node set size and k is the size of the sample
-
-    we want up to max_samples unique sets to be used as random starting labels
-
-    :param node_set: Set of nodes to sample from
-    :param sample_size: How many nodes to sample
-    :param max_samples: Maximum number of samples
-    :return:
-    """
-    sample_sets = set()
-
-    # maximum number of samples
-    sspace = binom(len(node_set), sample_size)
-    if sspace > max_samples:
-
-        if sspace > max_samples * 2:
-            # problem with this loop is when max_samples is close to n choose k
-            while len(sample_sets) < max_samples:
-                samp = tuple(sorted(np.random.choice(node_set, sample_size, replace=False)))
-                sample_sets.add(samp)
-        else:
-            # Generate max_samples, unique random numbers sampling without replacement from possible combinations
-            # Faster than above loop in case where n choose k is close to max_samples
-            sp = np.random.choice(range(int(binom(len(node_set), sample_size))), max_samples, replace=False)
-            poss = list(itertools.combinations(node_set, sample_size))
-            for s in sp:
-                sample_sets.add(poss[s])
-
-    else:
-        sample_sets = set(itertools.combinations(node_set, sample_size))
-
-    return sample_sets

### 2018-06-20 cluster_query_tool/experiments/utils.py

@@ -1,0 +1,140 @@
+from cluster_query_tool.louvain_consensus import query_vector
+
+from cigram import lfr_benchmark_graph
+from joblib import Parallel, delayed
+from multiprocessing import cpu_count
+import random
+import numpy as np
+from cluster_query_tool.indexer import get_index
+import logging
+from cluster_query_tool.random_walk import rwr
+
+from scipy.special import binom
+import itertools
+
+from numba import jit
+
+logger = logging.getLogger("cigram.generators")
+logger.setLevel(logging.ERROR)
+
+
+def param_modifier(params, param, values):
+    for val in values:
+        nparams = params.copy()
+        nparams[param] = val
+        yield nparams
+
+
+def _set_seed(params):
+    params["seed"] = random.randint(1, 10000000)
+    return params
+
+
+def gen_benchmark(params, seed, samples, n_jobs=cpu_count()):
+    random.seed(seed)
+    res = Parallel(n_jobs=n_jobs)(delayed(lfr_benchmark_graph)(**_set_seed(params)) for _ in range(samples))
+    return res
+
+
+def get_benchmarks(base_params, modified_params, param_vals, seed, samples):
+    for pset in param_modifier(base_params, modified_params, param_vals):
+        benchmarks = gen_benchmark(pset, seed, samples)
+        for graph, communities in benchmarks:
+            yield graph, communities, get_index(graph)
+
+
+def get_benchmark(params, num_procs=4):
+    graph, communities = lfr_benchmark_graph(**params)
+    return graph, communities, get_index(graph, num_procs=num_procs)
+
+
+def unique_sampler(node_set, sample_size, max_samples=120):
+    sample_sets = set()
+
+    # maximum number of samples
+    sspace = binom(len(node_set), sample_size)
+    if sspace > max_samples:
+
+        if sspace > max_samples * 2:
+            # problem with this loop is when max_samples is close to n choose k
+            while len(sample_sets) < max_samples:
+                samp = tuple(sorted(np.random.choice(node_set, sample_size, replace=False)))
+                sample_sets.add(samp)
+        else:
+            # Generate max_samples, unique random numbers sampling without replacement from possible combinations
+            # Faster than above loop in case where n choose k is close to max_samples
[…]

### 2018-06-20 experiments/experiments.py

@@ -1,140 +1,0 @@
-from cluster_query_tool.louvain_consensus import query_vector
-
-from cigram import lfr_benchmark_graph
-from joblib import Parallel, delayed
-from multiprocessing import cpu_count
-import random
-import numpy as np
-from cluster_query_tool.indexer import get_index
-import logging
-from cluster_query_tool.random_walk import rwr
-
-from scipy.special import binom
-import itertools
-
-from numba import jit
-
-logger = logging.getLogger("cigram.generators")
-logger.setLevel(logging.ERROR)
-
-
-def param_modifier(params, param, values):
-    for val in values:
-        nparams = params.copy()
-        nparams[param] = val
-        yield nparams
-
-
-def _set_seed(params):
-    params["seed"] = random.randint(1, 10000000)
-    return params
-
-
-def gen_benchmark(params, seed, samples, n_jobs=cpu_count()):
-    random.seed(seed)
-    res = Parallel(n_jobs=n_jobs)(delayed(lfr_benchmark_graph)(**_set_seed(params)) for _ in range(samples))
-    return res
-
-
-def get_benchmarks(base_params, modified_params, param_vals, seed, samples):
-    for pset in param_modifier(base_params, modified_params, param_vals):
-        benchmarks = gen_benchmark(pset, seed, samples)
-        for graph, communities in benchmarks:
-            yield graph, communities, get_index(graph)
-
-
-def get_benchmark(params, num_procs=4):
-    graph, communities = lfr_benchmark_graph(**params)
-    return graph, communities, get_index(graph, num_procs=num_procs)
-
-
-def unique_sampler(node_set, sample_size, max_samples=120):
-    sample_sets = set()
-
-    # maximum number of samples
-    sspace = binom(len(node_set), sample_size)
-    if sspace > max_samples:
-
-        if sspace > max_samples * 2:
-            # problem with this loop is when max_samples is close to n choose k
-            while len(sample_sets) < max_samples:
-                samp = tuple(sorted(np.random.choice(node_set, sample_size, replace=False)))
-                sample_sets.add(samp)
-        else:
-            # Generate max_samples, unique random numbers sampling without replacement from possible combinations
-            # Faster than above loop in case where n choose k is close to max_samples
[…]

### 2018-06-20 experiments/lfr_nooverlap.py

@@ -3,7 +3,7 @@ HPC script for running evaluation of performance on benchmark graphs
 
 This script is supposed to be run by the jobscript
 """
-from experiments import get_benchmark, get_auc_scores_community, get_auc_scores_community_rwr
+from cluster_query_tool.experiments.utils import get_benchmark, get_auc_scores_community, get_auc_scores_community_rwr
 from cigram import lfr_benchmark_graph
 from cluster_query_tool.louvain_consensus import membership_matrix
 import numpy as np
@@ -11,14 +11,12 @@ import click
 from subprocess import call
 import json
 import os
-from joblib import Parallel, delayed
-from itertools import product, chain
+
 import matplotlib as mpl
 mpl.use('Agg')
 from matplotlib import pyplot as plt
 import glob
 import pandas as pd
-import networkx as nx
 
 
 _base_params = dict(

### 2018-06-20 experiments/lfr_overlap.py

@@ -3,7 +3,8 @@ HPC script for running evaluation of performance on benchmark graphs
 
 This script is supposed to be run by the jobscript
 """
-from experiments import get_benchmark, get_auc_scores_community, get_auc_scores_community_rwr, lfr_benchmark_graph
+from cluster_query_tool.experiments.utils import get_benchmark, get_auc_scores_community, \
+    get_auc_scores_community_rwr, lfr_benchmark_graph
 import numpy as np
 import click
 from subprocess import call

### 2018-06-20 experiments/real_networks.py

@@ -1,7 +1,7 @@
 import networkx as nx
 from cluster_query_tool import louvain_consensus
 from cluster_query_tool.indexer import get_index
-from experiments import fast_auc, unique_sampler
+from cluster_query_tool.experiments.utils import fast_auc, unique_sampler
 from cluster_query_tool.random_walk import rwr
 from joblib import Parallel, delayed, cpu_count
 import json

### 2018-06-20 experiments/roc_calculation.py

@@ -1,86 +1,0 @@
-from __future__ import division
-import numpy as np
-cimport numpy as np
-
-
-def fast_auc(y_true, y_prob):
-    y_true = np.asarray(y_true)
-    y_true = y_true[np.argsort(y_prob)]
-    nfalse = 0
-    auc = 0
-    n = len(y_true)
-    for i in range(n):
-        y_i = y_true[i]
-        nfalse += (1 - y_i)
-        auc += y_i * nfalse
-    auc /= (nfalse * (n - nfalse))
-    return auc
-
-
-def mu_ivector(nodes, partitions, query):
-    """
-    For all nodes in V, return a vector $\mu$ such that $\mu$ is the fraction of times that a node is in
-    the largest cluster that intersects with the query set over all clusters.
-
-    returns muscore (numpy array of floats) and  mappings for keys to vector index.
-    """
-    muscore = np.zeros(nodes)
-
-    for partition in partitions:
-        cdef int best = 0
-        best_c = []
-        for cluster in partition:
-            intersect = np.intersect1d(cluster, partition)
-            if len(intersect) > best:
-                best = len(intersect)
-                best_c = cluster
-            elif len(intersect) == best:
-                best_c += cluster
-
-        for i in best_c:
-            muscore[i] += 1
-
-    # Normalise result
-    return muscore * 1/len(partitions)
-
-
-def roc_score_seed(seed_set, nodes, index, comm):
-    vec, key = mu_ivector(nodes, index, seed_set)
-    inc = lambda x: 1 if x in comm else 0
-    y_true = [inc(x) for x in nodes if x not in seed_set]
-    y_score = [vec[key[x]] for x in nodes if x not in seed_set]
-    return fast_auc(y_true, y_score)
-
-
-def unique_sampler(node_set, sample_size, max_samples=96):
-    sample_sets = set()
-
-    # maximum number of samples
-    sspace = binom(len(node_set), sample_size)
-    if sspace > max_samples:
-
-        if sspace > max_samples * 2:
-            # problem with this loop is when max_samples is close to n choose k
-            while len(sample_sets) < max_samples:
-                samp = tuple(sorted(np.random.choice(node_set, sample_size, replace=False)))
-                sample_sets.add(samp)
-        else:
-            # Generate max_samples, unique random numbers sampling without replacement from possible combinations
-            # Faster than above loop in case where n choose k is close to max_samples
[…]

### 2018-06-20 article/article.tex
Readme file

@@
 
-\begin{figure}[t]
-    \includegraphics[width=0.48\textwidth]{images/search_space_3.png}
-    \caption{Modularity search space of an \textit{E. coli} metabolic network.
- Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
-  The inset (top) demonstrates the landscape of the high modularity region.
-  Figure generated with the software of Good \textit{et al.} \cite{good2010performance}.}
-    \label{fig:modular_search_space}
-\end{figure}
+% \begin{figure}[t]
+%     \includegraphics[width=0.48\textwidth]{images/search_space_3.png}
+%     \caption{Modularity search space of an \textit{E. coli} metabolic network.
+%  Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
+%   The inset (top) demonstrates the landscape of the high modularity region.
+%   Figure generated with the software of Good \textit{et al.} \cite{good2010performance}.}
+%     \label{fig:modular_search_space}
+% \end{figure}
 
@@
 Each of these solution partitions are extremely close to the global maxima, making it both difficult to find the optimal value of $Q$ and difficult to argue that the highest scoring partition is the ``true'' community structure.
-This fact is visually demonstrated with the software from \cite{good2010performance} in Figure \ref{fig:modular_search_space}, which shows the modularity search space of an \textit{E.
+% This fact is visually demonstrated with the software from \cite{good2010performance} in Figure \ref{fig:modular_search_space}, which shows the modularity search space of an \textit{E.
 coli} metabolic network reconstruction \cite{GuimeraNature2005}.
-The similarity between the partitions is compared with the variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear} \footnote{The reader should note that axis on these plots are a result of the dimensionality reduction performed by curvilinear component analysis \cite{demartines1997curvilinear} and, therefore, have no natural interpretation.}.
+% The similarity between the partitions is compared with the variation of information measure \cite{meilua2003comparing} and dimensionality of the space is reduced with curvilinear component analysis \cite{demartines1997curvilinear} \footnote{The reader should note that axis on these plots are a result of the dimensionality reduction performed by curvilinear component analysis \cite{demartines1997curvilinear} and, therefore, have no natural interpretation.}.
 

### 2018-06-20 cluster_query_tool/sampler.py

@@ -1,8 +1,8 @@
 import networkx as nx
 from joblib import Parallel, cpu_count, delayed
 import random
-from . import louvain
-from .louvain_consensus import create_partition_from_edge_set, partition_to_cut_set
+from cluster_query_tool import louvain
+from cluster_query_tool.louvain_consensus import create_partition_from_edge_set, partition_to_cut_set
 from itertools import chain
 
 
@@ -29,7 +29,7 @@ def getpartitions(graph, seed):
     return partitions
 
 
-def gen_sample(network_path, nsamples=10000, seed=1, opt="partitions_mod.txt"):
+def gen_sample(graph, nsamples=10000, seed=1, opt="partitions_mod.txt"):
     """
     Sampler for visualisation of network parition space
     :param network_path:
@@ -37,7 +37,6 @@ def gen_sample(network_path, nsamples=10000, seed=1, opt="partitions_mod.txt"):
     :param seed:
     :return:
     """
-    graph = nx.read_edgelist(network_path, nodetype=int)
 
     # Sample start and end partitions and modularity for them
     # store only unique partitions
@@ -53,3 +52,8 @@ def gen_sample(network_path, nsamples=10000, seed=1, opt="partitions_mod.txt"):
             if cs not in cutsets:
                 cutsets.append(cs)
                 of.write("{},{}\n".format(q, ptl))
+
+
+def sample_file(network_path):
+    graph = nx.read_edgelist(network_path, nodetype=int)
+    gen_sample(graph)

### 2018-06-25 experiments/real_networks.py
Changed cross validation method slightly

@@ -101,7 +101,7 @@ def load_network(graph_path, graph_name, communities_path, index_path, node_type
 
 
     lengths = [len(x) for x in rcomm_l]
-    print(len(rcomms), min(lengths), max(lengths))
+    print("network contains", len(rcomms), "communities of min size", min(lengths), "and max size", max(lengths))
     return graph, rcomms, mmatrix, nmap
 
 
@@ -124,6 +124,67 @@ def get_community_significance_scores(mmatrix, nmap, comms):
     sign = Parallel(n_jobs=cpu_count())(delayed(comm_significance)(cid, map_com(comm, nmap), mmatrix)
                                         for cid, comm in comms.items())
     return dict(sign)
+                       
+def construct_true_memberships_matrix(nmap, com_dict):
+    
+    tmm = np.zeros((len(nmap), len(com_dict)), dtype=np.int8)
+    
+    c_keys = dict(enumerate(sorted(com_dict.keys())))
+    
+    for i, cid in c_keys.items():
+        for n in com_dict[cid]:
+            tmm[nmap[n]][i] = 1
+    
+    return tmm, c_keys
+    
+def get_y_true(seed_ind, tmm):
+    """
+    returns true membership vector for a set of seed nodes
+    This corrects for the situation where a group of seed nodes have the same overlapping community membership
+    """
+    if len(seed_ind) == 1:
+        seed_ind = np.array([seed_ind[0], seed_ind[0]])
+    
+    subm = tmm[np.array(seed_ind)]
+    
+    # Recursive bitwise and
+    tv = np.bitwise_and(subm[0], subm[0])
+    for sb in subm[1:]:
+        tv = np.bitwise_and(tv, sb)
+    
+    comm_indexes = np.where(tv)
+    
+    tr = np.unique(np.where(tmm.transpose()[comm_indexes]))
+    
+    y_true = np.array(
+        [i in tr for i in range(tmm.shape[0]) if i not in seed_ind],
+        dtype=np.int8
+    )
+    return y_true
+
+
+def samp_roc_and_auc_new(samp, mmatrix, comm, cid, s, true_membership_matrix):
+    ncom = np.array([x for x in range(mmatrix.shape[0]) if x not in samp])
[…]

### 2018-06-25 article/article.tex
Rewrite of lfr tests to us new cross validation method

--- 2018-06-20 article/article.tex
@@
 For this work we would like to capture binary classification  performance, \textit{true positives (tp)}, \textit{true negatives (tn), false positives (fp)} and \textit{false negatives (fn)}, on our datasets of community memberships.
-In order to generate the different sets for the cross validation we take each label set and generate unique sample sets of vertices from the known true positive labels.
-We also note that although each node can have multiple labels, in the tests performed in this study we only consider performance on individual labels.
+In order to generate the different sets for the cross validation we take each label set and generate unique sample sets of vertices from the known true positive labels\footnote{Note that although each node can have multiple labels, in the tests performed in this study we only consider performance on individual labels as this is likely the situation one would encounter with limited label sets in practice.}.
 
@@
 
+In the case for the synthetic networks tested below, true labels are drawn from the known communities, with each tested in isolation.
+For the real world networks tested the labels are considered in the same manner though many nodes have no assigned labels.
+Every community is considered with different seed set sizes.
+
 \subsection{Random walk with restart}
-As a comparison, we compare our method with the commonly used random walk with restart method as described in \cite{kohler2008walking}.
-This simulates an infinite random walk with a probability, $\alpha$ that a walker would teleport back to the initial seed nodes. 
+In the following sections compare our method with the commonly used random walk with restart method as described in \cite{kohler2008walking}.
+This simulates an infinite random walk with a fixed probability, $\alpha$ that a walker would teleport back to the initial seed nodes. 
 Formally, the random walk with restart algorithm uses the form
@@
 where $W$ is the row normalised adjacency matrix of a graph, $\vec{p}_0$ is the initial walk vector such that $\vec{p}_0 = \frac{1}{|S|}$ for vertices in the seed set.
-The random walk algorithm repeats equation \ref{eq:rwr} from $\vec{p}_0$ until the L1 norm between  $\vec{p}_t$ and  $\vec{p}_{t+1}$ converges to 0.
+The random walk algorithm repeats equation \ref{eq:rwr} from $\vec{p}_0$ until the L1 norm between  $\vec{p}_t$ and  $\vec{p}_{t+1}$ converges to 0, simulating the steady state vector $\vec{p}_{\infty}$.
 For the tests performed in this work we use a restart probability $\alpha = 0.25$.
@@
 \subsubsection{Tests on gene ontology labels}
-\begin{figure*}[]
+\begin{figure*}[t]
      \centering
@@
 
-\begin{figure*}[t]
-\includegraphics[width=0.8\textwidth]{images/ppi_example_combined.eps}
+\begin{figure}[t]
+\includegraphics[width=0.48\textwidth]{images/ppi_example_combined.eps}
 \caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
@@
 \label{fig:query_example}
-\end{figure*}
+\end{figure}
 
@@
 
+The reader may also consider the similarity of this approach to that of label propagation \cite{raghavan2007near, gregory2010finding}, which seeks to find communities based on a vote, where at different time steps a node updates it's label to to be the most common amongst its neighbours.
+A common problem with label propagation schemes is that they often fail to converge, resulting in many competing clusterings of a network.
+We liken this to the problem encountered by Good Good \textit{et al.} \cite{good2010performance} in modularity maximisation.
+The core contribution of this paper is that, in such situations, there is no single, context independent labelling scheme that can be seen as the ``true'' community structure, overlapping or not.
+Indeed, the approach applied here is extremely general and could be adapted to the label propagation approach (or any other community detection algorithm) should sufficient semi-supervised group memberships be known \textit{a priori}.
+
 Many existing method are based on the idea of a locally dense subgraph containing \textit{all query nodes} \cite{benson2016higher}.

### 2018-06-25 cluster_query_tool/experiments/utils.py

@@ -94,47 +94,81 @@ def fast_auc(y_true, y_prob):
     return auc
 
 
-def roc_score_seed(seed_set, nodes, membership_ma, comm):
+def roc_score_seed(seed_set, nodes, membership_ma, comm, tmm):
     vec = query_vector(seed_set, membership_ma)
 
-    def inc(x):
-        if x in comm:
-            return 1
-        return 0
-
-    y_true = np.array([inc(x) for x in nodes if x not in seed_set])
+    y_true = get_y_true(seed_set, tmm)
     y_score = np.array([vec[x] for x in nodes if x not in seed_set])
     return fast_auc(y_true, y_score)
 
 
-def roc_score_seed_rwr(seed_set, graph, comm, nmap):
+def roc_score_seed_rwr(seed_set, graph, comm, nmap, tmm):
     ncom = np.array([nmap[x] for x in graph.nodes() if nmap[x] not in seed_set])
     probs = rwr(graph, seed_set)
 
-    def inc(n):
-        if n in comm:
-            return 1
-        return 0
-
-    y_true = np.array([inc(x) for x in ncom])
+    y_true = get_y_true(seed_set, tmm)
     y_score = probs[ncom]
     return fast_auc(y_true, y_score)
 
 
-def get_auc_scores_community(seed_size, community, nodes, membership_ma, sample_seed=1337):
+def get_auc_scores_community(seed_size, community, nodes, membership_ma, tmm, sample_seed=1337):
     np.random.seed(sample_seed)
     samples = unique_sampler(community, seed_size)
 
-    funcs = (delayed(roc_score_seed)(np.array(sample), nodes, membership_ma, community) for sample in samples)
+    funcs = (delayed(roc_score_seed)(np.array(sample), nodes, membership_ma, community, tmm) for sample in samples)
     auc_scores = Parallel(n_jobs=cpu_count(), backend='threading')(funcs)
     return auc_scores
 
 
-def get_auc_scores_community_rwr(seed_size, community, graph, nmap, sample_seed=1337):
+def get_auc_scores_community_rwr(seed_size, community, graph, nmap, tmm, sample_seed=1337):
     np.random.seed(sample_seed)
     samples = unique_sampler(community, seed_size)
 
-    funcs = (delayed(roc_score_seed_rwr)(np.array(sample), graph, community, nmap) for sample in samples)
[…]

### 2018-06-25 experiments/lfr_nooverlap.py

@@ -3,7 +3,8 @@ HPC script for running evaluation of performance on benchmark graphs
 
 This script is supposed to be run by the jobscript
 """
-from cluster_query_tool.experiments.utils import get_benchmark, get_auc_scores_community, get_auc_scores_community_rwr
+from cluster_query_tool.experiments.utils import get_benchmark, get_auc_scores_community, get_auc_scores_community_rwr, \
+    construct_true_memberships_matrix
 from cigram import lfr_benchmark_graph
 from cluster_query_tool.louvain_consensus import membership_matrix
 import numpy as np
@@ -46,6 +47,7 @@ def auc_compute(seed, n, mu, results_folder):
     graph, communities, index = get_benchmark(pset)
 
     membership_ma, nmap = membership_matrix(graph.nodes(), index)
+    tmm, cmap = construct_true_memberships_matrix(nmap, communities)
 
     nodes = np.array(list(nmap.values()))
     results = []
@@ -54,7 +56,7 @@ def auc_compute(seed, n, mu, results_folder):
             if len(comm) > seed_size:
                 # Seed of AUC scores for node this size
                 scom = np.array([nmap[i] for i in comm])
-                auc_s = get_auc_scores_community(seed_size, scom, nodes, membership_ma)
+                auc_s = get_auc_scores_community(seed_size, scom, nodes, membership_ma, tmm)
                 results.append([int(n), float(mu), int(seed), c, seed_size, len(comm), np.mean(auc_s), np.std(auc_s)])
 
     with open(results_file, "w+") as rf:
@@ -78,6 +80,7 @@ def auc_compute_rwr(seed, n, mu, results_folder):
     graph, communities = lfr_benchmark_graph(**pset)
 
     nmap = dict([(j, i) for i, j in enumerate(sorted(graph.nodes()))])
+    tmm, cmap = construct_true_memberships_matrix(nmap, communities)
 
     results = []
     for c, comm in communities.items():
@@ -85,7 +88,7 @@ def auc_compute_rwr(seed, n, mu, results_folder):
             if len(comm) > seed_size:
                 # Seed of AUC scores for node this size
                 scom = [nmap[i] for i in comm]
-                auc_s = get_auc_scores_community_rwr(seed_size, scom, graph, nmap)
+                auc_s = get_auc_scores_community_rwr(seed_size, scom, graph, nmap, tmm)
[…]

### 2018-06-25 experiments/lfr_overlap.py

@@ -4,7 +4,7 @@ HPC script for running evaluation of performance on benchmark graphs
 This script is supposed to be run by the jobscript
 """
 from cluster_query_tool.experiments.utils import get_benchmark, get_auc_scores_community, \
-    get_auc_scores_community_rwr, lfr_benchmark_graph
+    get_auc_scores_community_rwr, lfr_benchmark_graph, construct_true_memberships_matrix
 import numpy as np
 import click
 from subprocess import call
@@ -43,6 +43,8 @@ def auc_compute(seed, n, ol, results_folder):
 
     membership_ma, nmap = membership_matrix(graph.nodes(), index)
 
+    tmm, cmap = construct_true_memberships_matrix(nmap, communities)
+
     nodes = np.array(list(nmap.values()))
     results = []
     for c, comm in communities.items():
@@ -50,7 +52,7 @@ def auc_compute(seed, n, ol, results_folder):
             if len(comm) > seed_size:
                 # Seed of AUC scores for node this size
                 scom = np.array([nmap[i] for i in comm])
-                auc_s = get_auc_scores_community(seed_size, scom, nodes, membership_ma)
+                auc_s = get_auc_scores_community(seed_size, scom, nodes, membership_ma, tmm)
                 results.append([int(n), int(ol), int(seed), c, seed_size, len(comm), np.mean(auc_s), np.std(auc_s)])
 
     with open(results_file, "w+") as rf:
@@ -75,13 +77,14 @@ def auc_compute_rwr(seed, n, ol, results_folder):
 
     nmap = dict([(j, i) for i, j in enumerate(sorted(graph.nodes()))])
 
+    tmm, cmap = construct_true_memberships_matrix(nmap, communities)
     results = []
     for c, comm in communities.items():
         for seed_size in _seed_sizes:
             if len(comm) > seed_size:
                 # Seed of AUC scores for node this size
                 scom = [nmap[i] for i in comm]
-                auc_s = get_auc_scores_community_rwr(seed_size, scom, graph, nmap)
+                auc_s = get_auc_scores_community_rwr(seed_size, scom, graph, nmap, tmm)
                 results.append([int(n), int(ol), int(seed), c, seed_size, len(comm), np.mean(auc_s), np.std(auc_s)])
 
     with open(results_file, "w+") as rf:

### 2018-06-25 experiments/real_networks.py

@@ -1,7 +1,7 @@
 import networkx as nx
 from cluster_query_tool import louvain_consensus
 from cluster_query_tool.indexer import get_index
-from cluster_query_tool.experiments.utils import fast_auc, unique_sampler
+from cluster_query_tool.experiments.utils import fast_auc, unique_sampler, construct_true_memberships_matrix, get_y_true
 from cluster_query_tool.random_walk import rwr
 from joblib import Parallel, delayed, cpu_count
 import json
@@ -124,43 +124,6 @@ def get_community_significance_scores(mmatrix, nmap, comms):
     sign = Parallel(n_jobs=cpu_count())(delayed(comm_significance)(cid, map_com(comm, nmap), mmatrix)
                                         for cid, comm in comms.items())
     return dict(sign)
-                       
-def construct_true_memberships_matrix(nmap, com_dict):
-    
-    tmm = np.zeros((len(nmap), len(com_dict)), dtype=np.int8)
-    
-    c_keys = dict(enumerate(sorted(com_dict.keys())))
-    
-    for i, cid in c_keys.items():
-        for n in com_dict[cid]:
-            tmm[nmap[n]][i] = 1
-    
-    return tmm, c_keys
-    
-def get_y_true(seed_ind, tmm):
-    """
-    returns true membership vector for a set of seed nodes
-    This corrects for the situation where a group of seed nodes have the same overlapping community membership
-    """
-    if len(seed_ind) == 1:
-        seed_ind = np.array([seed_ind[0], seed_ind[0]])
-    
-    subm = tmm[np.array(seed_ind)]
-    
-    # Recursive bitwise and
-    tv = np.bitwise_and(subm[0], subm[0])
-    for sb in subm[1:]:
-        tv = np.bitwise_and(tv, sb)
-    
-    comm_indexes = np.where(tv)
-    
-    tr = np.unique(np.where(tmm.transpose()[comm_indexes]))
-    
-    y_true = np.array(
-        [i in tr for i in range(tmm.shape[0]) if i not in seed_ind],
-        dtype=np.int8
-    )
-    return y_true
 
 
 def samp_roc_and_auc_new(samp, mmatrix, comm, cid, s, true_membership_matrix):

### 2018-06-25 experiments/lfr_overlap.py
quick test

@@ -73,9 +73,9 @@ def auc_compute_rwr(seed, n, ol, results_folder):
     rp = "{}_{}_{}_rwr.json".format(n, ol, seed)
     results_file = os.path.abspath(os.path.join(results_folder, rp))
 
-    graph, communities = lfr_benchmark_graph(**pset)
+    graph, communities, index = get_benchmark(pset)
 
-    nmap = dict([(j, i) for i, j in enumerate(sorted(graph.nodes()))])
+    membership_ma, nmap = membership_matrix(graph.nodes(), index)
 
     tmm, cmap = construct_true_memberships_matrix(nmap, communities)
     results = []

### 2018-06-25 article/article.tex
Removed faulty results
Trying to fix bug with HPC. Code functions on this pc but not hpc...

@@
 \begin{figure}[t]
-    \includegraphics[width=0.48\textwidth]{images/search_space_3.png}
+    \includegraphics[width=0.48\textwidth]{images/e_coli_search_space.eps}
     \caption{Modularity search space of an \textit{E. coli} metabolic network.
@@
 The cross validation procedure we devise is described as follows and depends on the size of the community and the number of initial seed labels being used.
+
 For this work we would like to capture binary classification  performance, \textit{true positives (tp)}, \textit{true negatives (tn), false positives (fp)} and \textit{false negatives (fn)}, on our datasets of community memberships.
-In order to generate the different sets for the cross validation we take each label set and generate unique sample sets of vertices from the known true positive labels\footnote{Note that although each node can have multiple labels, in the tests performed in this study we only consider performance on individual labels as this is likely the situation one would encounter with limited label sets in practice.}.
+In order to generate the different sets for the cross validation we take each label set and generate unique sample sets of vertices from the known true positive labels.
 
@@
 Consequently, cross validation is either conducted on an exhaustive set of all possible $\binom{|S|}{s}$ unique labellings or 120 seed queries sampled randomly without replacement from the possible subsets \footnote{This is equivalent to $\binom{10}{3}$ combinations, an exhaustive sample would not be possible for the larger communities in this study.}, where $S$ is the set of gold standard true labels and $s$ is the size of the randomly selected seed sets.
+
+As the selected seed sets can be contained within multiple communities, we consider the set of true positives not to be the community for which the seed set is randomly selected, but all communities for which that seed set is a subset of.
+This is because the purpose of the approach presented within this paper is to distinguish between different communities in a context specific manner, if the overlap between two communities is represented by the seed nodes this should be considered in the tests.
+
 It should therefore be noted that presented receiver operator characteristic (ROC) scores are dependent on community sizes.
@@
  \item Exclude vertices in $S_t$ from the test
- \item Consider all nodes in $S$ but not in $S_t$ to be the true positive set.
+ \item Consider the true community membership of $S_t$ to be the true positive set.
  \item Consider each of the nodes in $V$ not in $S$ to be the true negative set.
@@
 These results represent ROC curves and mean AUC statistics.
-For all the datasets in this study, binary community classification is high, with an average AUC scores above 0.87, even when using only a single seed node.
+
+The results of our method are comparable to the random walk with restart approach, which performs better on the datasets tested with the exception of the EU email dataset for which our model produces higher AUC scores.
+
 In the case of the \textit{Arabidopsis thaliana} network the protein complexes tested are significantly smaller than for other networks and so a comparison of seed sizes is not possible.
 However, in the other networks studied, using 3 or more seed nodes appears to improve results, though for 15 seed nodes the results are not significantly better than with 7 seeds.
-The results of our method are comparable to the random walk with restart approach, which performs better on the datasets tested with the exception of the EU email dataset for which our model performs significantly better.
+The lower quality labels within the Arabidopsis protein complex dataset likely explains the significant difference in results when compared with other protein interaction datasets.
 
@@
 
-\begin{figure}[t]
-\includegraphics[width=0.48\textwidth]{images/ppi_example_combined.eps}
-\caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
-(A) Shows the full network with 3 randomly chosen query nodes from the full query set.
-(B) Shows a reduced view of the network where a threshold of $\mu_i(S) > 0.8$ is selected, reducing the network to 404 nodes.
-Blue nodes indicates the 3 randomly selected query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
-(C) Shows an example ROC curve from the cross validation described in the main text.
-}
-\label{fig:query_example}
-\end{figure}
+% \begin{figure}[t]
+% \includegraphics[width=0.48\textwidth]{images/ppi_example_combined.eps}
+% \caption{An example of the GO term \textit{``SNAP receptor activity''} (16 nodes) on the \textit{Arabidopsis thaliana} protein-protein interaction network.
+% (A) Shows the full network with 3 randomly chosen query nodes from the full query set.
+% (B) Shows a reduced view of the network where a threshold of $\mu_i(S) > 0.8$ is selected, reducing the network to 404 nodes.
+% Blue nodes indicates the 3 randomly selected query nodes, yellow the remaining nodes in the term and the shade of red relates to the strength of the relationship each node has to the query set.
+% (C) Shows an example ROC curve from the cross validation described in the main text.
+% }
+% \label{fig:query_example}
+% \end{figure}
 
-In a practical situation the high quality label sets described above are not likely to be available.
+In a practical situation the higher quality label sets described above are not likely to be available.
 Consequently, we wish to highlight that the method also serves as a useful network reduction tool where the quality of labels is not well defined.
@@
 Gene Ontology is a controlled vocabulary of terms associated with biological functions in three broad categories of Cellular Components (CC),  Metabolic Functions (MF) and Biological Processes (BP), forming a hierarchy of terms and associated sub terms.
-The use of a $\mu_i(S)$ score on a network is visually demonstrated for the \textit{Arabidopsis PPI} dataset shown in Figure \ref{fig:query_example} with the hand selected GO term \textit{``SNAP receptor activity''}.
 
@@
 However, we speculate that it is likely due to the fact that the co-classification of vertices between different partitions remains fairly tolerant to changes.
-In other words, whilst the large communities they reside in changes significantly, the small cluster of nodes is always clustered in the same community, regardless of the partition.
+In other words, the small cluster of nodes is always clustered in the same community, regardless of the partition.
 We do note that, where communities are very small, any approach will be extremely sensitive to false positive and false negative results.
@@
 
-The results also appear to be highly tolerant to a small number of seed nodes.
+The approach also appears to be tolerant to a small number of seed nodes.
 This is interesting as in most sampled cases the relevant nodes are unlikely to be direct neighbours.
@@
 In the case of synthetic networks communities are correctly detected up to the detectability threshold.
-For real world networks with small label sets, average AUC scores were above 0.87 and comparable to the random walk with restart method for the high quality datasets tested in this study.
+For real world networks with small label sets, average AUC scores were comparable to the random walk with restart method for the high quality datasets tested in this study.
 

### 2018-06-25 experiments/lfr_overlap.py

@@ -11,6 +11,7 @@ from subprocess import call
 import os
 import json
 from cluster_query_tool.louvain_consensus import membership_matrix
+import networkx as nx
 
 
 _base_params = dict(
@@ -75,7 +76,12 @@ def auc_compute_rwr(seed, n, ol, results_folder):
 
     graph, communities, index = get_benchmark(pset)
 
-    membership_ma, nmap = membership_matrix(graph.nodes(), index)
+    nmap = dict([(j, i) for i, j in enumerate(graph.nodes())])
+
+    ngraph = nx.Graph()
+
+    for edge in graph.edges():
+        ngraph.add_edge(nmap[edge[0]], nmap[edge[1]])
 
     tmm, cmap = construct_true_memberships_matrix(nmap, communities)
     results = []
@@ -84,7 +90,7 @@ def auc_compute_rwr(seed, n, ol, results_folder):
             if len(comm) > seed_size:
                 # Seed of AUC scores for node this size
                 scom = [nmap[i] for i in comm]
-                auc_s = get_auc_scores_community_rwr(seed_size, scom, graph, nmap, tmm)
+                auc_s = get_auc_scores_community_rwr(seed_size, scom, ngraph, nmap, tmm)
                 results.append([int(n), int(ol), int(seed), c, seed_size, len(comm), np.mean(auc_s), np.std(auc_s)])
 
     with open(results_file, "w+") as rf:

### 2018-06-25 experiments/lfr_overlap.py
fix?

@@ -76,12 +76,7 @@ def auc_compute_rwr(seed, n, ol, results_folder):
 
     graph, communities, index = get_benchmark(pset)
 
-    nmap = dict([(j, i) for i, j in enumerate(graph.nodes())])
-
-    ngraph = nx.Graph()
-
-    for edge in graph.edges():
-        ngraph.add_edge(nmap[edge[0]], nmap[edge[1]])
+    nmap = dict([(j, i) for i, j in enumerate(sorted(graph.nodes()))])
 
     tmm, cmap = construct_true_memberships_matrix(nmap, communities)
     results = []
@@ -90,7 +85,7 @@ def auc_compute_rwr(seed, n, ol, results_folder):
             if len(comm) > seed_size:
                 # Seed of AUC scores for node this size
                 scom = [nmap[i] for i in comm]
-                auc_s = get_auc_scores_community_rwr(seed_size, scom, ngraph, nmap, tmm)
+                auc_s = get_auc_scores_community_rwr(seed_size, scom, graph, nmap, tmm)
                 results.append([int(n), int(ol), int(seed), c, seed_size, len(comm), np.mean(auc_s), np.std(auc_s)])
 
     with open(results_file, "w+") as rf:

### 2018-06-25 experiments/lfr_overlap.py
no fix

@@ -11,7 +11,6 @@ from subprocess import call
 import os
 import json
 from cluster_query_tool.louvain_consensus import membership_matrix
-import networkx as nx
 
 
 _base_params = dict(

### 2018-06-25 cluster_query_tool/experiments/utils.py
should fix

@@ -103,7 +103,7 @@ def roc_score_seed(seed_set, nodes, membership_ma, comm, tmm):
 
 
 def roc_score_seed_rwr(seed_set, graph, comm, nmap, tmm):
-    ncom = np.array([nmap[x] for x in graph.nodes() if nmap[x] not in seed_set])
+    ncom = np.array([x for x in range(tmm.shape[0]) if x not in seed_set])
     probs = rwr(graph, seed_set)
 
     y_true = get_y_true(seed_set, tmm)

### 2018-06-25 experiments/lfr_overlap.py

@@ -73,7 +73,7 @@ def auc_compute_rwr(seed, n, ol, results_folder):
     rp = "{}_{}_{}_rwr.json".format(n, ol, seed)
     results_file = os.path.abspath(os.path.join(results_folder, rp))
 
-    graph, communities, index = get_benchmark(pset)
+    graph, communities = lfr_benchmark_graph(**pset)
 
     nmap = dict([(j, i) for i, j in enumerate(sorted(graph.nodes()))])
 

### 2018-06-27 article/article.tex
updates to article

@@
 %\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
+\setcopyright{rightsretained}
 %\setcopyright{usgov}
@@
 % DOI
-\acmDOI{-}
+\makeatletter
+\renewcommand\@formatdoi[1]{\ignorespaces}
+\makeatother
 
@@
 \acmYear{2018}
-\copyrightyear{2018 Copyright held by the owner/author(s).}
+\copyrightyear{2018}
 \acmPrice{}
+
+\settopmatter{printacmref=false} % Removes citation information below abstract
+\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
+\pagestyle{plain} % removes running headers
 
@@
 More formally, the problem tackled in this paper can be formulated as follows:
-Given a graph made up of vertices and edges $G = (V, E)$, and a query set $S \subset V$, we formally ask the question; \textit{How well is a given vertex, $i \notin S$ related to $S$?}
+Given a graph made up of vertices and edges $G = (V, E)$, and a query set $S \subset V$, we ask the question; \textit{How well is a given vertex, $i \notin S$ related to $S$?}
 
@@
  Distance between partitions is calculated using variation of information \cite{meilua2003comparing} and dimensionality reduction is performed using curvilinear component analysis \cite{demartines1997curvilinear}.
-  The inset (top) demonstrates the landscape of the high modularity region.
+  The inset (top) demonstrates the landscape of the high modularity partitions.
   Figure generated with the software of Good \textit{et al.} \cite{good2010performance}.}
@@
 \subsection{Random walk with restart}
+\label{sec:rwr}
 In the following sections compare our method with the commonly used random walk with restart method as described in \cite{kohler2008walking}.
@@
 \subsubsection{Non-overlapping modules.}
-Figure \ref{fig:auc_no_overlap} represents tests on 100 networks with 1000 and 5000 nodes varying the mixing coefficient (number of edges between communities).
+Figure \ref{fig:auc_no_overlap} represents tests on 10 networks with 1000 and 5000 nodes varying the mixing coefficient (number of edges between communities).
 As one would expect, the prediction of the method drops off steeply where communities are less defined above a mixing coefficient of 0.6.
@@
     \caption{Non-overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
-     Data points represent mean AUC scores for all communities on 100 sampled networks at varying mixing coefficients.
+     Data points represent mean AUC scores for all communities on 10 sampled networks at varying mixing coefficients.
      Error bars represent one standard deviation.}
@@
     \caption{Overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
-     Data points represent mean AUC scores for all communities on 100 sampled networks at varying overlapping fraction of nodes.
+     Data points represent mean AUC scores for all communities on 10 sampled networks at varying overlapping fraction of nodes.
      Error bars represent one standard deviation.}
@@
 Here, a given seed set is created and random walks are analysed to find clearly related communities of vertices.
-One of the most common approaches to finding related vertices in a network is the random walk with restart (RWR) \cite{can2005analysis, kohler2008walking}.
+One of the most common approaches to finding related vertices in a network is the random walk with restart (RWR) \cite{can2005analysis, kohler2008walking} explained in section \ref{sec:rwr}.
 This approach has been applied in fields as diverse as recommender systems and the detection of potential drug targets \cite{chen2012drug}.
 In RWR the relatedness of any pair of vertices can be seen as the probability of a particle traversing the graph starting at a given vertex and ending at another.
-The restart aspect of the random walk can be thought of as the probability of the walker teleporting back to the start vertex set, as a fixed parameter. 
-The higher the probability of the walker ending up at a given vertex, the more likely it is that the two vertices are related.
-
 Conceptually, RWR is very similar to the method presented in this paper given that the user has a given query.
-The RWR probability as analogous to the value of $\mu_i(S)$ presented above.
+The RWR probability as analogous though not equivalent to the value of $\mu_i(S)$.
 
@@
 A common problem with label propagation schemes is that they often fail to converge, resulting in many competing clusterings of a network.
-We liken this to the problem encountered by Good Good \textit{et al.} \cite{good2010performance} in modularity maximisation.
-The core contribution of this paper is that, in such situations, there is no single, context independent labelling scheme that can be seen as the ``true'' community structure, overlapping or not.
+We liken this to the problem encountered by Good \textit{et al.} \cite{good2010performance} in modularity maximisation.
+A core contribution of this paper is that, in such situations, there is no single, context independent labelling scheme that can be seen as the ``true'' community structure, overlapping or not.
 Indeed, the approach applied here is extremely general and could be adapted to the label propagation approach (or any other community detection algorithm) should sufficient semi-supervised group memberships be known \textit{a priori}.

### 2018-06-28 article/article.tex
camera ready submission

@@
   \country{United Kingdom}
-  \postcode{NG7 2RD}
+  \postcode{NG8 1BB}
 }
@@
 A full coverage index could be considered as every locally optimal partition.
-Given that there is no free lunch and it is impossible to know every solution, one can only ensure a full coverage index through an exhaustive search over the $2^m$ possible starting cut sets.
+Given that there is no free lunch and it is impossible to know every solution, one can only ensure a full coverage index through an exhaustive search over the $2^m$ possible starting cut sets, where m is the number of edges in the graph.
 Consequently, the approach taken here is to use a large but not exhaustive subset of the possible solutions using a suitably large space of 2000 solutions for the networks studied in this paper
@@
 However, for the case where $i$ is in $S$ we, instead, consider the value $\mu_i(S - i)$ to remove bias.
-In many cases, a query set will not be fully represented by the partitions found within the network, this is further elaborated in the following section.
 
@@
 As the seed label sets can be as small as 3 vertices, exhaustive cross validation was not possible for all labelling schemes.
-Consequently, cross validation is either conducted on an exhaustive set of all possible $\binom{|S|}{s}$ unique labellings or 120 seed queries sampled randomly without replacement from the possible subsets \footnote{This is equivalent to $\binom{10}{3}$ combinations, an exhaustive sample would not be possible for the larger communities in this study.}, where $S$ is the set of gold standard true labels and $s$ is the size of the randomly selected seed sets.
+Consequently, cross validation is either conducted on an exhaustive set of all possible $\binom{|S|}{s}$ unique labellings or 120 seed queries sampled randomly without replacement from the possible subsets \footnote{This is equivalent to $\binom{10}{3}$ combinations, given time constraints, an exhaustive sample would not be possible for the larger communities in this study.}, where $S$ is the set of gold standard true labels and $s$ is the size of the randomly selected seed sets.
 
@@
  \item Consider the true community membership of $S_t$ to be the true positive set.
- \item Consider each of the nodes in $V$ not in $S$ to be the true negative set.
- \item Generate an average ROC curve interpolated from all test subsets.
+ \item Consider each of the nodes in $V$ not in the community membership of $S_t$ to be the true negative set.
+ \item Generate a network wide average ROC curve interpolated from all test subsets from all communities.
  \end{itemize}
@@
     \end{subfigure}
-    \caption{Non-overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
+    \caption{Non-overlapping LFR community networks with varying seed nodes with 1000 and 5000 nodes.
      Data points represent mean AUC scores for all communities on 10 sampled networks at varying mixing coefficients.
@@
     \end{subfigure}
-    \caption{Overlapping community varying seed nodes on LFR networks with 1000 and 5000 nodes.
+    \caption{Overlapping LFR community networks with varying seed nodes with 1000 and 5000 nodes.
      Data points represent mean AUC scores for all communities on 10 sampled networks at varying overlapping fraction of nodes.
@@
  The metadata used are known, experimentally validated protein complexes from \cite{pu2008up}.
- The network contains 6222 nodes in the largest connected component, with 22,3868 edges.
+ The network contains 6222 nodes in the largest connected component, with 22,386 edges.
  There are 409 experimentally validated protein complexes, 236 of which contain 3 or more nodes.
@@
  \item \textbf{\textit{Arabidopsis thaliana} protein-protein interaction network (Arabidopsis PPI)} \cite{ArabidopsisConsortium2011}.
-  The network itself contains 4519 nodes and 11096 edges.
+  The network itself contains 4519 nodes and 11,096 edges.
   For the Arabidopsis dataset, the complex sources were more limited.
@@
 As expected, average ROC and AUC scores shown in Figure \ref{fig:GO_TERM_ROCS} are considerably lower than for the Protein complexes for both our method and the rwr approach. 
-Interestingly, however, the performance of the rwr approach is significantly worse than one would expect to find at random for the Yeast GO terms.
-The reason for this performance remains unknown.
+Notably, however, the performance of the rwr approach is significantly worse than one would expect to find at random for the Yeast GO terms.
+The reason for this performance remains unknown, however, it is likely to to the fact that the gene ontology labels are poorly represented in the dataset.
 However, this approach should be considered in contrast to conventional gene enrichment strategies on conventional network clusters \cite{chen2013enrichr}.
